### 2024-02-05 main.tex
20240205

\documentclass{elsarticle}
\usepackage{amsmath,amssymb,amsfonts,amsthm,bm}
\usepackage{hyperref}
\usepackage{booktabs,multirow}
\usepackage{lineno}
\linenumbers

\begin{document}
\include{mix}
\end{document}

### 2024-02-06 examples.tex
temp

\section{Numerical examples}
\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth]{figures/patchtest_msh}
    \caption{Meshfree discretization for patch test}

\end{figure}

### 2024-02-09 boundary.tex
20240209

\section{Naturally variational enforcement for essential boundary conditions}

### 2024-02-09 kinematics.tex
20240209

\section{Hu-Washizu's formulation of complementary energy for thin shell}
\subsection{Kinematics for thin shell}
\begin{equation}
\varepsilon_{\alpha\beta} = \frac{1}{2}(\boldsymbol a_\alpha \cdot \boldsymbol v_{,\beta} + \boldsymbol a_\beta \cdot \boldsymbol v_{,\alpha})
\end{equation}

\begin{equation}
\theta_{\boldsymbol n} = \boldsymbol a_3 \cdot \boldsymbol v_{,\alpha} n^\alpha
\end{equation}

\begin{equation}
\kappa_{\alpha\beta} = (\Gamma^\gamma_{\alpha\beta} \boldsymbol v_{,\gamma} - \boldsymbol v_{,\alpha\beta}) \cdot \boldsymbol a_3 = - \boldsymbol v_{,\alpha}\vert_\beta \cdot \boldsymbol a_3
\end{equation}

\begin{equation}
\boldsymbol t = \boldsymbol t_N + \boldsymbol t_M
\end{equation}

\begin{equation}
\boldsymbol t_N = \boldsymbol a_\alpha N^{\alpha\beta} n_\beta
\end{equation}

\begin{equation}
\boldsymbol t_M = (\boldsymbol a_3 M^{\alpha\beta})\vert_\beta n_\alpha + (\boldsymbol a_3 M^{\alpha\beta} s_\alpha n_\beta)_{,\gamma} s^\gamma
\end{equation}

\begin{equation}
M_{\boldsymbol{nn}} = M^{\alpha\beta}n_\alpha n_\beta
\end{equation}

\begin{equation}
\boldsymbol b = \boldsymbol b_N + \boldsymbol b_M
\end{equation}

\begin{equation}
\boldsymbol b_N = (\boldsymbol a_\alpha N^{\alpha\beta})\vert_\beta
\end{equation}

\begin{equation}
\boldsymbol b_M = (\boldsymbol a_3 M^{\alpha\beta})_{,\alpha}\vert_\beta
\end{equation}

\begin{equation}
P = -[[M^{\alpha\beta}s_\alpha n_\beta]]
\end{equation}

\subsection{Galerkin weak form for Hu-Washizu principle of complementary energy}
In accordance with the Hu-Washizu variational principle of complementary energy \cite{dah-wei1985}, the corresponding complementary functional, denoted by $\Pi$, is listed as follow:
\begin{equation} \label{functional}
\begin{split}
&\Pi(\boldsymbol v, \varepsilon_{\alpha\beta},\kappa_{\alpha\beta},N^{\alpha\beta},M^{\alpha\beta}) \\
= &\int_\Omega \frac{h}{2}\varepsilon_{\alpha\beta} C^{\alpha\beta\gamma\eta}\varepsilon_{\gamma\eta}d\Omega 
+ \int_\Omega \frac{h^3}{24}\kappa_{\alpha\beta} C^{\alpha\beta\gamma\eta}\kappa_{\gamma\eta}d\Omega \\
+& \int_\Omega \varepsilon_{\alpha\beta} (N^{\alpha\beta} - h C^{\alpha\beta\gamma\eta} \varepsilon_{\gamma\eta}) d\Omega
+ \int_\Omega \kappa_{\alpha\beta} (M^{\alpha\beta} - \frac{h^3}{12} C^{\alpha\beta\gamma\eta} \kappa_{\gamma\eta}) d\Omega \\
-& \int_{\Gamma_v} \boldsymbol t \cdot \bar{\boldsymbol v} d\Gamma 
+ \int_{\Gamma_\theta} M_{\boldsymbol{nn}} \bar \theta_{\boldsymbol n} d\Gamma - (P \boldsymbol a_3 \cdot \bar{\boldsymbol v})_{\boldsymbol x \in C_w} \\
+ &\int_{\Gamma_M} \theta_{\boldsymbol n} (M_{\boldsymbol{nn}} - \bar M_{\boldsymbol{nn}}) d\Gamma
- \int_{\Gamma_t} \boldsymbol v \cdot (\boldsymbol t - \bar{\boldsymbol t})d\Gamma - \boldsymbol v \cdot \boldsymbol a_3 (P - \bar{P})_{\boldsymbol x \in C_P} \\
- &\int_\Omega \boldsymbol v \cdot (\boldsymbol b - \bar{\boldsymbol b}) d\Omega \\
\end{split}
\end{equation}

Introducing a standard variational argument to Eq. (\ref{functional}), $\delta \Pi=0$, and considering the arbitrariness of virtual variables, $\delta \boldsymbol v$, $\delta \varepsilon_{\alpha\beta}$, $\delta \kappa_{\alpha\beta}$, $N^{\alpha\beta}$, $M^{\alpha\beta}$ lead to the following weak form:

\begin{subequations}
\begin{equation}
- \int_\Omega h \delta \varepsilon_{\alpha\beta} C^{\alpha\beta\gamma\eta}\varepsilon_{\gamma\eta}d\Omega 
+ \int_\Omega \delta \varepsilon_{\alpha\beta} N^{\alpha\beta} d\Omega = 0
\end{equation}
\begin{equation}
- \int_\Omega \frac{h^3}{12} \delta \kappa_{\alpha\beta} C^{\alpha\beta\gamma\eta}\kappa_{\gamma\eta}d\Omega 
+ \int_\Omega \delta \kappa_{\alpha\beta} M^{\alpha\beta} d\Omega = 0
\end{equation}
\begin{multline}
\int_\Omega \delta N^{\alpha\beta} \varepsilon_{\alpha\beta} d\Omega
- \int_\Gamma \delta \boldsymbol t_N \cdot \boldsymbol v d\Gamma 
+ \int_\Omega \delta \boldsymbol b_N \cdot \boldsymbol v d\Omega \\
+ \int_{\Gamma_v} \delta \boldsymbol t_N \cdot \boldsymbol v d\Gamma 
= \int_{\Gamma_v} \delta \boldsymbol t_N \cdot \bar{\boldsymbol v} d\Gamma 
\end{multline}
\begin{multline}
\int_\Omega \delta M^{\alpha\beta} \kappa_{\alpha\beta} d\Omega 
- \int_\Gamma \delta M_{\boldsymbol{nn}} \theta_{\boldsymbol n}d\Gamma
+ \int_\Gamma \delta \boldsymbol t_M \cdot \boldsymbol v d\Gamma
+ (\delta P \boldsymbol a_3 \cdot \boldsymbol v)_{\boldsymbol x \in C}
+ \int_\Omega \delta \boldsymbol b_M \cdot \boldsymbol v d\Omega \\
+ \int_{\Gamma_\theta} \delta M_{\boldsymbol{nn}} \theta_{\boldsymbol n}d\Gamma
- \int_{\Gamma_v} \delta \boldsymbol t_M \cdot \boldsymbol v d\Gamma
- (\delta P \boldsymbol a_3 \cdot \boldsymbol v)_{\boldsymbol x \in C_v} \\ =
\int_{\Gamma_\theta} \delta M_{\boldsymbol{nn}} \bar{\theta}_{\boldsymbol n}d\Gamma
- \int_{\Gamma_v} \delta \boldsymbol t_M \cdot \bar{\boldsymbol v} d\Gamma
- (\delta P \boldsymbol a_3 \cdot \bar{\boldsymbol v})_{\boldsymbol x \in C_v} \\
\end{multline}
\begin{multline}
\int_{\Gamma} \delta \theta_{\boldsymbol n} M_{\boldsymbol{nn}} d\Gamma
    - \int_\Gamma \delta \boldsymbol v \cdot \boldsymbol t d\Gamma 
    - (\delta \boldsymbol v \cdot \boldsymbol a_3 P)_{\boldsymbol x \in C}
    + \int_\Omega \delta \boldsymbol v \cdot \boldsymbol b d\Omega \\
    - \int_{\Gamma_\theta} \delta \theta_{\boldsymbol n} M_{\boldsymbol{nn}} d\Gamma
    + \int_{\Gamma_v} \delta \boldsymbol v \cdot \boldsymbol t d\Gamma 
    + (\delta \boldsymbol v \cdot \boldsymbol a_3 P)_{\boldsymbol x \in C_v}
    = - \int_{\Gamma_t} \delta \boldsymbol v \cdot \bar{\boldsymbol t} d\Gamma - \int_\Omega \delta \boldsymbol v \cdot \bar{\boldsymbol b} d\Omega
\end{multline}
\end{subequations}
where the geometric relationships of Eq. () is used herein.

### 2024-02-09 kinematics.tex
202402010

@@
 \end{equation}
-
 Introducing a standard variational argument to Eq.
 (\ref{functional}), $\delta \Pi=0$, and considering the arbitrariness of virtual variables, $\delta \boldsymbol v$, $\delta \varepsilon_{\alpha\beta}$, $\delta \kappa_{\alpha\beta}$, $N^{\alpha\beta}$, $M^{\alpha\beta}$ lead to the following weak form:
-
 \begin{subequations}
-\begin{equation}
+\begin{equation}\label{w1}
 - \int_\Omega h \delta \varepsilon_{\alpha\beta} C^{\alpha\beta\gamma\eta}\varepsilon_{\gamma\eta}d\Omega 
@@
 \end{equation}
-\begin{equation}
+\begin{equation}\label{w2}
 - \int_\Omega \frac{h^3}{12} \delta \kappa_{\alpha\beta} C^{\alpha\beta\gamma\eta}\kappa_{\gamma\eta}d\Omega 
@@
 \end{equation}
-\begin{multline}
+\begin{multline}\label{w3}
 \int_\Omega \delta N^{\alpha\beta} \varepsilon_{\alpha\beta} d\Omega
@@
 \end{multline}
-\begin{multline}
+\begin{multline}\label{w4}
 \int_\Omega \delta M^{\alpha\beta} \kappa_{\alpha\beta} d\Omega 
@@
 \end{multline}
-\begin{multline}
+\begin{multline}\label{w5}
 \int_{\Gamma} \delta \theta_{\boldsymbol n} M_{\boldsymbol{nn}} d\Gamma

### 2024-02-10 boundary.tex
temp

@@
 \section{Naturally variational enforcement for essential boundary conditions}
+\subsection{Discrete equilibrium equations}
+With the approximated effective stresses and strains, the last equation of weak form becomes:
+\begin{equation}\label{w51}
+- \sum_{C=1}^{n_e}(\tilde{\boldsymbol g}^T_{\alpha I} - \bar{\boldsymbol g}^T_{\alpha I}) \boldsymbol d_N^{\alpha}
+- \sum_{C=1}^{n_e}(\tilde{\boldsymbol g}^T_{\alpha\beta I} - \bar{\boldsymbol g}^T_{\alpha\beta I}) \boldsymbol d_M^{\alpha\beta} = \boldsymbol f_I
+\end{equation}
+where $\boldsymbol f_I$'s are the components of the traditional force vector:
+\begin{equation}
+        \boldsymbol f_I = \int_{\Gamma_t} \Psi_I \bar{\boldsymbol t} d\Gamma - \int_{\Gamma_M} \Psi_{I,\gamma} n^\gamma \bar M_{\boldsymbol{nn}} d\Gamma + [[\Psi_I\boldsymbol a_3 \bar P]]_{\boldsymbol x\in C_P} + \int_\Omega \Psi_I \bar{\boldsymbol b} d\Omega
+\end{equation}
+and further substituting coefficients $\boldsymbol d_N^\alpha$, $\boldsymbol d_M^{\alpha\beta}$ into Eq. (\ref{w51}) gives the final discrete equilibrium equations: 
+\begin{equation}
+\begin{split}
+&- \sum_{C=1}^{n_c}(\tilde{\boldsymbol g}^T_{\alpha I} - \bar{\boldsymbol g}^T_{\alpha I}) \boldsymbol d_N^{\alpha}
+- \sum_{C=1}^{n_c}(\tilde{\boldsymbol g}^T_{\alpha\beta I} - \bar{\boldsymbol g}^T_{\alpha\beta I}) \boldsymbol d_M^{\alpha\beta} \\
+= &\sum_{C=1}^{n_e} \sum_{J=1}^{n_p} \left (
+\begin{split}
+& \boldsymbol a_\alpha \tilde{\boldsymbol g}^T_{\beta I} h C^{\alpha\beta\gamma\eta} \boldsymbol a_\gamma \tilde{\boldsymbol g}_{\eta J} 
++ \tilde{\boldsymbol g}^T_{\alpha\beta I} \boldsymbol a_3 \frac{h^3}{12}C^{\alpha\beta\gamma\eta} \boldsymbol a_3 \tilde{\boldsymbol g}_{\gamma\eta} \\
+- & \boldsymbol a_\alpha \bar{\boldsymbol g}^T_{\beta I} h C^{\alpha\beta\gamma\eta} \boldsymbol a_\gamma \tilde{\boldsymbol g}_{\eta J} - \boldsymbol a_\alpha \tilde{\boldsymbol g}^T_{\beta I} h C^{\alpha\beta\gamma\eta} \boldsymbol a_\gamma \bar{\boldsymbol g}_{\eta J} \\
+- & \bar{\boldsymbol g}^T_{\alpha\beta I}\boldsymbol a_3 \frac{h^3}{12} C^{\alpha\beta\gamma\eta} \boldsymbol a_3 \tilde{\boldsymbol g}_{\gamma\eta J} - \tilde{\boldsymbol g}^T_{\alpha\beta I} \boldsymbol a_3 \frac{h^3}{12} C^{\alpha\beta\gamma\eta} \boldsymbol a_3 \bar{\boldsymbol g}_{\gamma\eta J} \\
++ & \boldsymbol a_\alpha \tilde{\boldsymbol g}^T_{\beta I} h C^{\alpha\beta\gamma\eta} \boldsymbol a_\gamma \hat{\boldsymbol g}_{\eta J}
+- \boldsymbol a_\alpha \bar{\boldsymbol g}^T_{\beta I} h C^{\alpha\beta\gamma\eta} \boldsymbol a_\gamma \hat{\boldsymbol g}_{\eta J} \\
++ & \tilde{\boldsymbol g}^T_{\alpha\beta I}\boldsymbol a_3 \frac{h^3}{12} C^{\alpha\beta\gamma\eta} \boldsymbol a_3 \hat{\boldsymbol g}_{\gamma\eta J} - \bar{\boldsymbol g}^T_{\alpha\beta I} \boldsymbol a_3 \frac{h^3}{12} C^{\alpha\beta\gamma\eta} \boldsymbol a_3 \hat{\boldsymbol g}_{\gamma\eta J} \\
++ & \boldsymbol a_\alpha \bar{\boldsymbol g}^T_{\beta I} h C^{\alpha\beta\gamma\eta} \boldsymbol a_\gamma \bar{\boldsymbol g}_{\eta J}
++ \bar{\boldsymbol g}^T_{\alpha\beta I}\boldsymbol a_3 \frac{h^3}{12} C^{\alpha\beta\gamma\eta} \boldsymbol a_3 \bar{\boldsymbol g}_{\gamma\eta J} 
+\end{split}
+\right ) \\
+= &\sum_{J=1}^{n_p} (\boldsymbol K_{IJ}+\tilde{\boldsymbol K}_{IJ}+\bar{\boldsymbol K}_{IJ}) \cdot \boldsymbol d_J - \tilde{\boldsymbol f}_I - \bar{\boldsymbol f}_I
+\end{split}
+\end{equation}
+where
+\begin{equation}\label{de1}
+        \boldsymbol K_{IJ} = \int_\Omega \tilde{\boldsymbol \varepsilon}_{\alpha\beta I} \tilde{\boldsymbol N}^{\alpha\beta}_J d\Omega + \int_\Omega \tilde{\boldsymbol \kappa}_{\alpha\beta I} \tilde{\boldsymbol M}^{\alpha\beta}_J d\Omega
+\end{equation}
+\begin{subequations}\label{de2}
+\begin{align}
+\begin{split}
+        \tilde{\boldsymbol K}_{IJ} = &- \int_{\Gamma_v} (\Psi_I \tilde{\boldsymbol t}_J + \tilde{\boldsymbol t}_I \Psi_J) d\Gamma \\
+                                     &+ \int_{\Gamma_\theta} (\Psi_{I,\gamma} n^\gamma \boldsymbol a_3 \tilde M_{\boldsymbol{nn}J} + \boldsymbol a_3 \tilde M_{\boldsymbol{nn}I} \Psi_{I,\gamma}n^\gamma)d\Gamma \\
+                                     & + ([[\Psi_I \boldsymbol a_3 P_J]] + [[P_I \boldsymbol a_3 \Psi_J]])_{\boldsymbol x \in C_v}
+\end{split} \\
+\tilde{\boldsymbol f}_I = &- \int_{\Gamma_v} \tilde{\boldsymbol t}_I \cdot \bar{\boldsymbol v} d\Gamma + \int_{\Gamma_\theta} \tilde M_{\boldsymbol{nn}} \bar{\theta}_{\boldsymbol n} d\Gamma + [[\tilde P_I\boldsymbol a_3 \cdot \bar{\boldsymbol v}]]_{\boldsymbol x \in C_v}
+\end{align}
+\end{subequations}
+\begin{subequations}\label{de3}
+\begin{align}
+\bar{\boldsymbol K}_{IJ} &= - \int_{\Gamma_v} \bar{\boldsymbol t}_I \Psi_J d\Gamma 
++ \int_{\Gamma_\theta} \boldsymbol a_3\bar M_{\boldsymbol{nn}I} \Psi_{J,\gamma}n^\gamma d\Gamma + [[\bar P_I \boldsymbol a_3 \Psi_J]]_{\boldsymbol x \in C_v} \\
+\bar{\boldsymbol f}_I &= - \int_{\Gamma_v} \bar{\boldsymbol t}_I \cdot \bar{\boldsymbol v} d\Gamma + \int_{\Gamma_\theta} \bar M_{\boldsymbol{nn}} \bar{\theta}_{\boldsymbol n} d\Gamma + [[\bar P_I\boldsymbol a_3 \cdot \bar{\boldsymbol v}]]_{\boldsymbol x \in C_v}
+\end{align}
+\end{subequations}
+
+The detailed derivations of Eqs (\ref{de1})-(\ref{de3}) are listed in the Appendix.
+As shown in these equations, the Eq.
+(\ref{de1}) is the conventional stiffness matrix evaluated by smoothed gradients of Eqs.
+()

### 2024-02-10 introduction.tex
temp

\section{Introduction}
Thin shell is one of the most frequently used structure in engineering practice, where the thickness of this kind structure is often much smaller than its radius. With the Kirchhoff-Love hypothesis [1–3], the transverse shear deformation is eliminated in thin shell analysis, such that at least C1 continuous shape functions are required within Galerkin methods. In static and dynamic simulation of structure, the conventional finite element methods [1,2] are one of the most popular approximation scheme, however the construction of C1 continuity is still a big challenge for cell-based finite element methods. In last three decades, the meshfree methods [1–3] equipped high order smoothed shape functions have attracted significant research attention, while the meshfree shape functions are established based upon a set of scattered nodes and the high order continuity of shape functions is easily fulfilled even with low order basis function. For thin shell analysis, this high order meshfree approximations can also alleviate the membrane locking caused by the mismatched approximation order of membrane strain and bending strain [1]. Moreover, in general, the nodal-based meshfree approximations can release the burden of mesh distortion and have the flexibility of local refinement. Due to these advantages, a wide variety meshfree methods are proposed and have been applied to many scientific or engineering fields. Among of them, moving least squares (MLS) and reproducing kernel (RK) meshfree approximations built their shape functions by enforcing the so-call consistency conditions, where the consistency conditions require that the corresponding approximations should exactly reproduce every functions spanned by basis functions, and this conditions usually serve as a basic requirement for the error convergence of resolved Galerkin solutions [1]. However, the high order smoothed meshfree shape functions accompany with the severely overlapping supports, which leads to a misalignment between numerical integration domains and supports of shape functions. As a result, the meshfree shape functions usually exhibit a piecewise rational nature in each integration domains, and it brings a serious difficulty to the accurate numerical integration in Galerkin weak forms [1].

### 2024-02-11 boundary.tex
202402011

@@
 As shown in these equations, the Eq.
-(\ref{de1}) is the conventional stiffness matrix evaluated by smoothed gradients of Eqs.
-()
+(\ref{de1}) is the conventional stiffness matrix evaluated by smoothed gradients $\tilde \Psi_{I,\alpha}$, $\tilde \Psi_{I,\alpha}\vert_\beta$, and the Eqs.
+(\ref{de2}) and (\ref{de3}) contribute for the enforcement of essential boundary.
+
+\subsection{Comparison with Nitsche's method}
+The Nitsche's method for enforcing essential boundary can be regarded as a combination of Lagrangian multiplier method and penalty method, in which the Lagrangian multiplier is represented by the approximated displacement.
+The corresponding total potential energy functional $\Pi_P$ is given by:
+\begin{equation}
+\begin{split}
+\Pi_P(\boldsymbol v) &= \int_\Omega \frac{1}{2}\varepsilon_{\alpha\beta} N^{\alpha\beta} d\Oemga +
+\int_\Omega \frac{1}{2} \kappa_{\alpha\beta}M^{\alpha\beta} d\Omega \\
+                     &- \int_{\Gamma_t} \boldsymbol v \cdot \bar{\boldsymbol t} d\Gamma 
+                     + \int_{\Gamma_M} \boldsymbol v_{,\gamma} n^\gamma \boldsymbol a_3 M_{\boldsymbol{nn}} d\Gamma
+                     + (\boldsymbol v \cdot \boldsymbol a_3 P)_{\boldsymbol x \in C_P}
+                     - \int_\Omega \boldsymbol v \cdot \bar{\boldsymbol b} d\Omega \\
+                     &- \underbrace{\int_{\Gamma_v} \boldsymbol t \cdot (\boldsymbol v - \bar{\boldsymbol v}) d\Gamma
+                     + \int_{\Gamma_\theta} M_{\boldsymbol{nn}}(\theta_{\boldsymbol n} - \bar \theta_{\boldsymbol n})d\Gamma
+                     + (P\boldsymbol a_3 \cdot (\boldsymbol v - \bar{\boldsymbol v}))_{\boldsymbol x \in C_v}}_{\text{consistent term}} \\
+                     &+ \underbrace{\frac{\alpha_v}{2} \int_{\Gamma_v} \boldsymbol v \cdot \boldsymbol v d\Gamma 
+                     + \frac{\alpha_\theta}{2} \int_{\Gamma_\theta} \theta_{\boldsymbol n}^2 d\Gamma
+             + \frac{\alpha_C}{2}(\boldsymbol v \cdot \boldsymbol v)_{\boldsymbol x\in C_v}}_{\text{stabilized term}}
+\end{split}
+\end{equation}
+where the consistent term rephrased from Lagrangian multiplier method contributes to enforce the essential boundary and meet the variational consistency condition.
+However the consistent term can not always ensure the coercivity of stiffness, so the penalty method is introduced to be regarded as a stabilized term.
+With a standard variational argument, the corresponding weak form can be stated as:
+\begin{equation}
+\begin{split}
+\delta \Pi_P(\boldsymbol v) &= \int_\Omega\delta \varepsilon_{\alpha\beta} N^{\alpha\beta} d\Oemga +
+\int_\Omega \delta \kappa_{\alpha\beta}M^{\alpha\beta} d\Omega \\
+                     &- \int_{\Gamma_t} \delta \boldsymbol v \cdot \bar{\boldsymbol t} d\Gamma 
+                     + \int_{\Gamma_M} \delta \boldsymbol v_{,\gamma} n^\gamma \boldsymbol a_3 M_{\boldsymbol{nn}} d\Gamma
+                     + (\delta \boldsymbol v \cdot \boldsymbol a_3 P)_{\boldsymbol x \in C_P}
+                     - \int_\Omega \delta \boldsymbol v \cdot \bar{\boldsymbol b} d\Omega \\
+                     &- \int_{\Gamma_v} \delta \boldsymbol v \cdot \boldsymbol t d\Gamma 
+                     + \int_{\Gamma_\theta} \delta \theta_{\boldsymbol n} M_{\boldsymbol{nn}}d\Gamma 
+                     + (\boldsymbol v \cdot \boldsymbol a_3 P)_{\boldsymbol x \in C_v}\\
+                     &- \int_{\Gamma_v} \delta \boldsymbol t \cdot (\boldsymbol v - \bar{\boldsymbol v}) d\Gamma
+                     + \int_{\Gamma_\theta} \delta M_{\boldsymbol{nn}}(\theta_{\boldsymbol n} - \bar \theta_{\boldsymbol n})d\Gamma
+                     + (\delta P\boldsymbol a_3 \cdot (\boldsymbol v - \bar{\boldsymbol v}))_{\boldsymbol x \in C_v} \\
+                     &+ \alpha_v \int_{\Gamma_v} \delta \boldsymbol v \cdot \boldsymbol v d\Gamma 
+                     + \alpha_\theta \int_{\Gamma_\theta} \delta \theta_{\boldsymbol n}\theta_{\boldsymbol n} d\Gamma
+                     + \alpha_C(\delta \boldsymbol v \cdot \boldsymbol v)_{\boldsymbol x\in C_v} \\
+                     &= 0
+\end{split}
+\end{equation}
+in which $\alpha_v$, $\alpha_\theta$ and $\alpha_C$ are experimental artificial parameters.
+Further invoking the conventional reproducing kernel approximation of Eq.
+(\ref{approxv}) leads to the following discrete equilibrium equations:
+\begin{equation}
+\sum_{J=1}^{n_p}(\boldsymbol K_{IJ} + \boldsymbol K^c_{IJ} + \boldsymbol K^s_{IJ}) \boldsymbol d_J = \boldsymbol f_I + \boldsymbol f^c + \boldsymbol f^s
+\end{equation}
+where the stiffness $\boldsymbol K_{IJ}$ is identical with Eq.
+(\ref{de1}).
+$\boldsymbol K^c_{IJ}$ and $\boldsymbol K^s_{IJ}$ are the stiffness matrix for consistent and stabilized terms respectively, and have the following forms:
+\begin{subequations}
+\begin{equation}
+\begin{split}
+        \boldsymbol K^c_{IJ} &= -\int_{\Gamma_v} \left ((\boldsymbol {\mathcal T}^\alpha \Psi_{I,\alpha} + \boldsymbol{\mathcal V}^{\alpha\beta} \Psi_{I,\alpha}\vert_\beta) \Psi_J + \Psi_I (\boldsymbol {\mathcal T}^\alpha \Psi_{J,\alpha} + \boldsymbol{\mathcal V}^{\alpha\beta}\Psi_{J,\alpha}\vert_\beta)\right ) d\Gamma \\
+                             &+ \int_{\Gamma_M} (\mathcal M^{\alpha\beta} \Psi_{I,\alpha}\vert_\beta \boldsymbol a_3 \Psi_{J,\gamma}n^\gamma + \Psi_{I,\gamma}n^\gamma \boldsymbol a_3 \mathcal M^{\alpha\beta} \Psi_{I,\alpha}\vert_\beta) d\Gamma
+\end{split}
+\end{equation}
+\end{subequations}

### 2024-02-11 kinematics.tex
202402011

@@
 \subsection{Kinematics for thin shell}
+Consider the configuration of a shell $\bar \Omega$, as shown in Fig.
+\ref{}, which can be easily described by a parametric curvilinear coordinate system $\boldsymbol \xi = \{\xi^i\}_{i=1,2,3}$.
+The mid-surface of the shell is specified by the in-plane coordinates $\boldsymbol \xi = \{\xi^\alpha\}_{\alpha=1,2}$, as the thickness direction of shell is by $\xi^3$, $-\frac{h}{2} \le \xi^3 \le \frac{h}{2}$, $h$ is the thick of shell.
+In this work, Latin indices take 22 the values from 1 to 3, and Greek indices are evaluated by 1 or 2.
+For the Kirchhoff hypothesis \cite{krysl1996}, the position $\boldsymbol x\in \bar \Omega$ are defined by linear functions with respect to $\xi^3$ :
+\begin{equation}\label{x}
+\boldsymbol x(\xi^1, \xi^2, \xi^3) = \boldsymbol r(\xi^1,\xi^2) + \xi^3 \boldsymbol a_3(\xi^1,\xi^2)
+\end{equation}
+in which $\boldsymbol r$ means the position on the mid-surface of shell, and the $\boldsymbol a_3$ is corresponding normal direction.
+For the mid-surface of shell, the in-plane covariant base vector with respect to $\xi^\alpha$ can be derived by a trivial partial differentiation to $\boldsymbol r$:
+\begin{equation}
+\boldsymbol a_\alpha = \frac{\partial \boldsymbol r}{\partial \xi^\alpha} = \boldsymbol r_{,\alpha}, \alpha  = 1,2
+\end{equation}
+for a clear expression, the subscript comma denotes the partial differentiation operation with respect to in-plane coordinates $\xi^\alpha$.
+And the normal vector $\boldsymbol a_3$ can be obtained by the normalized cross product of $\boldsymbol a_{\alpha}$'s as follow:
+\begin{equation}
+\boldsymbol a_3 = \frac{\boldsymbol a_1 \times \boldsymbol a_2}{\Vert \boldsymbol a_1 \times \boldsymbol a_2 \Vert}
+\end{equation}
+where $\Vert \bullet \Vert$ is the Euclidean norm operator.
+
+With the assumption of infinitesimal deformation, the strain components respected to global contravariant base can be sated as:
+\begin{equation}\label{epsilon}
+\epsilon_{ij} = \frac{1}{2}(\boldsymbol x_{,i} \cdot \boldsymbol u_{,j} + \boldsymbol u_{,i} \cdot \boldsymbol x_{,j})
+\end{equation}
+where $\boldsymbol u$ is the displacement for shell deformation. To fulfillment with Kirchhoff hypothesis, the displacement is assumed to be the following form:
+\begin{equation}\label{u}
+\boldsymbol u(\xi^1,\xi^2,\xi^3) = \boldsymbol v(\xi^1,\xi^2) + \boldsymbol \theta(\xi^1,\xi^2) \xi^3
+\end{equation}
+in which the quadratic and higher order terms are neglected. $\boldsymbol v$, $\boldsymbol \theta$ respect the displacement and rotation in mid-surface.
+
+Subsequently, plugging Eqs. (\ref{x}) and (\ref{u}) into Eq. (\ref{epsilon}) and neglecting quadratic terms, the strain components can be rephrased as follows:
+\begin{subequations}
+\begin{align}
+\begin{split}
+\epsilon_{\alpha\beta} &= \frac{1}{2}(\boldsymbol a_\alpha \cdot \boldsymbol v_{,\beta} + \boldsymbol v_{,\alpha}\cdot \boldsymbol a_\beta) \\ 
+&+ \frac{1}{2}(\boldsymbol a_{3,\alpha} \cdot \boldsymbol v_{,\beta} + \boldsymbol v_{,\alpha}\cdot \boldsymbol a_{3,\beta} + \boldsymbol a_\alpha \cdot \boldsymbol \theta_{,\beta} + \boldsymbol \theta_{,\alpha}\cdot \boldsymbol a_\beta)\xi^3 \\
+&= \varepsilon_{\alpha\beta} + \kappa_{\alpha\beta}\xi^3
+\end{split} \\
+\epsilon_{\alpha 3} &= \frac{1}{2}(\boldsymbol a_\alpha \cdot \boldsymbol \theta + \boldsymbol v_{,\alpha}\cdot \boldsymbol a_3) + \frac{1}{2} (\boldsymbol a_3 \cdot \boldsymbol \theta)_{,\alpha}\xi^3 \\
+\epsilon_{33} &= \boldsymbol a_3 \cdot \boldsymbol \theta
+\end{align}
+\end{subequations}
+where $\varepsilon_{\alpha\beta}$, $\kappa_{\alpha\beta}$ are membrane and bending strains respectively:
+\begin{equation}
+\varepsilon_{\alpha\beta} = \frac{1}{2}(\boldsymbol a_\alpha \cdot \boldsymbol v_{,\beta} + \boldsymbol v_{,\alpha}\cdot \boldsymbol a_\beta) 
+\end{equation}
+\begin{equation}\label{kappa1}
+\kappa_{\alpha\beta} = \frac{1}{2}(\boldsymbol a_{3,\alpha} \cdot \boldsymbol v_{,\beta} + \boldsymbol v_{,\alpha}\cdot \boldsymbol a_{3,\beta} + \boldsymbol a_\alpha \cdot \boldsymbol \theta_{,\beta} + \boldsymbol \theta_{,\alpha}\cdot \boldsymbol a_\beta)
+\end{equation}
+
+In accordance with Kirchhoff hypothesis, the thickness of shell will not change and the deformation related with direction of $\xi^3$ will be vanished, i.e.
+$\epsilon_{3i}=0$.
+Thus, the rotation $\boldsymbol \theta$ can be rewritten as:
+\begin{equation}\label{a3}
+\epsilon_{3i} = 0 \Rightarrow
+\left \{
+\begin{split}
+&\boldsymbol \theta \cdot \boldsymbol a_\alpha + \boldsymbol v_{,\alpha} \cdot \boldsymbol a_3 = 0 \\
+&\boldsymbol \theta \cdot \boldsymbol a_3 = 0
+\end{split}
+\right .
+\Rightarrow \boldsymbol \theta = - \boldsymbol v_{,\alpha} \cdot \boldsymbol a_3 \boldsymbol a^\alpha
+\end{equation}
+where $\boldsymbol a^\alpha$'s are the in-plane contravariant base vectors, $\boldsymbol a^\alpha \cdot \boldsymbol a_\beta = \delta^\alpha_\beta$, $\delta$ is the Kronecker delta function.
+Substituting Eq.
+(\ref{a3}) into Eq.
+(\ref{kappa1}) leads to:
+\begin{equation}
+\kappa_{\alpha\beta} = (\Gamma^\gamma_{\alpha\beta} \boldsymbol v_{,\gamma} - \boldsymbol v_{,\alpha\beta}) \cdot \boldsymbol a_3 = - \boldsymbol v_{,\alpha}\vert_\beta \cdot \boldsymbol a_3
+\end{equation}
+in which $\Gamma^\gamma_{\alpha\beta} = \boldsymbol a_{\alpha,\beta} \cdot \boldsymbol a^\gamma$ is namely Christoffel symbol of the second kind.
 \begin{equation}

### 2024-02-11 examples.tex
20240209
temp

@@
 \section{Numerical examples}
-\begin{figure}[H]
+\begin{figure}[h!]
     \centering
@@
 \end{figure}
+
+\begin{table}[h!]
+\centering
+\caption{Results of patch test for flat model}
+\begin{tabular}{lcccc}
+\toprule
+ & \multicolumn{2}{c}{Linear patch test} & \multicolumn{2}{c}{Quadratic patch test} \\ \cline{2-5}
+ & $L_2$-Error & $H_e$-Error & $L_2$-Error & $H_e$-Error \\
+    \midrule
+    GI-Penalty & $4.45E-4$ & $1.35E-2$ & $2.01E-3$ & $1.63E-2$ \\
+    GI-Nitsche & $4.51E-4$ & $1.42E-2$ & $1.22E-3$ & $1.68E-2$ \\
+    RKGSI-Penalty & $3.64E-9$ & $6.77E-8$ & $4.54E-9$ & $6.57E-8$ \\
+    RKGSI-Nitsche & $3.31E-12$ & $1.34E-11$ & $5.98E-12$ & $1.21E-11$ \\
+    RKGSI-HR & $6.67E-13$ & $1.50E-11$ & $1.07E-12$ & $1.26E-11$ \\
+    \bottomrule
+\end{tabular}
+\end{table}
+
+\begin{table}[h!]
+\centering
+\caption{Results of patch test for curved model}
+\begin{tabular}{lcccc}
+\toprule
+ & \multicolumn{2}{c}{Linear patch test} & \multicolumn{2}{c}{Quadratic patch test} \\ \cline{2-5}
+ & $L_2$-Error & $H_e$-Error & $L_2$-Error & $H_e$-Error \\
+    \midrule
+    GI-Penalty & $3.79E-4$ & $1.30E-2$ & $1.74E-3$ & $1.37E-2$ \\
+    GI-Nitsche & $4.04E-4$ & $1.42E-2$ & $1.15E-3$ & $1.49E-2$ \\
+    RKGSI-Penalty & $3.64E-9$ & $6.77E-8$ & $4.54E-9$ & $6.57E-8$ \\
+    RKGSI-Nitsche & $3.31E-12$ & $1.34E-11$ & $5.98E-12$ & $1.21E-11$ \\
+    RKGSI-HR & $4.28E-6$ & $1.30E-4$ & $9.69E-6$ & $1.30E-4$ \\
+    \bottomrule
+\end{tabular}
+\end{table}

### 2024-02-11 frontmatter.tex
temp

\begin{frontmatter}
    \title{A principle meshfree formulation for thin shells with naturally consistent enforcement of essential boundary conditions}
    \author[1]{Junchao Wu\corref{cor1}}
    \ead{jcwu@hqu.edu.cn}
    \author[2]{Yangtao Xu}
    \author[1]{Bin Xu}
    \author[3]{Syed Humayun Basha}

    \affiliation[1]{organization={Key Laboratory for Intelligent Infrastructure and Monitoring of Fujian Province,
                                  College of Civil Engineering,
                                  Huaqiao University},
                    city={Xiamen},
                    state={Fujian},
                    postcode={361021},
                    country={China}}

    \affiliation[2]{organization={College of Civil Engineering,
                                  Huaqiao University},
                    city={Xiamen},
                    state={Fujian},
                    postcode={361021},
                    country={China}}

    \affiliation[3]{organization={Key Laboratory for Structural Engineering and Disaster Prevention of Fujian Province,
                                  College of Civil Engineering,
                                  Huaqiao University},
                    city={Xiamen},
                    state={Fujian},
                    postcode={361021},
                    country={China}}

    \cortext[cor1]{Corresponding author}

\begin{abstract}
Thin shell problems ignore the shear deformations and this leads to a requirement of C1 continuous approximations. Meshfree methods equipped with high order smoothed shape functions is suitable for thin shell analysis, since the high order shape function can also suppress the membrane locking in thin shell problems. However, meshfree shape function always perform a natural rational property, this is a big challenge to meet integration consistency for traditional Gauss integration rule within Galerkin weak form, while integration consistency serves a key role in accuracy of Galerkin meshfree methods. In this work, we proposed a reproducing kernel gradient smoothing integration (RKGSI) algorithm for thin shell problems, while the first and second order smoothed gradients are constructed based upon reproducing kernel smoothing gradient framework, with the aid of this framework, the integration consistency becomes a natural property by a replacement between smoothed gradients and traditional gradients of shape functions in Galerkin weak form. The order of basis functions used in smoothed gradient is determined by ensuring the optimal order of error convergence respected to energy norm. The traditional costly second order gradients are totally eliminated in RKGSI formulation. To further increase the efficiency of proposed method, a set of integration schemes are developed for consistent assembly of stiffness matrix, force vector and smoothed gradients, where the number of integration points, which accompanied with calculation of traditional shape functions and their first order gradients, are minimized by a global point of view. It is evident that the smoothed gradients meets the reproducing consistency of gradients that can ensure the optimal convergence property. The numerical examples demonstrate the efficacy and efficiency of proposed method, while the RKGSI performs a comparable result in energy error with interpolation by meshfree approximations.
\end{abstract}
\begin{keyword}
Meshfree \sep Thin shell \sep Hu-Washizu variational principle \sep Reproducing kernel gradient smoothing \sep Essential boundary condition
\end{keyword}
\end{frontmatter}

### 2024-02-11 kinematics.tex
temp

@@
 \ref{}, which can be easily described by a parametric curvilinear coordinate system $\boldsymbol \xi = \{\xi^i\}_{i=1,2,3}$.
-The mid-surface of the shell is specified by the in-plane coordinates $\boldsymbol \xi = \{\xi^\alpha\}_{\alpha=1,2}$, as the thickness direction of shell is by $\xi^3$, $-\frac{h}{2} \le \xi^3 \le \frac{h}{2}$, $h$ is the thick of shell.
-In this work, Latin indices take 22 the values from 1 to 3, and Greek indices are evaluated by 1 or 2.
+The mid-surface of the shell is specified by the in-plane coordinates $\boldsymbol \xi = \{\xi^\alpha\}_{\alpha=1,2}$, as the thickness direction of shell is by $\xi^3$, $-\frac{h}{2} \le \xi^3 \le \frac{h}{2}$, $h$ is the thickness of shell.
+In this work, Latin indices take the values from 1 to 3, and Greek indices are evaluated by 1 or 2.
 For the Kirchhoff hypothesis \cite{krysl1996}, the position $\boldsymbol x\in \bar \Omega$ are defined by linear functions with respect to $\xi^3$ :
@@
 in which $\Gamma^\gamma_{\alpha\beta} = \boldsymbol a_{\alpha,\beta} \cdot \boldsymbol a^\gamma$ is namely Christoffel symbol of the second kind.
-\begin{equation}
-\varepsilon_{\alpha\beta} = \frac{1}{2}(\boldsymbol a_\alpha \cdot \boldsymbol v_{,\beta} + \boldsymbol a_\beta \cdot \boldsymbol v_{,\alpha})
-\end{equation}
-
-\begin{equation}
-\theta_{\boldsymbol n} = \boldsymbol a_3 \cdot \boldsymbol v_{,\alpha} n^\alpha
-\end{equation}
-
-\begin{equation}
-\kappa_{\alpha\beta} = (\Gamma^\gamma_{\alpha\beta} \boldsymbol v_{,\gamma} - \boldsymbol v_{,\alpha\beta}) \cdot \boldsymbol a_3 = - \boldsymbol v_{,\alpha}\vert_\beta \cdot \boldsymbol a_3
-\end{equation}
-
-\begin{equation}
-\boldsymbol t = \boldsymbol t_N + \boldsymbol t_M
-\end{equation}
-
-\begin{equation}
-\boldsymbol t_N = \boldsymbol a_\alpha N^{\alpha\beta} n_\beta
-\end{equation}
-
-\begin{equation}
-\boldsymbol t_M = (\boldsymbol a_3 M^{\alpha\beta})\vert_\beta n_\alpha + (\boldsymbol a_3 M^{\alpha\beta} s_\alpha n_\beta)_{,\gamma} s^\gamma
-\end{equation}
-
-\begin{equation}
-M_{\boldsymbol{nn}} = M^{\alpha\beta}n_\alpha n_\beta
-\end{equation}
-
-\begin{equation}
-\boldsymbol b = \boldsymbol b_N + \boldsymbol b_M
-\end{equation}
-
-\begin{equation}
-\boldsymbol b_N = (\boldsymbol a_\alpha N^{\alpha\beta})\vert_\beta
-\end{equation}
-
-\begin{equation}
-\boldsymbol b_M = (\boldsymbol a_3 M^{\alpha\beta})_{,\alpha}\vert_\beta
-\end{equation}
-
-\begin{equation}
-P = -[[M^{\alpha\beta}s_\alpha n_\beta]]
-\end{equation}
-
-\subsection{Galerkin weak form for Hu-Washizu principle of complementary energy}
-In accordance with the Hu-Washizu variational principle of complementary energy \cite{dah-wei1985}, the corresponding complementary functional, denoted by $\Pi$, is listed as follow:
-\begin{equation} \label{functional}
-\begin{split}
-&\Pi(\boldsymbol v, \varepsilon_{\alpha\beta},\kappa_{\alpha\beta},N^{\alpha\beta},M^{\alpha\beta}) \\
-= &\int_\Omega \frac{h}{2}\varepsilon_{\alpha\beta} C^{\alpha\beta\gamma\eta}\varepsilon_{\gamma\eta}d\Omega 
-+ \int_\Omega \frac{h^3}{24}\kappa_{\alpha\beta} C^{\alpha\beta\gamma\eta}\kappa_{\gamma\eta}d\Omega \\
-+& \int_\Omega \varepsilon_{\alpha\beta} (N^{\alpha\beta} - h C^{\alpha\beta\gamma\eta} \varepsilon_{\gamma\eta}) d\Omega
-+ \int_\Omega \kappa_{\alpha\beta} (M^{\alpha\beta} - \frac{h^3}{12} C^{\alpha\beta\gamma\eta} \kappa_{\gamma\eta}) d\Omega \\
--& \int_{\Gamma_v} \boldsymbol t \cdot \bar{\boldsymbol v} d\Gamma 
-+ \int_{\Gamma_\theta} M_{\boldsymbol{nn}} \bar \theta_{\boldsymbol n} d\Gamma - (P \boldsymbol a_3 \cdot \bar{\boldsymbol v})_{\boldsymbol x \in C_w} \\
-+ &\int_{\Gamma_M} \theta_{\boldsymbol n} (M_{\boldsymbol{nn}} - \bar M_{\boldsymbol{nn}}) d\Gamma
-- \int_{\Gamma_t} \boldsymbol v \cdot (\boldsymbol t - \bar{\boldsymbol t})d\Gamma - \boldsymbol v \cdot \boldsymbol a_3 (P - \bar{P})_{\boldsymbol x \in C_P} \\
-- &\int_\Omega \boldsymbol v \cdot (\boldsymbol b - \bar{\boldsymbol b}) d\Omega \\
-\end{split}
-\end{equation}
-Introducing a standard variational argument to Eq.
-(\ref{functional}), $\delta \Pi=0$, and considering the arbitrariness of virtual variables, $\delta \boldsymbol v$, $\delta \varepsilon_{\alpha\beta}$, $\delta \kappa_{\alpha\beta}$, $N^{\alpha\beta}$, $M^{\alpha\beta}$ lead to the following weak form:
-\begin{subequations}
-\begin{equation}\label{w1}
-- \int_\Omega h \delta \varepsilon_{\alpha\beta} C^{\alpha\beta\gamma\eta}\varepsilon_{\gamma\eta}d\Omega 
-+ \int_\Omega \delta \varepsilon_{\alpha\beta} N^{\alpha\beta} d\Omega = 0
-\end{equation}
-\begin{equation}\label{w2}
-- \int_\Omega \frac{h^3}{12} \delta \kappa_{\alpha\beta} C^{\alpha\beta\gamma\eta}\kappa_{\gamma\eta}d\Omega 
-+ \int_\Omega \delta \kappa_{\alpha\beta} M^{\alpha\beta} d\Omega = 0
-\end{equation}
-\begin{multline}\label{w3}
-\int_\Omega \delta N^{\alpha\beta} \varepsilon_{\alpha\beta} d\Omega
-- \int_\Gamma \delta \boldsymbol t_N \cdot \boldsymbol v d\Gamma 
-+ \int_\Omega \delta \boldsymbol b_N \cdot \boldsymbol v d\Omega \\
-+ \int_{\Gamma_v} \delta \boldsymbol t_N \cdot \boldsymbol v d\Gamma 
-= \int_{\Gamma_v} \delta \boldsymbol t_N \cdot \bar{\boldsymbol v} d\Gamma 
-\end{multline}
-\begin{multline}\label{w4}
-\int_\Omega \delta M^{\alpha\beta} \kappa_{\alpha\beta} d\Omega 
-- \int_\Gamma \delta M_{\boldsymbol{nn}} \theta_{\boldsymbol n}d\Gamma
-+ \int_\Gamma \delta \boldsymbol t_M \cdot \boldsymbol v d\Gamma
-+ (\delta P \boldsymbol a_3 \cdot \boldsymbol v)_{\boldsymbol x \in C}
-+ \int_\Omega \delta \boldsymbol b_M \cdot \boldsymbol v d\Omega \\
-+ \int_{\Gamma_\theta} \delta M_{\boldsymbol{nn}} \theta_{\boldsymbol n}d\Gamma
-- \int_{\Gamma_v} \delta \boldsymbol t_M \cdot \boldsymbol v d\Gamma
-- (\delta P \boldsymbol a_3 \cdot \boldsymbol v)_{\boldsymbol x \in C_v} \\ =
-\int_{\Gamma_\theta} \delta M_{\boldsymbol{nn}} \bar{\theta}_{\boldsymbol n}d\Gamma
-- \int_{\Gamma_v} \delta \boldsymbol t_M \cdot \bar{\boldsymbol v} d\Gamma
-- (\delta P \boldsymbol a_3 \cdot \bar{\boldsymbol v})_{\boldsymbol x \in C_v} \\
-\end{multline}
-\begin{multline}\label{w5}
-\int_{\Gamma} \delta \theta_{\boldsymbol n} M_{\boldsymbol{nn}} d\Gamma
-    - \int_\Gamma \delta \boldsymbol v \cdot \boldsymbol t d\Gamma 
-    - (\delta \boldsymbol v \cdot \boldsymbol a_3 P)_{\boldsymbol x \in C}
-    + \int_\Omega \delta \boldsymbol v \cdot \boldsymbol b d\Omega \\
-    - \int_{\Gamma_\theta} \delta \theta_{\boldsymbol n} M_{\boldsymbol{nn}} d\Gamma
-    + \int_{\Gamma_v} \delta \boldsymbol v \cdot \boldsymbol t d\Gamma 
-    + (\delta \boldsymbol v \cdot \boldsymbol a_3 P)_{\boldsymbol x \in C_v}
-    = - \int_{\Gamma_t} \delta \boldsymbol v \cdot \bar{\boldsymbol t} d\Gamma - \int_\Omega \delta \boldsymbol v \cdot \bar{\boldsymbol b} d\Omega
-\end{multline}
-\end{subequations}
-where the geometric relationships of Eq. () is used herein.

### 2024-02-12 examples.tex
temp

@@
 \section{Numerical examples}
+In this section, several examples are carried out to verify proposed method, which employs the consistent reproducing kernel gradient smoothing integration scheme (RKGSI) and the non-consistent Gauss integration scheme (GI) with penalty method, Nitsche's method and the proposed Hu-Washizu formulation (HW) to enforce the essential boundary conditions.
+A normalized support size of 2.5 is used for all methods to ensure the requirement of quadratic base meshfree approximation.
+To eliminate the influence of integration, the Gauss integration scheme use 6 Gauss points for domain integration and 3 points for boundary integration, and such that the number of integration points are identical between Gauss scheme and RKGSI scheme.
+The error estimates of displacement namely $L_2$-Error and energy namely $H_e$-Error is used here:
+\begin{equation}
+\begin{split}
+L_2\text{-Error} &= \frac{\sqrt{\int_\Omega(\boldsymbol v - \boldsymbol v^h) \cdot (\boldsymbol v - \boldsymbol v^h)d\Omega}}{\sqrt{\boldsymbol v \cdot \boldsymbol v}} \\
+H_e\text{-Error} &= \frac{\sqrt{\int_\Omega \left ((\varepsilon_{\alpha\beta} - \varepsilon_{\alpha\beta}^h)(N^{\alpha\beta} - N^{\alpha\beta h}) + \int_\Omega(\kappa_{\alpha\beta}-\kappa_{\alpha\beta}^h)(M^{\alpha\beta}-M^{\alpha\beta h}) \right )d\Omega}}{\sqrt{\int_\Omega(\varepsilon_{\alpha\beta}N^{\alpha\beta} + \kappa_{\alpha\beta}M^{\alpha\beta})d\Omega}}
+\end{split}
+\end{equation}
+
+\subsection{Patch tests}
+The linear and quadratic patch tests for flat and curved thin shell are firstly study to verify the variational consistency of the proposed method.
+As shown in Fig.
+\ref{ptf1}, the flat and curved model is depicted by an identical parametric domain $\Omega = (0,1)\otimes(0,1)$, where the cylindrical coordinate system with radius $R=1$ is employed to describe the curved model, and the whole domain $\Omega$ is discretized by $165$ meshfree nodes.
+All the boundaries are enforced as essential boundary conditions with the following manufactured exact solution:
+\begin{equation}
+\boldsymbol v = \begin{Bmatrix}
+(\xi^1+2\xi^2)^n \\ (3\xi^1+4\xi^2)^n \\ (5\xi^1+6\xi^2)^n
+\end{Bmatrix},\quad
+n = \begin{cases}
+1 & \text{Linear patch test} \\
+2 & \text{Quadratic patch test}
+\end{cases}
+\end{equation}
+
 \begin{figure}[h!]
@@
     \includegraphics[width=\textwidth]{figures/patchtest_msh}
-    \caption{Meshfree discretization for patch test}
+    \caption{Meshfree discretization for patch test}\label{ptf1}
+\end{figure}
 
-\end{figure}
+Table \ref{ptt1} lists the $L_2$- and $H_e$-Error results of patch test with flat model, where the RKGSI with variational consistent essential boundary enforcement, i.e.
+RKGSI-Nitsche and RKGSI-HW, can pass the linear and quadratic path test.
+Due to the loss of variational consistency condition, even with Nitsche's method, Gauss meshfree formulations show noticeable errors.
+Table \ref{ptt2} shows the results for curved model, which indicated that all the mehtods cannot pass the patch test, which mainly because the proposed smoothed gradient of Eqs.
+(\ref{approxse1}), (\ref{approxse2}) is unable to exactly reproduce the non-polynomial membrane and bending stress.
+However, the RKGSI-HW and RKGSI-Nitsche also performance better accuracy than other methods due to the fulfillment of first two order variational consistency.
+Meanwhile, the bending moment contours of $M^{12}$ are listed in Fig.
+\ref{ptf2}, which further verify that the proposed method obtain a satisfactory result comparing with exact solution, the conventional Gauss meshree formulations show observable errors.
 
@@
 \centering
-\caption{Results of patch test for flat model}
+\caption{Results of patch test for flat model}\label{ptt1}
 \begin{tabular}{lcccc}
@@
 \centering
-\caption{Results of patch test for curved model}
+\caption{Results of patch test for curved model.}\label{ptt2}
 \begin{tabular}{lcccc}
@@
     GI-Nitsche & $4.04E-4$ & $1.42E-2$ & $1.15E-3$ & $1.49E-2$ \\
-    RKGSI-Penalty & $3.64E-9$ & $6.77E-8$ & $4.54E-9$ & $6.57E-8$ \\
-    RKGSI-Nitsche & $3.31E-12$ & $1.34E-11$ & $5.98E-12$ & $1.21E-11$ \\
-    RKGSI-HR & $4.28E-6$ & $1.30E-4$ & $9.69E-6$ & $1.30E-4$ \\
+    RKGSI-Penalty & $1.47E-4$ & $5.39E-3$ & $2.26E-4$ & $2.09E-3$ \\
+    RKGSI-Nitsche & $2.41E-6$ & $7.37E-5$ & $2.47E-6$ & $2.89E-5$ \\
+    RKGSI-HR & $4.28E-6$ & $1.30E-4$ & $9.69E-6$ & $2.41E-4$ \\
     \bottomrule
@@
 \end{table}
+
+\begin{figure}[h!]
+\centering
+\includegraphics[width=\textwidth]{figures/patchtest_msh}
+\caption{Contour plots of $M^{12}$ for curved shell patch test.}\label{ptf2}
+\end{figure}
+
+\subsection{Scordelis-Lo roof}
+This example consider the classical Scordelis-Lo roof problem, as shown in Fig., the cylindrical roof has the radius $R=25$, length $L=50$, thickness $h=0.25$, Young's modulus $E=4.32\times 10^8$ and Poisson rate $\nu=0.0$.
+An uniform body force of $b_z = -90$ are enforced in whole roof and the curved edges are enforced by $v_x=v_z=0$, and the straight edges are free.
+
+Due to the symmetry, only a quadrant of the model is considered for meshfree analysis, which is discretized by the $5\times 8$, $11\times 16$, $17\times 24$ and $23\times32$ meshfree nodes.
+
+\begin{figure}[h!]
+\centering
+\includegraphics[width=\textwidth]{figures/patchtest_msh}
+\caption{Description of Scordelis-Lo roof problem.}\label{ptf2}
+\end{figure}

### 2024-02-12 kinematics.tex
202402012

@@
 \ref{}, which can be easily described by a parametric curvilinear coordinate system $\boldsymbol \xi = \{\xi^i\}_{i=1,2,3}$.
-The mid-surface of the shell is specified by the in-plane coordinates $\boldsymbol \xi = \{\xi^\alpha\}_{\alpha=1,2}$, as the thickness direction of shell is by $\xi^3$, $-\frac{h}{2} \le \xi^3 \le \frac{h}{2}$, $h$ is the thickness of shell.
+The mid-surface of the shell denoted by $\Omega$ is specified by the in-plane coordinates $\boldsymbol \xi = \{\xi^\alpha\}_{\alpha=1,2}$, as the thickness direction of shell is by $\xi^3$, $-\frac{h}{2} \le \xi^3 \le \frac{h}{2}$, $h$ is the thickness of shell.
 In this work, Latin indices take the values from 1 to 3, and Greek indices are evaluated by 1 or 2.
@@
 in which $\Gamma^\gamma_{\alpha\beta} = \boldsymbol a_{\alpha,\beta} \cdot \boldsymbol a^\gamma$ is namely Christoffel symbol of the second kind.
+And $\boldsymbol v_{,\alpha}\vet$ is the in-plane covariant derivative of $\boldsymbol v_{,\alpha}$, i.e.
+$\boldsymbol v_{,\alpha}\vert_\beta = \Gamma^\gamma_{\alpha\beta}\boldsymbol v_{,\gamma} - \boldsymbol v_{,\alpha\beta}$.
+
+\subsection{Galerkin weak form for Hu-Washizu principle of complementary energy}
+In this study, the Hu-Washizu variational principle of complementary energy \cite{dah-wei1985} is used herein for development of this method, the corresponding complementary functional, denoted by $\Pi_C$, is listed as follow:
+\begin{equation} \label{functionalc}
+\begin{split}
+&\Pi_C(\varepsilon_{\alpha\beta},\kappa_{\alpha\beta},N^{\alpha\beta},M^{\alpha\beta}) \\
+= &\int_\Omega \frac{h}{2}\varepsilon_{\alpha\beta} C^{\alpha\beta\gamma\eta}\varepsilon_{\gamma\eta}d\Omega 
++ \int_\Omega \frac{h^3}{24}\kappa_{\alpha\beta} C^{\alpha\beta\gamma\eta}\kappa_{\gamma\eta}d\Omega \\
++& \int_\Omega \varepsilon_{\alpha\beta} (N^{\alpha\beta} - h C^{\alpha\beta\gamma\eta} \varepsilon_{\gamma\eta}) d\Omega
++ \int_\Omega \kappa_{\alpha\beta} (M^{\alpha\beta} - \frac{h^3}{12} C^{\alpha\beta\gamma\eta} \kappa_{\gamma\eta}) d\Omega \\
+-& \int_{\Gamma_v} \boldsymbol T \cdot \bar{\boldsymbol v} d\Gamma 
++ \int_{\Gamma_\theta} M_{\boldsymbol{nn}} \bar \theta_{\boldsymbol n} d\Gamma - (P \boldsymbol a_3 \cdot \bar{\boldsymbol v})_{\boldsymbol x \in C_w} \\
+\end{split}
+\end{equation}
+where $C^{\alpha\beta\gamma\eta}$'s are the components of fourth order elasticity tensor with respect to covariant base and plane stress assumption, and it can be expressed by Young's modulus $E$, Poisson rate $\nu$ and the in-plane contravariant metric coefficients $a^{\alpha\beta}$'s, $a^{\alpha\beta} = \boldsymbol a^\alpha \cdot \boldsymbol a^\beta$, as follow:
+\begin{equation}
+C^{\alpha\beta\gamma\eta} = \frac{E}{2(1+\nu)}(a^{\alpha\gamma}a^{\beta\eta} + a^{\alpha\eta}a^{\beta\gamma} + \frac{2\nu}{1-\nu} a^{\alpha\beta}a^{\gamma\eta})
+\end{equation}
+and $N^{\alpha\beta}$, $M^{\alpha\beta}$ are the components of membrane and bending stresses given by:
+\begin{equation}
+N^{\alpha\beta} = hC^{\alpha\beta\gamma\eta}\varepsilon_{\gamma\eta}, \quad
+M^{\alpha\beta} = \frac{h^3}{12}C^{\alpha\beta\gamma\eta}\kappa_{\gamma\eta}
+\end{equation}
+
+Essential boundaries on the edges and corners denoted by $\Gamma_v$, $\Gamma_\theta$ and $C_v$ are naturally existed in complementary energy functional, $\bar{\boldsymbol v}$, $\bar \theta_{\boldsymbol n}$ are the corresponding prescribed displacement and normal rotation.
+$\boldsymbol T$, $M_{\bodlsymbol{nn}}$ and $P$ can be determined by Euler-Lagrange equations of shell problem \cite{benzaken2021} as follows:
+\begin{equation}
+\boldsymbol T = \boldsymbol T_N + \boldsymbol T_M \; \rightarrow
+\begin{cases}
+\boldsymbol T_N = \boldsymbol a_\alpha N^{\alpha\beta}n_\beta \\
+\boldsymbol T_M = (\boldsymbol a_3 M^{\alpha\beta}s_\alpha n_\beta)_{,\gamma} s^\gamma
++ (\boldsymbol a_3 M^{\alpha\beta})\vert_\beta n_\alpha
+\end{cases}
+\end{equation}
+\begin{equation}
+M_{\boldsymbol{nn}} = M^{\alpha\beta}n_\alpha n_\beta
+\end{equation}
+\begin{equation}
+P = -[[M^{\alpha\beta}s_\alpha n_\beta]]
+\end{equation}
+where $\boldsymbol n = n^\alpha \boldsymbol a_\alpha = n_\alpha \boldsymbol a^\alpha$ and $\boldsymbol s = s^\alpha \boldsymbol a_\alpha = s_\alpha \boldsymbol a^\alpha$ are the outward normal and tangent directions on boundaries.
+$[[f]]$ is the jump operator defined by:
+\begin{equation}
+[[f]]_{\boldsymbol x = \boldsymbol x_c} = \lim_{\boldsymbol \epsilon\rightarrow \boldsymbol 0+}(f(\boldsymbol x_c + \boldsymbol \epsilon) - f(\boldsymbol x_c - \boldsymbol \epsilon)), \boldsymbol x_c \in \Gamma
+\end{equation}
+where $f$ is an arbitrary function on $\Gamma$.
+
+Moreover, the natural boundary conditions should be applied by Lagrangian multiplier method with displacement $\boldsymbol v$ regarded as multiplier.
+Thus then the new complementary energy functional namely $\Pi$ is given by:
+\begin{equation} \label{functional}
+\begin{split}
+&\Pi(\boldsymbol v, \varepsilon_{\alpha\beta},\kappa_{\alpha\beta},N^{\alpha\beta},M^{\alpha\beta}) \\
+=&\Pi_C(\varepsilon_{\alpha\beta},\kappa_{\alpha\beta},N^{\alpha\beta},M^{\alpha\beta})
++ \int_{\Gamma_M} \theta_{\boldsymbol n} (M_{\boldsymbol{nn}} - \bar M_{\boldsymbol{nn}}) d\Gamma \\
+- &\int_{\Gamma_T} \boldsymbol v \cdot (\boldsymbol T - \bar{\boldsymbol T})d\Gamma - \boldsymbol v \cdot \boldsymbol a_3 (P - \bar{P})_{\boldsymbol x \in C_P}
+- \int_\Omega \boldsymbol v \cdot (\boldsymbol b - \bar{\boldsymbol b}) d\Omega 
+\end{split}
+\end{equation}
+where $\bar{\boldsymbol T}$, $\bar M_{\boldsymbol nn}$ and $\bar P$ are the corresponding prescribed traction, bending moment and concentrated force on edges $\Gamma_T$, $\Gamma_M$ and corner $C_P$ respectively.
+All the boundaries meet the following geometric relationships:
+\begin{equation}\label{geo}
+\begin{cases}
+\Gamma=\Gamma_v \cup \Gamma_T \cup \Gamma_\theta \cup \Gamma_M, \quad C = C_v \cup C_P, \\
+\Gamma_v \cap \Gamma_T = \Gamma_\theta \cap \Gamma_M = C_v \cap C_P = \varnothing
+\end{cases}
+\end{equation}
+and $\bar{\boldsymbol b}$ stands for the prescribed body force in $\Omega$, $\boldsymbol b$ also can be given based upon Euler-Lagrange equations \cite{benzaken2021} as:
+\begin{equation}
+\boldsymbol b = \boldsymbol b_N + \boldsymbol b_M \rightarrow
+\begin{cases}
+\boldsymbol b_N = (\boldsymbol a_\alpha N^{\alpha\beta})\vert_\beta \\
+\boldsymbol b_M = (\boldsymbol a_3 M^{\alpha\beta})\vert_{\alpha\beta}
+\end{cases}
+\end{equation}
+
+Introducing a standard variational argument to Eq.
+(\ref{functional}), $\delta \Pi=0$, and considering the arbitrariness of virtual variables, $\delta \boldsymbol v$, $\delta \varepsilon_{\alpha\beta}$, $\delta \kappa_{\alpha\beta}$, $N^{\alpha\beta}$, $M^{\alpha\beta}$ lead to the following weak form:
+\begin{subequations}
+\begin{equation}\label{w1}
+- \int_\Omega h \delta \varepsilon_{\alpha\beta} C^{\alpha\beta\gamma\eta}\varepsilon_{\gamma\eta}d\Omega 
++ \int_\Omega \delta \varepsilon_{\alpha\beta} N^{\alpha\beta} d\Omega = 0
+\end{equation}
+\begin{equation}\label{w2}
+- \int_\Omega \frac{h^3}{12} \delta \kappa_{\alpha\beta} C^{\alpha\beta\gamma\eta}\kappa_{\gamma\eta}d\Omega 
++ \int_\Omega \delta \kappa_{\alpha\beta} M^{\alpha\beta} d\Omega = 0
+\end{equation}
+\begin{multline}\label{w3}
+\int_\Omega \delta N^{\alpha\beta} \varepsilon_{\alpha\beta} d\Omega
+- \int_\Gamma \delta \boldsymbol T_N \cdot \boldsymbol v d\Gamma 
++ \int_\Omega \delta \boldsymbol b_N \cdot \boldsymbol v d\Omega \\
++ \int_{\Gamma_v} \delta \boldsymbol T_N \cdot \boldsymbol v d\Gamma 
+= \int_{\Gamma_v} \delta \boldsymbol T_N \cdot \bar{\boldsymbol v} d\Gamma 
+\end{multline}
+\begin{multline}\label{w4}
+\int_\Omega \delta M^{\alpha\beta} \kappa_{\alpha\beta} d\Omega 
+- \int_\Gamma \delta M_{\boldsymbol{nn}} \theta_{\boldsymbol n}d\Gamma
++ \int_\Gamma \delta \boldsymbol T_M \cdot \boldsymbol v d\Gamma
++ (\delta P \boldsymbol a_3 \cdot \boldsymbol v)_{\boldsymbol x \in C}
++ \int_\Omega \delta \boldsymbol b_M \cdot \boldsymbol v d\Omega \\
++ \int_{\Gamma_\theta} \delta M_{\boldsymbol{nn}} \theta_{\boldsymbol n}d\Gamma
+- \int_{\Gamma_v} \delta \boldsymbol T_M \cdot \boldsymbol v d\Gamma
+- (\delta P \boldsymbol a_3 \cdot \boldsymbol v)_{\boldsymbol x \in C_v} \\ =
+\int_{\Gamma_\theta} \delta M_{\boldsymbol{nn}} \bar{\theta}_{\boldsymbol n}d\Gamma
+- \int_{\Gamma_v} \delta \boldsymbol T_M \cdot \bar{\boldsymbol v} d\Gamma
+- (\delta P \boldsymbol a_3 \cdot \bar{\boldsymbol v})_{\boldsymbol x \in C_v} \\
+\end{multline}
+\begin{multline}\label{w5}
+\int_{\Gamma} \delta \theta_{\boldsymbol n} M_{\boldsymbol{nn}} d\Gamma
+    - \int_\Gamma \delta \boldsymbol v \cdot \boldsymbol T d\Gamma 
+    - (\delta \boldsymbol v \cdot \boldsymbol a_3 P)_{\boldsymbol x \in C}
+    + \int_\Omega \delta \boldsymbol v \cdot \boldsymbol b d\Omega \\
+    - \int_{\Gamma_\theta} \delta \theta_{\boldsymbol n} M_{\boldsymbol{nn}} d\Gamma
+    + \int_{\Gamma_v} \delta \boldsymbol v \cdot \boldsymbol T d\Gamma 
+    + (\delta \boldsymbol v \cdot \boldsymbol a_3 P)_{\boldsymbol x \in C_v}
+    = - \int_{\Gamma_T} \delta \boldsymbol v \cdot \bar{\boldsymbol t} d\Gamma - \int_\Omega \delta \boldsymbol v \cdot \bar{\boldsymbol b} d\Omega
+\end{multline}
+\end{subequations}
+where the geometric relationships of Eq. (\ref{geo}) is used herein.

### 2024-02-13 examples.tex
turn light

@@
-\section{Numerical examples}
+\section{Numerical examples}\label{examples}
 In this section, several examples are carried out to verify proposed method, which employs the consistent reproducing kernel gradient smoothing integration scheme (RKGSI) and the non-consistent Gauss integration scheme (GI) with penalty method, Nitsche's method and the proposed Hu-Washizu formulation (HW) to enforce the essential boundary conditions.

### 2024-02-13 frontmatter.tex
turn light

@@
 \begin{frontmatter}
-    \title{A principle meshfree formulation for thin shells with naturally consistent enforcement of essential boundary conditions}
+    \title{A Hu-Washizu variational consistent meshfree thin shell formulation with naturally accommodating essential boundary conditions}
     \author[1]{Junchao Wu\corref{cor1}}
@@
 \begin{abstract}
-Thin shell problems ignore the shear deformations and this leads to a requirement of C1 continuous approximations.
-Meshfree methods equipped with high order smoothed shape functions is suitable for thin shell analysis, since the high order shape function can also suppress the membrane locking in thin shell problems.
-However, meshfree shape function always perform a natural rational property, this is a big challenge to meet integration consistency for traditional Gauss integration rule within Galerkin weak form, while integration consistency serves a key role in accuracy of Galerkin meshfree methods.
-In this work, we proposed a reproducing kernel gradient smoothing integration (RKGSI) algorithm for thin shell problems, while the first and second order smoothed gradients are constructed based upon reproducing kernel smoothing gradient framework, with the aid of this framework, the integration consistency becomes a natural property by a replacement between smoothed gradients and traditional gradients of shape functions in Galerkin weak form.
-The order of basis functions used in smoothed gradient is determined by ensuring the optimal order of error convergence respected to energy norm.
-The traditional costly second order gradients are totally eliminated in RKGSI formulation.
-To further increase the efficiency of proposed method, a set of integration schemes are developed for consistent assembly of stiffness matrix, force vector and smoothed gradients, where the number of integration points, which accompanied with calculation of traditional shape functions and their first order gradients, are minimized by a global point of view.
-It is evident that the smoothed gradients meets the reproducing consistency of gradients that can ensure the optimal convergence property.
+A Hu-Washizu principle based variational consistent meshfree formulation with naturally enforcement of essential boundary conditions is proposed for thin shell analysis.
+In this approach, a mixed formulation of displacements, strains and stresses within the framework of Hu-Washizu variational principle is employed, where the displacements are discretized by meshfree shape functions, the strains and stresses are expressed as the smoothed gradients and covariant smoothed gradients which meet the first two order integration constraint and have the quasi- varational consistency.
 The numerical examples demonstrate the efficacy and efficiency of proposed method, while the RKGSI performs a comparable result in energy error with interpolation by meshfree approximations.

### 2024-02-13 introduction.tex
turn light

@@
-\section{Introduction}
-Thin shell is one of the most frequently used structure in engineering practice, where the thickness of this kind structure is often much smaller than its radius.
-With the Kirchhoff-Love hypothesis [1–3], the transverse shear deformation is eliminated in thin shell analysis, such that at least C1 continuous shape functions are required within Galerkin methods.
-In static and dynamic simulation of structure, the conventional finite element methods [1,2] are one of the most popular approximation scheme, however the construction of C1 continuity is still a big challenge for cell-based finite element methods.
-In last three decades, the meshfree methods [1–3] equipped high order smoothed shape functions have attracted significant research attention, while the meshfree shape functions are established based upon a set of scattered nodes and the high order continuity of shape functions is easily fulfilled even with low order basis function.
-For thin shell analysis, this high order meshfree approximations can also alleviate the membrane locking caused by the mismatched approximation order of membrane strain and bending strain [1].
+\section{Introduction}\label{introduction}
+Thin shell structure follows the Kirchhoff hypothesis that neglects the shear deformation \cite{donnell1976}, which requires the approximation should have at least $C^1$ continuity in Galerkin formulations.
+The traditional finite element methods usually only has $C^0$ continuous shape functions, and it more prefers Mindlin thick shear theory, hybrid and mixed models in simulation of shell structure \cite{hughes2000}.
+In last three decades, the meshfree methods \cite{belytschko1994, liu1995, chen2017a} equipped high order smoothed shape functions have attracted significant research attention, while the meshfree shape functions are established based upon a set of scattered nodes and the high order continuity of shape functions is easily fulfilled even with low order basis function.
+For thin shell analysis, this high order meshfree approximations can also alleviate the membrane locking caused by the mismatched approximation order of membrane strain and bending strain \cite{krysl1996}.
 Moreover, in general, the nodal-based meshfree approximations can release the burden of mesh distortion and have the flexibility of local refinement.
 Due to these advantages, a wide variety meshfree methods are proposed and have been applied to many scientific or engineering fields. 
-Among of them, moving least squares (MLS) and reproducing kernel (RK) meshfree approximations built their shape functions by enforcing the so-call consistency conditions, where the consistency conditions require that the corresponding approximations should exactly reproduce every functions spanned by basis functions, and this conditions usually serve as a basic requirement for the error convergence of resolved Galerkin solutions [1].
-However, the high order smoothed meshfree shape functions accompany with the severely overlapping supports, which leads to a misalignment between numerical integration domains and supports of shape functions.
-As a result, the meshfree shape functions usually exhibit a piecewise rational nature in each integration domains, and it brings a serious difficulty to the accurate numerical integration in Galerkin weak forms [1].
+However, the high order smoothed meshfree shape functions accompany with the enlarged and overlapping supports, which may also leads to many issues for shape functions.
+One is the loss of Kronecker delta property \cite{fernandez-mendez2004}, which leads to that the essential boundary conditions cannot be enforced directly like finite element methods.
+Another issue is that the variational consistency or said integration constraint cannot be satisfied, which is caused by the misalignment between numerical integration domains and supports of shape functions, and the shape functions exhibit a piecewise rational nature in each integration domains.
+Variational consistency is of importance to the solution accuracy in Galerkin formulations \cite{wu2021}.
+
+To directly enforce the essential boundary for Galerkin meshfree methods, several approaches have been proposed for the recovery of shape functions' Kronecker property.
+For examples, interpolation element-free method \cite{liu2019a}, mixed transformation method \cite{chen2000a}, boundary singular kernel method \cite{chen2000a} etc.
+However, these methods are not based on a variational setting, and cannot guarantee the variational consistency, enforcing accuracy may be worse on where there is no meshfree node.
+In contrast, enforcing the essential boundary conditions by a variational approach are more preferred for Galerkin meshfree methods.
+Belytschko et al.
+\cite{belytschko1994, krysl1996} firstly introduced the variational consistent Lagrange multiplier method to Galerkin meshfree method, in which the extra degrees of freedom should be employed for discretion of Lagrange multiplier.
+And this method has been extended to geometrically nonlinear thin shells by Ivannikov et al.
+\cite{ivannikov2014a}.
+To eliminate the extra degrees of freedom, Lu et al.
+\cite{lu1994} represented the Lagrange multiplier by corresponding tractions and proposed the modified variational essential boundary enforcement method.
+However, the coercivity of this approach is not always ensured and potentially reduces the accuracy.
+Zhu and Atluri \cite{zhu1998} pioneered the penalty method for meshfree method, making it straightforward approach for enforcing essential boundary conditions via Galerkin weak form.
+However, penalty method suffers from a lack of variational consistency, and requires the experimental artificial parameters, whose optimal value is hard to be determined.
+Fernández-Méndez and Huerta \cite{fernandez-mendez2004} used the Nitsche's method in meshfree formulation for imposing essential boundary conditions.
+This method can be viewed as a hybrid of modified variational method and penalty method, since its consistent term that ensure variational consistency generated by modified variational method, and the penalty method is employed as stabilized term to recovery the coercivity.
+Skatulla and Sansour \cite{skatulla2008} further extended Nitsche's method for thin shell analysis and proposed an iteration algorithm to determine artificial parameters at each integration points.
+
+To address the issue of numerical integration, a serial of consistent integration scheme has been developed for Galerkin meshfree methods.
+For instance, stabilized conforming nodal integration \cite{chen2001}, variational consistent integration \cite{chen2013}, quadratic consistent integration \cite{duan2012}, reproducing kernel gradient smoothing integration \cite{wang2019d}, consistent projection integration \cite{wang2023} etc.
+The most consistent integration scheme is established by assumed strain approach, while the costly higher order derivatives of traditional meshfree shape functions are replaced by smoothed gradient, and show a high efficiency.
+Moreover, in order to achieve the global variational consistency, a consistent essential boundary condition enforcement should cooperate with the consistent integration scheme. 
+The pair of consistent integration scheme and Nitsche's method for the treatment of essential boundary conditions shows a good performance, since it no needs the extra degrees of freedom and can fulfilled the coercivity.
+However,in Nitsche's method, the artificial parameters still exist in stabilized term and the costly higher order derivatives should be recalled, especially for thin plate and thin shell problems \cite{benzaken2021}.
+Recently, Wu et al \cite{wu2022b, wu2023} proposed a efficient and stabilized essential boundary condition enforcement based upon the Hellinger-Reissner (HR) variational principle, where the reproducing kernel gradient smoothing integration is recast by a mixed formulation in Hellinger-Reissner weak form.
+The terms for enforcing essential boundary conditions is mostly identical with Nitsche's method, both have consistent term and stabilized term.
+Nevertheless, the stabilized term of this method naturally exist in Hellinger-Reissner weak form and no longer needs the artificial parameters, even for essential boundary enforcement, total of the higher order derivatives are represented by smoothed gradients and their derivatives.
+
+In this study, an efficient and stabilized variational consistent meshfree method with naturally enforcing the essential boundary conditions is developed for thin shell structure.
+Follow the ideas of Hellinger-Reissner principle base consistent meshfree method, the Hu-Washizu variational principle of complementary energy \cite{dah-wei1985} with variables of displacement, strains and stresses is employed, where the displacement is approximated by conventional meshfree shape functions, and the strains and stresses are expressed by the smoothed gradients or covariant smoothed gradients with covariant bases.
+It should be noted that the smoothed gradients inherently embed the first two order integration constraints, however, due to the non-polynomial property of stresses, the fulfillment of these integration constraint only can get a quasi-satisfaction of variational consistency.
+All of the essential boundary conditions about displacements and rotations are considered in Hu-Washizu weak form, and present a Nitsche-like formalism but without any artificial parameters.
+Comparing with Nitsche's method, the costly higher order derivatives are replaced by conventional reproducing smoothed gradients and its direct derivatives.
+Taking the advantages of reproducing kernel gradient smoothing framework, the smoothed gradients shows a better performance on efficiency than conventional derivatives of shape functions, which improves the computational efficiency of meshfree formulation.
+
+The remainder of this paper is organized as follows.
+Section \ref{Kinematics} briefly describes the kinematics of thin shell structure and the corresponding Hu-Washizu principle weak form.
+Subsequently, the mixed formulation regarding the displacements, strains and stresses in accordance with Hu-Washizu weak form is presented in Section \ref{mixed}.
+Section \ref{boundary} derives the discrete equilibrium equations with the naturally accommodation of essential, and compares them with those of Nitsche's method.
+The efficacy of the proposed Hu-Washizu meshfree thin shell formulation is validated by numerical results in Section \ref{examples}.
+Concluding remarks are finally drawn in Section \ref{conclusion}.

### 2024-02-14 boundary.tex
turn light
temp

@@
-\section{Naturally variational enforcement for essential boundary conditions}
+\section{Naturally variational enforcement for essential boundary conditions}\label{boundary}
 \subsection{Discrete equilibrium equations}
 With the approximated effective stresses and strains, the last equation of weak form becomes:
+\begin{equation}
+\begin{split}
+&\int_{\Gamma_C} \delta \theta_{\boldsymbol n} M_{\boldsymbol{nn}} d\Gamma 
+- \int_{\Gamma_C} \delta \boldsymbol v \cdot \boldsymbol T d\Gamma 
+- (\delta \boldsymbol v \cdot \boldlsymbol a_3 P)_{\boldsymbol x\in C_C} 
++ \int_{\Omega_C} \delta \boldsymbol v \cdot \boldsymbol b d\Omega \\
+= & - \int_{\Gamma_C} \delta \boldsymbol v \cdot \boldsymbol T_N d\Gamma 
++ \int_{\Omega_C} \delta \boldsymbol v \cdot \boldsymbol b_N d\Omega \\
++&\int_{\Gamma_C} \delta \theta_{\boldsymbol n} M_{\boldsymbol{nn}} d\Gamma 
+- \int_{\Gamma_C} \delta \boldsymbol v \cdot \boldsymbol T_M d\Gamma 
+- (\delta \boldsymbol v \cdot \boldlsymbol a_3 P)_{\boldsymbol x\in C_C} 
++ \int_{\Omega_C} \delta \boldsymbol v \cdot \boldsymbol b_M d\Omega \\
+=& -\sum_{I=1}^{n_p} \delta \boldsymbol d_I \cdot (
+\tilde{\boldsymbol g}_{\alpha I}^T \boldsymbol d^\alpha_N + \tilde{\boldsymbol g}_{\alpha\beta}^T \boldsymbol d^{\alpha\beta}_M) \\
+=& -\sum_{I=1}^{n_p} \delta \boldsymbol d_I \cdot (
+(\boldsymbol G^{-1}\tilde{\boldsymbol g}_{\alpha I})^T \boldsymbol G^{\alpha\eta}_N \cdot \boldsymbol d^\varepsilon_\eta) \\
+=& -\sum_{I=1}^{n_p} \delta \boldsymbol d_I \cdot (
+(\boldsymbol G^{-1}\tilde{\boldsymbol g}_{\alpha I})^T \int_{\Omega_C} \boldsymbol a_\beta \boldsymbol q h C^{\alpha\beta\gamma\eta} \boldsymbol q^T \boldsymbol a_\gamma \cdot \boldsymbol d^\varepsilon_\eta d\Omega) \\
+= &\int_{\Omega_C} \delta \tilde \varepsilon_{\alpha\beta} (\tilde N^{\alpha\beta} - \bar N^{\alpha\beta} + \hat N^{\alpha\beta}) d\Omega
+\end{split}
+\end{equation}
 \begin{equation}\label{w51}
-- \sum_{C=1}^{n_e}(\tilde{\boldsymbol g}^T_{\alpha I} - \bar{\boldsymbol g}^T_{\alpha I}) \boldsymbol d_N^{\alpha}
-- \sum_{C=1}^{n_e}(\tilde{\boldsymbol g}^T_{\alpha\beta I} - \bar{\boldsymbol g}^T_{\alpha\beta I}) \boldsymbol d_M^{\alpha\beta} = \boldsymbol f_I
+- \sum_{C=1}^{n_e}\sum_{I=1}^{n_p} \delta \boldsymbol d_I \cdot \left ( (\tilde{\boldsymbol g}^T_{\alpha I} - \bar{\boldsymbol g}^T_{\alpha I}) \boldsymbol d_N^{\alpha}
++ (\tilde{\boldsymbol g}^T_{\alpha\beta I} - \bar{\boldsymbol g}^T_{\alpha\beta I}) \boldsymbol d_M^{\alpha\beta} \right ) = - \sum_{I=1}^{n_p}\delta d_I \cdot \boldsymbol f_I
 \end{equation}
@@
         \boldsymbol f_I = \int_{\Gamma_t} \Psi_I \bar{\boldsymbol t} d\Gamma - \int_{\Gamma_M} \Psi_{I,\gamma} n^\gamma \bar M_{\boldsymbol{nn}} d\Gamma + [[\Psi_I\boldsymbol a_3 \bar P]]_{\boldsymbol x\in C_P} + \int_\Omega \Psi_I \bar{\boldsymbol b} d\Omega
+\end{equation}
+
+\begin{equation}
+\begin{split}
+\sum_{I=1}^{n_p} \delta \boldsymbol d_I \cdot \tilde{\boldsymbol g}^T_{\alpha I} \boldsymbol d_N^\alpha 
+&= \sum_{I=1}^{n_p} \delta \boldsymbol d_I \cdot (\boldsymbol G^{-1} \tilde{\boldsymbol g}_{\alpha I})^T  \boldsymbol G \boldsymbol d^\alpha_N \\
+&= \int_{\Omega_C} \sum_{I=1}^{n_p} \delta \boldsymbol d_I \cdot (\boldsymbol q^T\boldsymbol G^{-1} \tilde{\boldsymbol g}_{\alpha I})^T  \boldsymbol q^T \boldsymbol d^\alpha_N d\Omega \\
+&= \int_{\Omega_C} \sum_{I=1}^{n_p} \delta \boldsymbol d_I \cdot \boldsymbol a_\beta(\boldsymbol q^T\boldsymbol G^{-1} \tilde{\boldsymbol g}_{\alpha I})^T  N^{\alpha\beta h} d\Omega \\
+& = \int_{\Omega_C} \delta \tilde \varepsilon_{\alpha\beta}^h N^{\alpha\beta h} d\Omega 
+\end{split}
+\end{equation}
+\begin{equation}
+\begin{split}
+&\sum_{I=1}^{n_p} \delta \boldsymbol d_I \cdot  \left ( 
+(\tilde{\boldsymbol g}^T_{\alpha I} - \bar{\boldsymbol g}^T_{\alpha I}) \boldsymbol d^\alpha_N
++(\tilde{\boldsymbol g}^T_{\alpha\beta I} - \bar{\boldsymbol g}^T_{\alpha\beta I}) \boldsymbol d^{\alpha\beta}_M) \\
+=& \int_{\Omega_C}\left ( (\delta \tilde \varepsilon_{\alpha\beta} - \delta \bar \varepsilon_{\alpha\beta}) N^{\alpha\beta h}
++ (\delta \tilde \kappa_{\alpha\beta} - \delta \bar \kappa_{\alpha\beta})M^{\alpha\beta h}
+\right ) d\Omega
+\end{split}
+\right )
+\end{equation}
+\begin{equation}
+\begin{split}
+&\int_{\Omega_C} \delta \tilde \varepsilon_{\alpha\beta} N^{\alpha\beta h} d\Omega \\
+=&\int_{\Omega_C} \delta \tilde \varepsilon_{\alpha\beta} N^{\alpha\beta h} d\Omega \\
+\end{split}
 \end{equation}
@@
 \begin{split}
-\Pi_P(\boldsymbol v) &= \int_\Omega \frac{1}{2}\varepsilon_{\alpha\beta} N^{\alpha\beta} d\Oemga +
+\Pi_P(\boldsymbol v) &= \int_\Omega \frac{1}{2}\varepsilon_{\alpha\beta} N^{\alpha\beta} d\Omega +
 \int_\Omega \frac{1}{2} \kappa_{\alpha\beta}M^{\alpha\beta} d\Omega \\
@@
 \begin{split}
-\delta \Pi_P(\boldsymbol v) &= \int_\Omega\delta \varepsilon_{\alpha\beta} N^{\alpha\beta} d\Oemga +
+\delta \Pi_P(\boldsymbol v) &= \int_\Omega\delta \varepsilon_{\alpha\beta} N^{\alpha\beta} d\Omega +
 \int_\Omega \delta \kappa_{\alpha\beta}M^{\alpha\beta} d\Omega \\

### 2024-02-14 conclusion.tex
temp

\section{Conclusion}\label{conclusion}
An efficient and quasi-consistent meshfree thin shell formulation was presented to naturally enforce the essential boundary conditions. In this approach, the mixed formulation with Hu-Washizu principle weak form is employed, where the displacement is discretized by traditional meshfree shape functions, the strains and stresses can be expressed by reproducing kernel smoothed gradients and covariant smoothed gradients. The smoothed gradient naturally embed the first two order integration constraint, and has a quasi variational consistency for curved models in each integration cells. Owing to the Hu-Washizu variational principle, the essential boundary condition enforcement has a similar form with conventional Nitsche's method, both have the consistent term and stabilized term. Compared with Nitsche's method, the costly high order derivatives in Nitsche's consistent term have been replaced by smoothed gradients, which shows great computational speed due to the reproducing kernel gradient smoothing framework. Meanwhile, the stabilized term is naturally existed in Hu-Washizu weak form, and the artificial parameter needed in Nitsche's stabilized term has been vanished, which can automatically maintain the coercivity for stiffness matrix. Numerical results demonstrated that the proposed Hu-Washizu quasi-consistent meshfree thin shell formulation show great performance in terms of accuracy, efficiency and stability

### 2024-02-14 frontmatter.tex
temp

@@
 \begin{frontmatter}
-    \title{A Hu-Washizu variational consistent meshfree thin shell formulation with naturally accommodating essential boundary conditions}
+    % \title{A Hu-Washizu variational consistent meshfree thin shell formulation naturally accommodating essential boundary conditions}
+    \title{An quasi-consistent efficient meshfree thin shell formulation naturally accommodating essential boundary conditions}
     \author[1]{Junchao Wu\corref{cor1}}
@@
 \begin{abstract}
-A Hu-Washizu principle based variational consistent meshfree formulation with naturally enforcement of essential boundary conditions is proposed for thin shell analysis.
-In this approach, a mixed formulation of displacements, strains and stresses within the framework of Hu-Washizu variational principle is employed, where the displacements are discretized by meshfree shape functions, the strains and stresses are expressed as the smoothed gradients and covariant smoothed gradients which meet the first two order integration constraint and have the quasi- varational consistency.
-The numerical examples demonstrate the efficacy and efficiency of proposed method, while the RKGSI performs a comparable result in energy error with interpolation by meshfree approximations.
+This research proposed an eficient and quasi-consistent meshfree thin shell formulation with natural enforcement of essential boundary conditions.
+Within the framework of the Hu-Washizu variational principle, a mixed formulation of displacements, strains and stresses is employed in this approach, where the displacements are discretized using meshfree shape functions, and the strains and stresses are expressed using smoothed gradients, covariant smoothed gradients and covariant bases.
+The smoothed gradients satisfy the first and second order integration constraint and have quasi-consistent consistency.
+Owing to Hu-Washizu variational principle, the essential boundary conditions automatically arise in its weak form.
+As a result, the suggested technique's enforcement of essential boundary conditions resembles that of the traditional Nitsche's method.
+Contrary to Nitsche's method, the costly higher order derivatives of conventional meshfree shape functions were replaced by the smoothed gradients with fast computation, which improve the efficiency.
+Meanwhile, the proposed formulation features a naturally stabilized term without adding any artificial stabilization factors, which eliminates the stabilization parameter-dependent issue in the Nitsche's method.
+The efficacy of the proposed Hu-Washizu meshfree thin shell formulation is illustrated by a set of classical standard thin shell problems.
 \end{abstract}

### 2024-02-14 kinematics.tex
turn light
temp

@@
-\section{Hu-Washizu's formulation of complementary energy for thin shell}
+\section{Hu-Washizu's formulation of complementary energy for thin shell}\label{Kinematics}
 \subsection{Kinematics for thin shell}
@@
 in which $\Gamma^\gamma_{\alpha\beta} = \boldsymbol a_{\alpha,\beta} \cdot \boldsymbol a^\gamma$ is namely Christoffel symbol of the second kind.
-And $\boldsymbol v_{,\alpha}\vet$ is the in-plane covariant derivative of $\boldsymbol v_{,\alpha}$, i.e.
+And $\boldsymbol v_{,\alpha}\vert$ is the in-plane covariant derivative of $\boldsymbol v_{,\alpha}$, i.e.
 $\boldsymbol v_{,\alpha}\vert_\beta = \Gamma^\gamma_{\alpha\beta}\boldsymbol v_{,\gamma} - \boldsymbol v_{,\alpha\beta}$.
@@
 Essential boundaries on the edges and corners denoted by $\Gamma_v$, $\Gamma_\theta$ and $C_v$ are naturally existed in complementary energy functional, $\bar{\boldsymbol v}$, $\bar \theta_{\boldsymbol n}$ are the corresponding prescribed displacement and normal rotation.
-$\boldsymbol T$, $M_{\bodlsymbol{nn}}$ and $P$ can be determined by Euler-Lagrange equations of shell problem \cite{benzaken2021} as follows:
+$\boldsymbol T$, $M_{\boldsymbol{nn}}$ and $P$ can be determined by Euler-Lagrange equations of shell problem \cite{benzaken2021} as follows:
 \begin{equation}
@@
 - \int_{\Gamma_v} \delta \boldsymbol T_M \cdot \bar{\boldsymbol v} d\Gamma
-- (\delta P \boldsymbol a_3 \cdot \bar{\boldsymbol v})_{\boldsymbol x \in C_v} \\
+- (\delta P \boldsymbol a_3 \cdot \bar{\boldsymbol v})_{\boldsymbol x \in C_v}
 \end{multline}

### 2024-02-14 boundary.tex
last night

--- 2024-02-11 boundary.tex
@@
-\section{Naturally variational enforcement for essential boundary conditions}
+\section{Naturally variational enforcement for essential boundary conditions}\label{boundary}
 \subsection{Discrete equilibrium equations}
@@
 \begin{equation}\label{w51}
-- \sum_{C=1}^{n_e}(\tilde{\boldsymbol g}^T_{\alpha I} - \bar{\boldsymbol g}^T_{\alpha I}) \boldsymbol d_N^{\alpha}
-- \sum_{C=1}^{n_e}(\tilde{\boldsymbol g}^T_{\alpha\beta I} - \bar{\boldsymbol g}^T_{\alpha\beta I}) \boldsymbol d_M^{\alpha\beta} = \boldsymbol f_I
+- \sum_{C=1}^{n_e}\sum_{I=1}^{n_p} \delta \boldsymbol d_I \cdot \left ( (\tilde{\boldsymbol g}^T_{\alpha I} - \bar{\boldsymbol g}^T_{\alpha I}) \boldsymbol d_N^{\alpha}
++ (\tilde{\boldsymbol g}^T_{\alpha\beta I} - \bar{\boldsymbol g}^T_{\alpha\beta I}) \boldsymbol d_M^{\alpha\beta} \right ) = - \sum_{I=1}^{n_p}\delta d_I \cdot \boldsymbol f_I
 \end{equation}
@@
 \end{equation}
-and further substituting coefficients $\boldsymbol d_N^\alpha$, $\boldsymbol d_M^{\alpha\beta}$ into Eq. (\ref{w51}) gives the final discrete equilibrium equations: 
+the left side of Eq. (\ref{w51}) can be simplified by following steps. For clarity, the derivation of first term in Eq. (\ref{w51}) regarding as an example is given by:
 \begin{equation}
 \begin{split}
-&- \sum_{C=1}^{n_c}(\tilde{\boldsymbol g}^T_{\alpha I} - \bar{\boldsymbol g}^T_{\alpha I}) \boldsymbol d_N^{\alpha}
-- \sum_{C=1}^{n_c}(\tilde{\boldsymbol g}^T_{\alpha\beta I} - \bar{\boldsymbol g}^T_{\alpha\beta I}) \boldsymbol d_M^{\alpha\beta} \\
-= &\sum_{C=1}^{n_e} \sum_{J=1}^{n_p} \left (
+\sum_{I=1}^{n_p} \delta \boldsymbol d_I \cdot \tilde{\boldsymbol g}^T_{\alpha I} \boldsymbol d_N^\alpha 
+&= \sum_{I=1}^{n_p} \delta \boldsymbol d_I \cdot (\boldsymbol G^{-1} \tilde{\boldsymbol g}_{\alpha I})^T  \boldsymbol G \boldsymbol d^\alpha_N \\
+&= \int_{\Omega_C} \sum_{I=1}^{n_p} \delta \boldsymbol d_I \cdot (\boldsymbol q^T\boldsymbol G^{-1} \tilde{\boldsymbol g}_{\alpha I})^T  \boldsymbol q^T \boldsymbol d^\alpha_N d\Omega \\
+&= \int_{\Omega_C} \sum_{I=1}^{n_p} \delta \boldsymbol d_I \cdot \boldsymbol a_\beta(\boldsymbol q^T\boldsymbol G^{-1} \tilde{\boldsymbol g}_{\alpha I})^T  N^{\alpha\beta h} d\Omega \\
+& = \int_{\Omega_C} \delta \tilde \varepsilon_{\alpha\beta}^h N^{\alpha\beta h} d\Omega 
+\end{split}
+\end{equation}
+following the above procedure and including the weak form of Eqs. (\ref{w1}), (\ref{w2}), the left side of Eq. (\ref{w51}) in $\Omega_C$ becomes:
+\begin{equation}
 \begin{split}
-& \boldsymbol a_\alpha \tilde{\boldsymbol g}^T_{\beta I} h C^{\alpha\beta\gamma\eta} \boldsymbol a_\gamma \tilde{\boldsymbol g}_{\eta J} 
-+ \tilde{\boldsymbol g}^T_{\alpha\beta I} \boldsymbol a_3 \frac{h^3}{12}C^{\alpha\beta\gamma\eta} \boldsymbol a_3 \tilde{\boldsymbol g}_{\gamma\eta} \\
-- & \boldsymbol a_\alpha \bar{\boldsymbol g}^T_{\beta I} h C^{\alpha\beta\gamma\eta} \boldsymbol a_\gamma \tilde{\boldsymbol g}_{\eta J} - \boldsymbol a_\alpha \tilde{\boldsymbol g}^T_{\beta I} h C^{\alpha\beta\gamma\eta} \boldsymbol a_\gamma \bar{\boldsymbol g}_{\eta J} \\
-- & \bar{\boldsymbol g}^T_{\alpha\beta I}\boldsymbol a_3 \frac{h^3}{12} C^{\alpha\beta\gamma\eta} \boldsymbol a_3 \tilde{\boldsymbol g}_{\gamma\eta J} - \tilde{\boldsymbol g}^T_{\alpha\beta I} \boldsymbol a_3 \frac{h^3}{12} C^{\alpha\beta\gamma\eta} \boldsymbol a_3 \bar{\boldsymbol g}_{\gamma\eta J} \\
-+ & \boldsymbol a_\alpha \tilde{\boldsymbol g}^T_{\beta I} h C^{\alpha\beta\gamma\eta} \boldsymbol a_\gamma \hat{\boldsymbol g}_{\eta J}
-- \boldsymbol a_\alpha \bar{\boldsymbol g}^T_{\beta I} h C^{\alpha\beta\gamma\eta} \boldsymbol a_\gamma \hat{\boldsymbol g}_{\eta J} \\
-+ & \tilde{\boldsymbol g}^T_{\alpha\beta I}\boldsymbol a_3 \frac{h^3}{12} C^{\alpha\beta\gamma\eta} \boldsymbol a_3 \hat{\boldsymbol g}_{\gamma\eta J} - \bar{\boldsymbol g}^T_{\alpha\beta I} \boldsymbol a_3 \frac{h^3}{12} C^{\alpha\beta\gamma\eta} \boldsymbol a_3 \hat{\boldsymbol g}_{\gamma\eta J} \\
-+ & \boldsymbol a_\alpha \bar{\boldsymbol g}^T_{\beta I} h C^{\alpha\beta\gamma\eta} \boldsymbol a_\gamma \bar{\boldsymbol g}_{\eta J}
-+ \bar{\boldsymbol g}^T_{\alpha\beta I}\boldsymbol a_3 \frac{h^3}{12} C^{\alpha\beta\gamma\eta} \boldsymbol a_3 \bar{\boldsymbol g}_{\gamma\eta J} 
+&\sum_{I=1}^{n_p} \delta \boldsymbol d_I \cdot  \left ( 
+(\tilde{\boldsymbol g}^T_{\alpha I} - \bar{\boldsymbol g}^T_{\alpha I}) \boldsymbol d^\alpha_N
++(\tilde{\boldsymbol g}^T_{\alpha\beta I} - \bar{\boldsymbol g}^T_{\alpha\beta I}) \boldsymbol d^{\alpha\beta}_M \right) \\
+=& \int_{\Omega_C}\left ( (\delta \tilde \varepsilon^h_{\alpha\beta} - \delta \bar \varepsilon^h_{\alpha\beta}) N^{\alpha\beta h}
++ (\delta \tilde \kappa^h_{\alpha\beta} - \delta \bar \kappa^h_{\alpha\beta})M^{\alpha\beta h}
+\right ) d\Omega \\
+= &\int_{\Omega_C} (\delta \tilde \varepsilon^h_{\alpha\beta} - \delta \bar \varepsilon^h_{\alpha\beta}) hC^{\alpha\beta\gamma\eta} \varepsilon^h_{\gamma\eta}
++ (\delta \tilde \kappa^h_{\alpha\beta} - \delta \bar \kappa^h_{\alpha\beta}) \frac{h^3}{12}C^{\alpha\beta\gamma\eta}\kappa^h_{\gamma\eta} \\
+= &\int_{\Omega_C}\delta \tilde \varepsilon^h_{\alpha\beta}hC^{\alpha\beta\gamma\eta} \tilde\varepsilon^h_{\gamma\eta} d\Omega
++ \int_{\Omega_C}\delta \tilde \kappa^h_{\alpha\beta} \frac{h^3}{12}C^{\alpha\beta\gamma\eta}\tilde \kappa^h_{\gamma\eta}d\Omega \\
+- &\int_{\Omega_C}\delta \tilde \varepsilon^h_{\alpha\beta}hC^{\alpha\beta\gamma\eta} \bar \varepsilon^h_{\gamma\eta} d\Omega
+- \int_{\Omega_C}\delta \bar \varepsilon^h_{\alpha\beta}hC^{\alpha\beta\gamma\eta} \tilde \varepsilon^h_{\gamma\eta} d\Omega \\
+- &\int_{\Omega_C}\delta \tilde \kappa^h_{\alpha\beta} \frac{h^3}{12}C^{\alpha\beta\gamma\eta}\bar \kappa^h_{\gamma\eta}d\Omega 
+- \int_{\Omega_C}\delta \bar \kappa^h_{\alpha\beta} \frac{h^3}{12}C^{\alpha\beta\gamma\eta}\tilde \kappa^h_{\gamma\eta}d\Omega \\
++ &\int_{\Omega_C}\delta \bar \varepsilon^h_{\alpha\beta}hC^{\alpha\beta\gamma\eta} \bar \varepsilon^h_{\gamma\eta} d\Omega
++ \int_{\Omega_C}\delta \bar \kappa^h_{\alpha\beta} \frac{h^3}{12}C^{\alpha\beta\gamma\eta}\bar \kappa^h_{\gamma\eta}d\Omega \\
++ &\int_{\Omega_C}(\delta \tilde \varepsilon^h_{\alpha\beta} - \delta \bar \varepsilon^h_{\alpha\beta})hC^{\alpha\beta\gamma\eta} \hat \varepsilon^h_{\gamma\eta} d\Omega
++ \int_{\Omega_C}(\delta \tilde \kappa^h_{\alpha\beta} - \delta \bar \kappa^h_{\alpha\beta})\frac{h^3}{12}C^{\alpha\beta\gamma\eta}\hat \kappa^h_{\gamma\eta}d\Omega \\
 \end{split}
-\right ) \\
-= &\sum_{J=1}^{n_p} (\boldsymbol K_{IJ}+\tilde{\boldsymbol K}_{IJ}+\bar{\boldsymbol K}_{IJ}) \cdot \boldsymbol d_J - \tilde{\boldsymbol f}_I - \bar{\boldsymbol f}_I
-\end{split}
+\end{equation}
+and further substituting Eqs. (\ref{epsilon2}), (\ref{kappa2}) into above equation gives the final discrete equilibrium equations: 
+\begin{equation}
+        (\boldsymbol K + \tilde{\boldsymbol K} + \bar{\boldsymbol K} )\boldsymbol d = \boldsymbol f + \tilde{\boldsymbol f} + \bar{\boldsymbol f}
 \end{equation}
@@
 \begin{equation}\label{de1}
-        \boldsymbol K_{IJ} = \int_\Omega \tilde{\boldsymbol \varepsilon}_{\alpha\beta I} \tilde{\boldsymbol N}^{\alpha\beta}_J d\Omega + \int_\Omega \tilde{\boldsymbol \kappa}_{\alpha\beta I} \tilde{\boldsymbol M}^{\alpha\beta}_J d\Omega
+        \boldsymbol K_{IJ} = \int_\Omega \tilde{\boldsymbol \varepsilon}_{\alpha\beta I} hC^{\alpha\beta\gamma\eta}\tilde{\boldsymbol \varepsilon}_{\gamma\eta J} d\Omega + \int_\Omega \tilde{\boldsymbol \kappa}_{\alpha\beta I} \frac{h^3}{12}C^{\alpha\beta\gamma\eta} \tilde{\boldsymbol \kappa}_{\alpha\beta J} d\Omega
 \end{equation}
@@
 \begin{split}
-        \tilde{\boldsymbol K}_{IJ} = &- \int_{\Gamma_v} (\Psi_I \tilde{\boldsymbol t}_J + \tilde{\boldsymbol t}_I \Psi_J) d\Gamma \\
-                                     &+ \int_{\Gamma_\theta} (\Psi_{I,\gamma} n^\gamma \boldsymbol a_3 \tilde M_{\boldsymbol{nn}J} + \boldsymbol a_3 \tilde M_{\boldsymbol{nn}I} \Psi_{I,\gamma}n^\gamma)d\Gamma \\
-                                     & + ([[\Psi_I \boldsymbol a_3 P_J]] + [[P_I \boldsymbol a_3 \Psi_J]])_{\boldsymbol x \in C_v}
+        \tilde{\boldsymbol K}_{IJ} = &- \int_{\Gamma_v} (\Psi_I \tilde{\boldsymbol T}_{NJ} + \tilde{\boldsymbol T}_{NJ} \Psi_J) d\Gamma \\
+                                     &+ \int_{\Gamma_\theta} (\Psi_{I,\gamma} n^\gamma \boldsymbol a_3 \tilde{\boldsymbol M}_{\boldsymbol{nn}J} + \boldsymbol a_3 \tilde{\boldsymbol M}_{\boldsymbol{nn}I} \Psi_{I,\gamma}n^\gamma)d\Gamma \\
+                                     & + ([[\Psi_I \boldsymbol a_3 \tilde{\boldsymbol P}_J]] + [[\tilde{\boldsymbol P}_I \boldsymbol a_3 \Psi_J]])_{\boldsymbol x \in C_v}
 \end{split} \\
-\tilde{\boldsymbol f}_I = &- \int_{\Gamma_v} \tilde{\boldsymbol t}_I \cdot \bar{\boldsymbol v} d\Gamma + \int_{\Gamma_\theta} \tilde M_{\boldsymbol{nn}} \bar{\theta}_{\boldsymbol n} d\Gamma + [[\tilde P_I\boldsymbol a_3 \cdot \bar{\boldsymbol v}]]_{\boldsymbol x \in C_v}
+\tilde{\boldsymbol f}_I = &- \int_{\Gamma_v} \tilde{\boldsymbol T}_{NI} \cdot \bar{\boldsymbol v} d\Gamma + \int_{\Gamma_\theta} \tilde{\boldsymbol M}_{\boldsymbol{nn}I} \bar{\theta}_{\boldsymbol n} d\Gamma + [[\tilde{\boldsymbol P}_I\boldsymbol a_3 \cdot \bar{\boldsymbol v}]]_{\boldsymbol x \in C_v}
 \end{align}
@@
 \begin{align}
-\bar{\boldsymbol K}_{IJ} &= - \int_{\Gamma_v} \bar{\boldsymbol t}_I \Psi_J d\Gamma 
-+ \int_{\Gamma_\theta} \boldsymbol a_3\bar M_{\boldsymbol{nn}I} \Psi_{J,\gamma}n^\gamma d\Gamma + [[\bar P_I \boldsymbol a_3 \Psi_J]]_{\boldsymbol x \in C_v} \\
-\bar{\boldsymbol f}_I &= - \int_{\Gamma_v} \bar{\boldsymbol t}_I \cdot \bar{\boldsymbol v} d\Gamma + \int_{\Gamma_\theta} \bar M_{\boldsymbol{nn}} \bar{\theta}_{\boldsymbol n} d\Gamma + [[\bar P_I\boldsymbol a_3 \cdot \bar{\boldsymbol v}]]_{\boldsymbol x \in C_v}
+\bar{\boldsymbol K}_{IJ} &= - \int_{\Gamma_v} \bar{\boldsymbol T}_{MI} \Psi_J d\Gamma 
++ \int_{\Gamma_\theta} \boldsymbol a_3\bar{\boldsymbol M}_{\boldsymbol{nn}I} \Psi_{J,\gamma}n^\gamma d\Gamma + [[\bar{\boldsymbol P}_I \boldsymbol a_3 \Psi_J]]_{\boldsymbol x \in C_v} \\
+\bar{\boldsymbol f}_I &= - \int_{\Gamma_v} \bar{\boldsymbol T}_{MI} \cdot \bar{\boldsymbol v} d\Gamma + \int_{\Gamma_\theta} \bar{\boldsymbol M}_{\boldsymbol{nn} I} \bar{\theta}_{\boldsymbol n} d\Gamma + [[\bar{\boldsymbol P}_I\boldsymbol a_3 \cdot \bar{\boldsymbol v}]]_{\boldsymbol x \in C_v}
 \end{align}
@@
 
-The detailed derivations of Eqs (\ref{de1})-(\ref{de3}) are listed in the Appendix.
+The detailed derivations of Eqs (\ref{de1})-(\ref{de3}) are listed in the Appendix \ref{derivations}.
 As shown in these equations, the Eq.
@@
 (\ref{de2}) and (\ref{de3}) contribute for the enforcement of essential boundary.
+It should be mentioned that, in accordance with reproducing kernel smoothed gradient framework, the integration scheme of Eqs.
+(\ref{de1}-\ref{de3}) should be aligned with the those used in the construction of smoothed gradients.
+With a close look with Eqs.
+(\ref{de2}) and (\ref{de3}), the proposed approach for enforcing essential boundary conditions show an identical structure with traditional Nitsche's method, both have the consistent term and stabilized term.
+So the next subsection will review the Nitsche's method and compare it with proposed method.
 
@@
 $\boldsymbol K^c_{IJ}$ and $\boldsymbol K^s_{IJ}$ are the stiffness matrix for consistent and stabilized terms respectively, and have the following forms:
-\begin{subequations}
-\begin{equation}
+\begin{subequations}\label{nde2}
+\begin{align}
 \begin{split}
-        \boldsymbol K^c_{IJ} &= -\int_{\Gamma_v} \left ((\boldsymbol {\mathcal T}^\alpha \Psi_{I,\alpha} + \boldsymbol{\mathcal V}^{\alpha\beta} \Psi_{I,\alpha}\vert_\beta) \Psi_J + \Psi_I (\boldsymbol {\mathcal T}^\alpha \Psi_{J,\alpha} + \boldsymbol{\mathcal V}^{\alpha\beta}\Psi_{J,\alpha}\vert_\beta)\right ) d\Gamma \\
-                             &+ \int_{\Gamma_M} (\mathcal M^{\alpha\beta} \Psi_{I,\alpha}\vert_\beta \boldsymbol a_3 \Psi_{J,\gamma}n^\gamma + \Psi_{I,\gamma}n^\gamma \boldsymbol a_3 \mathcal M^{\alpha\beta} \Psi_{I,\alpha}\vert_\beta) d\Gamma
-\end{split}
-\end{equation}
+\boldsymbol K^c_{IJ} = &- \int_{\Gamma_v} (\Psi_I \boldsymbol T_{NJ} + \boldsymbol T_{NJ} \Psi_J) d\Gamma \\
+                                     &+ \int_{\Gamma_\theta} (\Psi_{I,\gamma} n^\gamma \boldsymbol a_3 \boldsymbol M_{\boldsymbol{nn}J} + \boldsymbol a_3 \boldsymbol M_{\boldsymbol{nn}I} \Psi_{I,\gamma}n^\gamma)d\Gamma \\
+                                     & + ([[\Psi_I \boldsymbol a_3 \boldsymbol P_J]] + [[\boldsymbol P_I \boldsymbol a_3 \Psi_J]])_{\boldsymbol x \in C_v}
+\end{split} \\
+\boldsymbol f^c_I = &- \int_{\Gamma_v} \boldsymbol T_I \cdot \bar{\boldsymbol v} d\Gamma + \int_{\Gamma_\theta} \boldsymbol M_{\boldsymbol{nn}I} \bar{\theta}_{\boldsymbol n} d\Gamma + [[\boldsymbol P_I\boldsymbol a_3 \cdot \bar{\boldsymbol v}]]_{\boldsymbol x \in C_v}
+\end{align}
 \end{subequations}
+\begin{subequations}\label{nde3}
+\begin{align}
+\boldsymbol K^s_{IJ} &= \alpha_v \int_{\Gamma_v} \Psi_I \Psi_J \boldsymbol 1 d\Gamma 
++ \alpha_\theta \int_{\Gamma_\theta} \Psi_{I,\eta} n^\eta \boldsymbol a_3 \boldsymbol a_3 n^\gamma\Psi_{J,\gamma} d\Gamma + \alpha_C [[\Psi_I \boldsymbol a_3 \boldsymbol a_3 \Psi_J]]_{\boldsymbol x \in C_v} \\
+\boldsymbol f^s_I &= \alpha_v \int_{\Gamma_v} \Psi_I \bar{\boldsymbol v} d\Gamma + \alpha_\theta \int_{\Gamma_\theta} \Psi_{I,\eta} n^\eta \boldsymbol a_3 \boldsymbol \bar \theta_{\boldsymbol n} d\Gamma + \alpha_C [[\Psi_I \boldsymbol a_3 \boldsymbol a_3 \cdot \bar{\boldsymbol v}]]_{\boldsymbol x \in C_v}
+\end{align}
+\end{subequations}
+
+Comparing with the consistent terms of Eqs (\ref{de2}) and (\ref{nde2}), their expression is almost identical, the major difference is that the higher order derivatives of shape functions have been replaced by smoothed gradients.
+Owing to the reproducing kernel framework, the construction of smoothed gradients only concerns about the computation of traditional meshfree shape functions and their first order derivatives, which avoids the costly computation of higher order derivatives.
+Moreover, the stabilized terms in Eq.
+(\ref{nd3}) employs the penalty method to ensure the coercivity of stiffness, in contrast, the stabilized term of Eq.
+(\ref{de3}) naturally exist in weak form, and it can stabilize the result without any artificial parameters.

### 2024-02-14 conclusion.tex
last night

@@
 Meanwhile, the stabilized term is naturally existed in Hu-Washizu weak form, and the artificial parameter needed in Nitsche's stabilized term has been vanished, which can automatically maintain the coercivity for stiffness matrix.
-Numerical results demonstrated that the proposed Hu-Washizu quasi-consistent meshfree thin shell formulation show great performance in terms of accuracy, efficiency and stability
+Numerical results demonstrated that the proposed Hu-Washizu quasi-consistent meshfree thin shell formulation show great performance in terms of accuracy, efficiency and stability.

### 2024-02-14 examples.tex
temp
last night

@@
 A normalized support size of 2.5 is used for all methods to ensure the requirement of quadratic base meshfree approximation.
-To eliminate the influence of integration, the Gauss integration scheme use 6 Gauss points for domain integration and 3 points for boundary integration, and such that the number of integration points are identical between Gauss scheme and RKGSI scheme.
+To eliminate the influence of integration, the Gauss integration scheme use 6 Gauss points for domain integration and 3 points for boundary integration to maintain the same integration accuracy between domain and boundaries, and moreover the number of integration points are identical between Gauss scheme and RKGSI scheme.
 The error estimates of displacement namely $L_2$-Error and energy namely $H_e$-Error is used here:
@@
 
-\begin{figure}[h!]
+\begin{figure}[!ht]
     \centering
-    \includegraphics[width=\textwidth]{figures/patchtest_msh}
+    % \includegraphics[width=\textwidth]{figures/patchtest_msh}
     \caption{Meshfree discretization for patch test}\label{ptf1}
@@
 
-\begin{table}[h!]
+\begin{table}[!ht]
 \centering
@@
 
-\begin{table}[h!]
+\begin{table}[!ht]
 \centering
-\caption{Results of patch test for curved model.}\label{ptt2}
+\caption{Results of patch test for cylindrical model.}\label{ptt2}
 \begin{tabular}{lcccc}
@@
 
-\begin{figure}[h!]
+\begin{figure}[!ht]
 \centering
-\includegraphics[width=\textwidth]{figures/patchtest_msh}
+% \includegraphics[width=\textwidth]{figures/patchtest_msh}
 \caption{Contour plots of $M^{12}$ for curved shell patch test.}\label{ptf2}
@@
 \subsection{Scordelis-Lo roof}
-This example consider the classical Scordelis-Lo roof problem, as shown in Fig., the cylindrical roof has the radius $R=25$, length $L=50$, thickness $h=0.25$, Young's modulus $E=4.32\times 10^8$ and Poisson rate $\nu=0.0$.
-An uniform body force of $b_z = -90$ are enforced in whole roof and the curved edges are enforced by $v_x=v_z=0$, and the straight edges are free.
+This example consider the classical Scordelis-Lo roof problem, as shown in Fig.
+\ref{slf1}, the cylindrical roof has the radius $R=25$, length $L=50$, thickness $h=0.25$, Young's modulus $E=4.32\times 10^8$ and Poisson rate $\nu=0.0$.
+An uniform body force of $b_z = -90$ is loaded in whole roof and the curved edges are enforced by $v_x=v_z=0$, and the straight edges are free.
 
-Due to the symmetry, only a quadrant of the model is considered for meshfree analysis, which is discretized by the $5\times 8$, $11\times 16$, $17\times 24$ and $23\times32$ meshfree nodes.
+Due to the symmetry, only a quadrant of the model is considered for meshfree analysis, which is discretized by the $5\times 8$, $11\times 16$, $17\times 24$ and $23\times32$ meshfree nodes(double check), as listed in Fig.
+\ref{slf2}.
+The comparison of the displacement in $z-$direction at node $A$, $v_{A3}$, is used as the investigated quantity, the reference value is 0.3024 given by reference \cite{macneal1985}.
+Firstly, Fig.
+\ref{slf3} presents a sensitivity study for the artificial parameters of $\alpha_v$'s, $\alpha_\theta$'s in the RKGSI meshfree formulations with Nitsche's method and penalty method, the results of Fig.
+\ref{slf3} reveal that Nitsche's method performed less artificial sensitivity, however both of them cannot trivially determine the optimal values of artificial parameters.
+The optimal artificial parameters from Fig.
+\ref{slf3} are adopted for the convergence study in Fig.
+\ref{slf4}, and the convergence result shown that the RKGSI get satisfactory results while the traditional Gauss methods have noticeable errors.
 
-\begin{figure}[h!]
+\begin{figure}[!ht]
 \centering
-\includegraphics[width=\textwidth]{figures/patchtest_msh}
-\caption{Description of Scordelis-Lo roof problem.}\label{ptf2}
+% \includegraphics[width=\textwidth]{figures/patchtest_msh}
+\caption{Description of Scordelis-Lo roof problem.}\label{slf1}
 \end{figure}
+\begin{figure}[!ht]
+\centering
+% \includegraphics[width=\textwidth]{figures/patchtest_msh}
+\caption{Meshfree discretizations for Scordelis-Lo roof problem.}\label{slf2}
+\end{figure}
+\begin{figure}[!ht]
+\centering
+% \includegraphics[width=\textwidth]{figures/patchtest_msh}
+\caption{sensitivity comparison of $\alpha_v$ and $\alpha_\theta$ for Scordelis-Lo problem.}\label{slf3}
+\end{figure}
+\begin{figure}[!ht]
+\centering
+% \includegraphics[width=\textwidth]{figures/patchtest_msh}
+\caption{Displacement convergence for Scordelis-Lo roof problem.}\label{slf4}
+\end{figure}
+
+\subsection{Pinched Hemispherical shell}
+Consider the hemispherical shell shown in Fig.
+\ref{phf1}, where four point loads $F=\pm 2$ are loaded at its bottom with an interval of $90^\circ$.
+The hemispherical shell has an radius $R=10$, thickness $h=0.04$, Young's modulus $E=6.825\times10^7$ and Poisson rate $\nu = 0.3$.
+
+Due to symmetry, only quadrant model has been study, where the quadrant shell has been discretized by (double check) meshfree nodes.
+The convergence investigated quantity is to comparing with the displacement at $x-$direction on point $A$, $v_{A1}$.
+The corresponding convergence result are presented in Fig.
+\ref{slfc}, where the RKGSI's performs much more favorably compared with GI meshfree formulation.
+Meanwhile the efficiency comparison for this problem is shown in Fig.
+\ref{slfe}, in which the CPU time for assembly and calculation of shape functions are considered.
+\begin{figure}[!ht]
+\centering
+% \includegraphics[width=\textwidth]{figures/patchtest_msh}
+\caption{Description of pinched hemispherical shell problem.}\label{slf1}
+\end{figure}
+\begin{figure}[!ht]
+\centering
+% \includegraphics[width=\textwidth]{figures/patchtest_msh}
+\caption{Description of pinched hemispherical shell problem.}\label{slfc}
+\end{figure}
+\begin{figure}[!ht]
+\centering
+% \includegraphics[width=\textwidth]{figures/patchtest_msh}
+\caption{Description of pinched hemispherical shell problem.}\label{slfe}
+\end{figure}

### 2024-03-09 response.tex
20240309

\documentclass{article}
\usepackage{amsmath,amssymb,amsfonts,amsthm,bm}
\title{Response to Reviewer's Comments}
\setlength{\parindent}{0em}
\setlength{\parskip}{1em}
\begin{document}

\maketitle

The authors sincerely thank the reviewers for their further comments. Accordingly, the authors have meticulously revised the manuscript and the details are given as follows.

\section*{Reviewer \#1}
\textit{This manuscript provides a meshfree thin shell formulation based on the Hu-Washizu variational principle. The essential boundary conditions in the present formulation do not require additional artificial parameters, which can be considered insensitive to those in Nitsche and Penalty’s approaches. The derivation is rigorous however several issues must be properly addressed before the publication. I recommend a major revision.}

\textbf{1.} \textit{After Eq. 5, the formulation of theta needs to be provided.}

\textbf{Reply:}

\textbf{2.} \textit{Consider using different symbols for the mid-surface displacement, v is always referring to velocity.}

\textbf{Reply:} Thanks to reviewer's suggestion. However, the velocity is not involved in this paper, it will not lead any misunstanding as $\boldsymbol v$ is denoted for mid-plane displacement.

\textbf{3.} $\boldsymbol \theta$ \textit{is the variation of $\boldsymbol a_3$, so $\boldsymbol \theta \cdot \boldsymbol a_3=0$. This relationship does not come from $\epsilon_{3i} = 0$, which was in Eq. (9).}

\textbf{Reply:} Thanks, the reviewer is right, the rotation $\boldsymbol \theta$ is perpendicular to $\boldsymbol a_3$. However, this relationship is also equivalent with $\epsilon_{3i}=0$, which follows the Kirchhofff hypothesis.

\textbf{4.} \textit{Eq. (10) seems to be wrong. Where is $\boldsymbol a_{3,\alpha}$ and where is the most complicated term $\boldsymbol \theta_{,\alpha}$?}

\textbf{Reply:} Thank you for this comment. The detailed dervation of Eq. (10) is given by the following steps:
\begin{equation}
    \begin{split}
        \kappa_{\alpha\beta} &=\frac{1}{2}(\boldsymbol a_{3,\alpha} \cdot \boldsymbol v_{,\beta} + \boldsymbol v_{,\alpha} \cdot \boldsymbol a_{3,\beta} + \boldsymbol a_\alpha \cdot \boldsymbol \theta_{,\beta} + \boldsymbol \theta_{,\alpha} \cdot \boldsymbol a_\beta) \\
        &=\frac{1}{2} \left ( 
        \begin{split}
            &\underbrace{(\boldsymbol a_3 \cdot \boldsymbol v_{,\beta})_{,\alpha} - \boldsymbol a_3 \cdot \boldsymbol v_{,\alpha\beta}}_{\boldsymbol a_{3,\alpha} \cdot \boldsymbol v_{,\beta}} \\
            +&\underbrace{(\boldsymbol a_3 \cdot \boldsymbol v_{,\alpha})_{,\beta} - \boldsymbol a_3 \cdot \boldsymbol v_{,\alpha\beta}}_{\boldsymbol v_{,\beta} \cdot \boldsymbol a_{3,\alpha}} \\
            -& \boldsymbol a_\alpha \cdot \underbrace{((\boldsymbol v_{,\gamma} \cdot \boldsymbol a_3)_{,\beta} \boldsymbol a^\gamma + \boldsymbol v_{,\gamma} \cdot \boldsymbol a_3 \boldsymbol a^\gamma_{,\beta})}_{-\boldsymbol \theta_{,\beta}} \\
            -& \boldsymbol a_\beta \cdot \underbrace{((\boldsymbol v_{,\gamma} \cdot \boldsymbol a_3)_{,\alpha} \boldsymbol a^\gamma + \boldsymbol v_{,\gamma} \cdot \boldsymbol a_3 \boldsymbol a^\gamma_{,\alpha})}_{-\boldsymbol \theta_{,\alpha}} \\
        \end{split}
        \right ) \\
        &=\frac{1}{2} \left ( 
        \begin{split}
            &\underbrace{(\boldsymbol a_3 \cdot \boldsymbol v_{,\beta})_{,\alpha}
            +(\boldsymbol a_3 \cdot \boldsymbol v_{,\alpha})_{,\beta}
            -(\boldsymbol v_{,\alpha} \cdot \boldsymbol a_3)_{,\beta}
            -(\boldsymbol v_{,\beta} \cdot \boldsymbol a_3)_{,\alpha}}_{0} \\
            -&2\boldsymbol a_3 \cdot \boldsymbol v_{,\alpha\beta}
            - \boldsymbol v_{,\gamma} \cdot \boldsymbol a_3 \underbrace{\boldsymbol a_\alpha \cdot \boldsymbol a^\gamma_{,\beta}}_{-\Gamma_{\alpha\beta}^\gamma}
            - \boldsymbol v_{,\gamma} \cdot \boldsymbol a_3 \underbrace{\boldsymbol a_\beta \cdot \boldsymbol a^\gamma_{,\alpha}}_{-\Gamma_{\alpha\beta}^\gamma} \\
        \end{split}
        \right ) \\
        &= (\Gamma_{\alpha\beta}^\gamma \boldsymbol v_{,\gamma} - \boldsymbol v_{,\alpha\beta}) \cdot \boldsymbol a_3
    \end{split}
\end{equation}
The detailed derivation can be found in reference (Benzaken et al. 2021). For the conciseness, the detailed derivation of Eq. (10) is not listed in manuscript, and the related statement has been added on line 150 (Page ).

\textbf{5.} \textit{Patchtest: table 2 is interesting. Eq. (62) assumes the solution is only polynomials on the mid-surface, which is already not a polynomial in the Cartesian coordinate. The flat model is simple, in this case, the parametric domain is the same as Cartesian. I believe the error in the curved case is due to bad parametrization. In general, the solution should be able to reproduce the parametric polynomials if the integration and parametrization are both good.}

\textbf{Reply:} Thank you for your comment. As we can find in Eqs. (32), (33), (35), (36),  the proposed approach was designated for polynomial strains and stresses. For flat model, the polynomial displacement leads to the polynomial strains and stresses. However, for curved model, the only polynomial strains can be got, the stresses turn to be non-polynomial due to the curvilinear coordinates. As a result, even the integration and parametrization are well posed, the approximated smoothed stresses cannot exactly reproduce this non-polynomial stresses. That is why the approach was named with "quasi-consistent".

\textbf{6.} \textit{Example 5.2, figure (7) is distracting. The purpose of the newly designed method is to get rid of the penalty parameters. In general, the final penalty parameter should be $E/h\times C$, where $C$ is a dimensionless coefficient. If one is testing the convergence rate of Nitsche or penalty methods, the penalty parameter needs to be scaled by the mesh size $h$, when the model is refined.}

\textbf{Reply:}

\textbf{7.} \textit{In Example 5.2, the authors provided the wrong reference value. $-0.3024$ is the one under RM shell theory. In this case, I believe the value should be $-0.3006$. See [1] for more information.}

\textbf{Reply:} Thank you for your suggestion, the reference value has been changed to $-0.3006$. Accordingly, the related statement on Page 21 is modified.

\textbf{8.} \textit{In Example 6.2, also check if the reference value provided in this study is for RM shells [2].}

\textbf{Reply:}

\textbf{9.} \textit{Scodelis-Lo roof, pinched hemisphere, and pinched cylinder are the most famous shell benchmark problems. In [3], the authors named them ”shell obstacle course”. These 3 examples are even harder than those finite deformation shell simulations. So a good shell formulation should be capable of passing these three challenges. It is strongly suggested that the authors add the pinched cylinder simulation to this manuscript.}

\textbf{Reply:}

\section*{Reviewer \#2}
\textit{With the aid of the Hu-Washizu variational principle and reproducing kernel smoothed gradients, an efficient and quasi-consistent meshfree Galerkin method is presented in this manuscript to solve thin shell problems. An outstanding merit of the method is that the essential boundary conditions can be enforced naturally. Computational formulas of the method are presented with some details. Numerical results are given to demonstrate the efficiency of the method.}

\textit{The current manuscript is well presented and contains material worthy of publication. Acceptance of the manuscript is recommended. The authors are, however, encouraged to address the comments listed below.}

\textbf{1.} \textit{Please check the gramma of the sentence below Eq. (22).}

\textbf{Reply:} Thanks, following the suggestion, this sentence have been revised on Page 9 and the authors have also doubly checked the writing of this revised.

\textbf{2.} \textit{Why is only the quadratic function used for the basis function vector p in Eq. (23)?}

\textbf{Reply:} Thanks for this comment, following the suggestion, this sentence have been revised on Page 9 and the authors have also doubly checked the writing of this revised.

\textbf{3.} \textit{Please provide the meaning of the symbol $s_{\alpha I}$ in Eq. (25). What is the parameter value used in this paper?}

\textbf{Reply:} Thanks for this comment, following the suggestion, this sentence have been revised on Page 9 and the authors have also doubly checked the writing of this revised.

\textbf{4.} \textit{Fig. 2 contains two sets of integration points. Considering the computational burden, using only one set of integration points may be more beneficial for Galerkin meshfree methods. Therefore, it is recommended to provide some explanations.}

\textbf{5.} \textit{On page 13, the authors stated that "Even with p-th order variational consistency, the proposed formulation can not exactly reproduce the solution spanned by basis functions". The reproducibility is important for Galerkin meshfree methods. So, just suggestion, is it possible to give some more explicit explanations.}

\textbf{6.} \textit{Numerical results of Nitsche's method and penalty method are also shown in Section 5.1. The values of penalty parameters used in the two methods should be provided. In addition, it is encouraged to provide some observations on numerical results of the RKGSI-penalty in Figure 4 and Tables 1 and 2.}

\textbf{7.} \textit{On pages 32-34, some reference information such as journal title and year of publication is missed.}

\textbf{Reply:} Thanks a lot, following the reviewer's suggestion, these reference's information have been revised, the authors also have doubly checked all the information and formats of references.

\end{document}

### 2024-03-09 examples.tex
20240309

--- 2024-02-12 examples.tex
@@
-\section{Numerical examples}
-In this section, several examples are carried out to verify proposed method, which employs the consistent reproducing kernel gradient smoothing integration scheme (RKGSI) and the non-consistent Gauss integration scheme (GI) with penalty method, Nitsche's method and the proposed Hu-Washizu formulation (HW) to enforce the essential boundary conditions.
-A normalized support size of 2.5 is used for all methods to ensure the requirement of quadratic base meshfree approximation.
-To eliminate the influence of integration, the Gauss integration scheme use 6 Gauss points for domain integration and 3 points for boundary integration, and such that the number of integration points are identical between Gauss scheme and RKGSI scheme.
-The error estimates of displacement namely $L_2$-Error and energy namely $H_e$-Error is used here:
+\section{Numerical examples}\label{examples}
+The suggested method, which uses Nitsche's method, the consistent reproducing kernel gradient smoothing integration scheme (RKGSI), and the non-consistent Gauss integration scheme (GI) with penalty method, as well as the proposed Hu-Washizu formulation (HW) to enforce the necessary boundary conditions, is validated in this section through several examples.
+A normalized support size of 2.5 is used for all the methods to ensure the requirement of quadratic base meshfree approximation.
+To eliminate the influence of integration, the Gauss integration scheme uses 6 Gauss points for domain integration and 3 points for boundary integration, so as to maintain the same integration accuracy between domain and boundaries.
+Moreover, the number of integration points are identical between the Gauss and RKGSI schemes.
+The error estimates of displacement ($L_2$-Error) and energy ($H_e$-Error) is used here:
 \begin{equation}
@@
 \subsection{Patch tests}
-The linear and quadratic patch tests for flat and curved thin shell are firstly study to verify the variational consistency of the proposed method.
+The linear and quadratic patch tests for flat and curved thin shells are firstly studied to verify the variational consistency of the proposed method.
 As shown in Fig.
-\ref{ptf1}, the flat and curved model is depicted by an identical parametric domain $\Omega = (0,1)\otimes(0,1)$, where the cylindrical coordinate system with radius $R=1$ is employed to describe the curved model, and the whole domain $\Omega$ is discretized by $165$ meshfree nodes.
+\ref{ptf1}, the flat and curved models are depicted by an identical parametric domain $\Omega = (0,1)\otimes(0,1)$, where the cylindrical coordinate system with radius $R=1$ is employed to describe the curved model, and the whole domain $\Omega$ is discretized by the $165$ meshfree nodes.
 All the boundaries are enforced as essential boundary conditions with the following manufactured exact solution:
@@
 
-\begin{figure}[h!]
+\begin{figure}[!ht]
     \centering
-    \includegraphics[width=\textwidth]{figures/patchtest_msh}
+    \includegraphics[width=\textwidth]{figures/ptmsh}
     \caption{Meshfree discretization for patch test}\label{ptf1}
@@
 
-Table \ref{ptt1} lists the $L_2$- and $H_e$-Error results of patch test with flat model, where the RKGSI with variational consistent essential boundary enforcement, i.e.
-RKGSI-Nitsche and RKGSI-HW, can pass the linear and quadratic path test.
+Table \ref{ptt1} lists the $L_2$- and $H_e$-Error results of patch test with flat model, where the RKGSI scheme with variational consistent essential boundary enforcement, i.e.
+RKGSI-Nitsche and RKGSI-HW, can pass the linear and quadratic patch test.
 Due to the loss of variational consistency condition, even with Nitsche's method, Gauss meshfree formulations show noticeable errors.
-Table \ref{ptt2} shows the results for curved model, which indicated that all the mehtods cannot pass the patch test, which mainly because the proposed smoothed gradient of Eqs.
-(\ref{approxse1}), (\ref{approxse2}) is unable to exactly reproduce the non-polynomial membrane and bending stress.
-However, the RKGSI-HW and RKGSI-Nitsche also performance better accuracy than other methods due to the fulfillment of first two order variational consistency.
+Table \ref{ptt2} shows the results for curved model, which indicated that all the considered methods cannot pass the patch test.
+This is mainly because the proposed smoothed gradient of Eqs.
+(\ref{approxse1}) and (\ref{approxse2}) could not exactly reproduce the non-polynomial membrane and bending stress.
+However, the RKGSI-HW and RKGSI-Nitsche methods also provide better accuracy compared to others due to the fulfillment of first second-order variational consistency.
 Meanwhile, the bending moment contours of $M^{12}$ are listed in Fig.
-\ref{ptf2}, which further verify that the proposed method obtain a satisfactory result comparing with exact solution, the conventional Gauss meshree formulations show observable errors.
+\ref{ptf2}, which further verify that the proposed method provided a satisfactory result compared to exact solution.
+On the other hand, the conventional Gauss meshree formulations showed errors.
 
-\begin{table}[h!]
+\begin{table}[!ht]
 \centering
-\caption{Results of patch test for flat model}\label{ptt1}
+\caption{Results of patch test for flat model.}\label{ptt1}
 \begin{tabular}{lcccc}
@@
 
-\begin{figure}[h!]
+\begin{figure}[!ht]
 \centering
-\includegraphics[width=\textwidth]{figures/patchtest_msh}
+\includegraphics[width=\textwidth]{figures/ptc}
 \caption{Contour plots of $M^{12}$ for curved shell patch test.}\label{ptf2}
@@
 \subsection{Scordelis-Lo roof}
-This example consider the classical Scordelis-Lo roof problem, as shown in Fig., the cylindrical roof has the radius $R=25$, length $L=50$, thickness $h=0.25$, Young's modulus $E=4.32\times 10^8$ and Poisson rate $\nu=0.0$.
-An uniform body force of $b_z = -90$ are enforced in whole roof and the curved edges are enforced by $v_x=v_z=0$, and the straight edges are free.
+This example considers the classical Scordelis-Lo roof problem, as depicted in Fig.
+\ref{slf1}.
+The cylindrical roof has dimensions $R=25$, $L=50$, $h=0.25$, Young's modulus $E=4.32\times 10^8$ and Poisson's ratio $\nu=0.0$.
+The entire roof is subjected to an uniform body force of $b_z = -90$, with the straight edges remainning free and the the curved edges are enforced by $v_x=v_z=0$.
 
-Due to the symmetry, only a quadrant of the model is considered for meshfree analysis, which is discretized by the $5\times 8$, $11\times 16$, $17\times 24$ and $23\times32$ meshfree nodes.
+Due to the symmetry, only a quadrant of the model is considered for meshfree analysis, which is discretized by the $11\times 16$, $13\times 20$, $17\times 24$ and $19\times28$ meshfree nodes, as listed in Fig.
+\ref{slf2}.
+The comparison of the displacement in $z-$direction at node $A$, $v_{A3}$, is used as the investigated quantity, with the reference value 0.3024 given by \cite{macneal1985}.
+Firstly, Fig.
+\ref{slf3} presents a sensitivity study for the artificial parameters of $\alpha_v$'s, $\alpha_\theta$'s in the RKGSI meshfree formulations with Nitsche's method and penalty method.
+The results of Fig.
+\ref{slf3} revealed, Nitsche's method observed less artificial sensitivity.
+However, both the methods cannot trivially determine the optimal values of the artificial parameters.
+The optimal artificial parameters from Fig.
+\ref{slf3} are adopted for the convergence study in Fig.
+\ref{slf4}.
+The convergence result showed that the RKGSI get satisfactory results while the traditional Gauss methods demonstrated noticeable errors.
 
-\begin{figure}[h!]
+\begin{figure}[!ht]
 \centering
-\includegraphics[width=\textwidth]{figures/patchtest_msh}
-\caption{Description of Scordelis-Lo roof problem.}\label{ptf2}
+\includegraphics[width=0.7\textwidth]{figures/slm}
+\caption{Description of Scordelis-Lo roof problem.}\label{slf1}
 \end{figure}
+\begin{figure}[!ht]
+\centering
+\includegraphics[width=\textwidth]{figures/slmsh}
+\caption{Meshfree discretizations for Scordelis-Lo roof problem.}\label{slf2}
+\end{figure}
+\begin{figure}[!ht]
+\centering
+\includegraphics[width=\textwidth]{figures/sla}
+\caption{Sensitivity comparison of $\alpha_v$ and $\alpha_\theta$ for Scordelis-Lo problem.}\label{slf3}
+\end{figure}
+\begin{figure}[!ht]
+\centering
+\includegraphics[width=\textwidth]{figures/sld}
+\caption{Displacement convergence for Scordelis-Lo roof problem.}\label{slf4}
+\end{figure}
+
+\subsection{Pinched Hemispherical shell}
+Consider the hemispherical shell shown in Fig.
+\ref{phf1}, which is loaded at four points $P=\pm 2$ at $90^\circ$ interval at its bottom.
+The hemispherical shell has an radius $R=10$, thickness $h=0.04$, Young's modulus $E=6.825\times10^7$ and Poisson's ratio $\nu = 0.3$.
+
+Due to symmetry, only quadrant model, where the $8\times8$, $16\times16$, $24\times24$ and $32\times32$ meshfree nodes have been discretized, was considered.
+The quantity under investigation for convergence is the displacement at $x-$direction on point $A$, $v_{A1}$.
+Fig.
+\ref{phf2} displays the corresponding convergence results, indicating the RKGSI scheme performed significantly better compared to the GI meshfree formulation.
+Meanwhile, the efficiency comparison for this problem is also shown in Fig.
+\ref{phf3}, in which the CPU time for assembly and calculation of shape functions are considered.
+Fig.
+\ref{phf3}(a) indicates that the RKGSI scheme observed high efficiency in assembly.
+This is due to the variational inconsistent Gauss meshfree formulation which require more Gaussian points to get satisfactory results.
+Fig.
+\ref{phf3}(b) lists the CPU time spent on enforcing essential boundary conditions for the penalty method, Nitsche's method and proposed HW method.
+The results highlighted that the proposed HW method consumed comparable CPU time in assembly compared to Nitsche's method.
+However, less time was spent to calculate the shape functions.
+Since both the HW method and penalty method were developed considering the shape functions first order derivatives.
+For this reason, both the methods shared an almost identical time in computing the shape functions.
+\begin{figure}[!ht]
+\centering
+\includegraphics[width=0.8\textwidth]{figures/pfm}
+\caption{Description of pinched hemispherical shell problem.}\label{phf1}
+\end{figure}
+\begin{figure}[!ht]
+\centering
+\includegraphics[width=\textwidth]{figures/pfd}
+\caption{Displacement convergence for pinched hemispherical shell problem.}\label{phf2}
+\end{figure}
+\begin{figure}[!ht]
+\centering
+\includegraphics[width=\textwidth]{figures/efficient}
+\caption{efficiency comparison for pinched hemispherical shell problem: (a) Whole domain; (b) Essential boundaries}\label{phf3}
+\end{figure}

### 2024-03-09 introduction.tex
20240309

--- 2024-02-10 introduction.tex
@@
-\section{Introduction}
-Thin shell is one of the most frequently used structure in engineering practice, where the thickness of this kind structure is often much smaller than its radius.
-With the Kirchhoff-Love hypothesis [1–3], the transverse shear deformation is eliminated in thin shell analysis, such that at least C1 continuous shape functions are required within Galerkin methods.
-In static and dynamic simulation of structure, the conventional finite element methods [1,2] are one of the most popular approximation scheme, however the construction of C1 continuity is still a big challenge for cell-based finite element methods.
-In last three decades, the meshfree methods [1–3] equipped high order smoothed shape functions have attracted significant research attention, while the meshfree shape functions are established based upon a set of scattered nodes and the high order continuity of shape functions is easily fulfilled even with low order basis function.
-For thin shell analysis, this high order meshfree approximations can also alleviate the membrane locking caused by the mismatched approximation order of membrane strain and bending strain [1].
-Moreover, in general, the nodal-based meshfree approximations can release the burden of mesh distortion and have the flexibility of local refinement.
-Due to these advantages, a wide variety meshfree methods are proposed and have been applied to many scientific or engineering fields.
-Among of them, moving least squares (MLS) and reproducing kernel (RK) meshfree approximations built their shape functions by enforcing the so-call consistency conditions, where the consistency conditions require that the corresponding approximations should exactly reproduce every functions spanned by basis functions, and this conditions usually serve as a basic requirement for the error convergence of resolved Galerkin solutions [1].
-However, the high order smoothed meshfree shape functions accompany with the severely overlapping supports, which leads to a misalignment between numerical integration domains and supports of shape functions.
-As a result, the meshfree shape functions usually exhibit a piecewise rational nature in each integration domains, and it brings a serious difficulty to the accurate numerical integration in Galerkin weak forms [1].
+\section{Introduction}\label{introduction}
+Thin shell structures generally adhere to the Kirchhoff hypothesis \cite{donnell1976}, that neglects the shear deformation can be described using Galerkin formulation which requires to have at least $C^1$ continuity.
+The traditional finite element methods usually only have $C^0$ continuous shape functions, and it prefers Mindlin thick shear theory, hybrid and mixed models in simulation of shell structure  \cite{hughes2000}.
+Meshfree methods \cite{belytschko1994,liu1995,chen2017} with high order smoothed shape functions have garnered much research attention over the past thirty years.
+These techniques established the shape functions based on a collection of dispersed nodes, and the high order continuity of shape functions can be easily achieved even with low-order basis functions.
+For thin shell analysis, this high order meshfree approximation can also alleviate the membrane locking caused by the mismatched approximation order of membrane strain and bending strain \cite{krysl1996}.
+Furthermore, nodal-based meshfree approximations generally offer the flexibility of local refinement and can relieve the burden of mesh distortion.
+Owing to these benefits, numerous meshfree techniques have been developed and implemented in many scientific and engineering fields \cite{liu2009,zhang2000meshless,millan2011,wang2023b,suchde2023,deng2023b}.
+However, the high order smoothed meshfree shape functions accompany the enlarged and overlapping supports, which may potentially cause many problems for shape functions.
+One of the issues is the loss of the Kronecker delta property, which means that, unlike the finite element methods, the necessary boundary conditions cannot be directly enforced  \cite{fernandez-mendez2004}.
+Another issue is that the variational consistency or said integration constraint cannot be satisfied due to the misalignment between the numerical integration domains and supports of shape functions.
+Besides, the shape functions exhibit a piecewise rational nature in each integration domain.
+Therefore, variational consistency is vital to the solution accuracy in Galerkin formulations \cite{li2016, wu2021}.
+
+Various ways have been presented to enforce the necessary boundary for Galerkin meshfree methods directly, including the boundary singular kernel method \cite{chen2000a}, mixed transformation method  \cite{chen2000a}, and interpolation element-free method \cite{liu2019a} for recovering shape functions’ Kronecker property.
+However, these methods are not based on a variational setting and cannot guarantee variational consistency.
+In the absence of a meshfree node, accuracy enforcement might be poorer.
+In contrast, enforcing the essential boundary conditions using a variational approach is preferred for Galerkin meshfree methods.
+The variational consistent Lagrange multiplier approach was initially used to the Galerkin meshfree method by Belytschko et al.
+\cite{belytschko1994}.
+In this method, the extra degrees of freedom are used to determine the discretion of Lagrange multiplier.
+Furthermore, Ivannikov et al.
+\cite{ivannikov2014a} have extended this approach to geometrically nonlinear thin shells.
+Lu et al.
+\cite{lu1994} suggested the modified variational essential boundary enforcement approach and expressed the Lagrange multiplier by equivalent tractions to eliminate the excess degrees of freedom.
+However, the coercivity of this approach is not always ensured and potentially reduces the accuracy.
+Zhu and Atluri \cite{zhu1998} pioneered the penalty method for meshfree method, making it a straightforward approach to enforce essential boundary conditions via Galerkin weak form.
+However, the penalty method lacks variational consistency and requires experimental artificial parameters whose optimal value is hard to determine.
+Fernández-Méndez and Huerta \cite{fernandez-mendez2004} imposed necessary boundary conditions using Nitsche's approach in the meshfree formulation.
+This approach can be seen as a hybrid combination of the modified variational method and the penalty method because the modified variational method generates variational consistency through the use of a consistent term, and the penalty method is used as a stabilized term to recover the coercivity.
+Skatulla and Sansour \cite{skatulla2008} extended Nitsche’s thin shell analysis method and proposed an iteration algorithm to determine artificial parameters at each integration point.
+
+In order to address the issue of numerical integration, a series of consistent integration schemes have been developed for Galerkin meshfree methods.
+Among these include stabilized conforming nodal integration \cite{chen2001} , variational consistent integration \cite{chen2013}, quadratic consistent integration \cite{duan2012a}, reproducing kernel gradient smoothing integration \cite{wang2019a}, and consistent projection integration  \cite{wang2023}.
+The assumed strain approach establishes the most consistent integration scheme, while the smoothed gradient replaces the costly higher order derivatives of traditional meshfree shape functions and shows a high efficiency.
+Moreover, to achieve global variational consistency, a consistent essential boundary condition enforcement should cooperate with the consistent integration scheme.
+The consistent integration scheme and Nitsche’s method for treating essential boundary conditions show a good performance since they can satisfy the coercivity without requiring additional degrees of freedom.
+Nevertheless, Nitsche's approach still retains the artificial parameters in stabilized terms, and it is essential to remain conscious of the costly higher order derivatives, particularly for thin plate and thin shell problems.
+Recently, Wu et al.
+\cite{wu2022a,wu2023}  proposed an efficient and stabilized essential boundary condition enforcement method based upon the Hellinger-Reissner variational principle, where a mixed formulation in Hellinger-Reissner weak form recasts the reproducing kernel gradient smoothing integration.
+The terms for enforcing essential boundary conditions are identical to the Nitsche’s method, and both have consistent and stabilized terms.
+Nevertheless, the stabilized term of this method naturally exists in the Hellinger-Reissner weak form and no longer needs the artificial parameters, even for essential boundary enforcement; instead all of the higher order derivatives are represented by smoothed gradients and their derivatives.
+
+In this study, an efficient and stabilized variational consistent meshfree method that naturally enforces the essential boundary conditions is developed for thin shell structure.
+Following the concept of the Hellinger-Reissner principle base consistent meshfree method, the Hu-Washizu variational principle of complementary energy with variables of displacement, strains, and stresses is employed.
+The displacement is approximated by conventional meshfree shape functions, and the strains and stresses are expressed by smoothed gradients with covariant bases.
+It is important to note that although the first second-order integration requirements are naturally embedded in the smoothed gradients, their fulfillment can only result in a quasi-satisfaction of variational consistency because of the non-polynomial nature of the stresses.
+Hu-Washizu's weak form is used to evaluate all the essential boundary conditions regarding displacements and rotations.
+This type of formulation is similar to the Nitsche's method but does not require any artificial parameters.
+Compared with Nitsche’s method, conventional reproducing smoothed gradients and its direct derivatives replace the costly higher order derivatives.
+By utilizing the advantages of a replicating kernel gradient smoothing framework, the smoothed gradients showed better performance compared to conventional derivatives of shape functions, hence increasing the meshfree formulation's computational efficiency.
+
+The remainder of this research paper is structured as follows: The kinematics of the thin shell structure and the weak form of the associated Hu-Washizu principle are briefly described in Section 2.
+Subsequently, the mixed formulation regarding the displacements, strains and stresses in accordance with Hu-Washizu weak form are presented in Section 3.
+The discrete equilibrium equations are derived in Section 4 using the naturally occurring accommodation of essential, and they are compared to the equations obtained using Nitsche's method.
+The numerical results in Section 5 validate the efficacy of the proposed Hu-Washizu meshfree thin shell formulation.
+Lastly, the concluding remarks are presented in Section 6.

### 2024-03-09 kinematics-v0.tex
20240309

--- 2024-02-14 kinematics.tex
@@
 Consider the configuration of a shell $\bar \Omega$, as shown in Fig.
-\ref{}, which can be easily described by a parametric curvilinear coordinate system $\boldsymbol \xi = \{\xi^i\}_{i=1,2,3}$.
+\ref{fig1}, which can be easily described by a parametric curvilinear coordinate system $\boldsymbol \xi = \{\xi^i\}_{i=1,2,3}$.
 The mid-surface of the shell denoted by $\Omega$ is specified by the in-plane coordinates $\boldsymbol \xi = \{\xi^\alpha\}_{\alpha=1,2}$, as the thickness direction of shell is by $\xi^3$, $-\frac{h}{2} \le \xi^3 \le \frac{h}{2}$, $h$ is the thickness of shell.
 In this work, Latin indices take the values from 1 to 3, and Greek indices are evaluated by 1 or 2.
-For the Kirchhoff hypothesis \cite{krysl1996}, the position $\boldsymbol x\in \bar \Omega$ are defined by linear functions with respect to $\xi^3$ :
+For the Kirchhoff hypothesis \cite{krysl1996}, the position $\boldsymbol x\in \bar \Omega$ is defined by linear functions with respect to $\xi^3$ :
 \begin{equation}\label{x}
@@
 \end{equation}
-in which $\boldsymbol r$ means the position on the mid-surface of shell, and the $\boldsymbol a_3$ is corresponding normal direction.
+\begin{figure}[!ht]
+\centering
+\includegraphics[width=0.7\textwidth]{figures/1}
+\caption{Kinematics for thin shell.}\label{fig1}
+\end{figure}
+in which $\boldsymbol r$ means the position on the mid-surface of shell, and $\boldsymbol a_3$ is corresponding normal direction.
 For the mid-surface of shell, the in-plane covariant base vector with respect to $\xi^\alpha$ can be derived by a trivial partial differentiation to $\boldsymbol r$:
@@
 \end{equation}
-for a clear expression, the subscript comma denotes the partial differentiation operation with respect to in-plane coordinates $\xi^\alpha$.
-And the normal vector $\boldsymbol a_3$ can be obtained by the normalized cross product of $\boldsymbol a_{\alpha}$'s as follow:
+to provide for a clear expression, the subscript comma denotes the partial differentiation operation with respect to in-plane coordinates $\xi^\alpha$, and the normal vector $\boldsymbol a_3$ can be obtained by the normalized cross product of $\boldsymbol a_{\alpha}$'s as follows:
 \begin{equation}
@@
 
-With the assumption of infinitesimal deformation, the strain components respected to global contravariant base can be sated as:
+With the assumption of infinitesimal deformation, the strain components with respect to the global contravariant base can be stated as:
 \begin{equation}\label{epsilon}
@@
 \end{equation}
-where $\boldsymbol u$ is the displacement for shell deformation. To fulfillment with Kirchhoff hypothesis, the displacement is assumed to be the following form:
+where $\boldsymbol u$ represents the displacement for the shell deformation. To satisfy the Kirchhoff hypothesis, the displacement is assumed to be of the following form:
 \begin{equation}\label{u}
@@
 \end{equation}
-in which the quadratic and higher order terms are neglected. $\boldsymbol v$, $\boldsymbol \theta$ respect the displacement and rotation in mid-surface.
+in which the quadratic and higher order terms are neglected. $\boldsymbol v$, $\boldsymbol \theta$ resperesent the displacement and rotation in mid-surface, respectively.
 
-Subsequently, plugging Eqs. (\ref{x}) and (\ref{u}) into Eq. (\ref{epsilon}) and neglecting quadratic terms, the strain components can be rephrased as follows:
+Subsequently, plugging Eqs. (\ref{x}) and (\ref{u}) into Eq. (\ref{epsilon}) and neglecting the quadratic terms, the strain components can be rephrased as follows:
 \begin{subequations}
@@
 \end{subequations}
-where $\varepsilon_{\alpha\beta}$, $\kappa_{\alpha\beta}$ are membrane and bending strains respectively:
+where $\varepsilon_{\alpha\beta}$, $\kappa_{\alpha\beta}$ represent membrane and bending strains, respectively, and are given as follows:
 \begin{equation}
@@
 
-In accordance with Kirchhoff hypothesis, the thickness of shell will not change and the deformation related with direction of $\xi^3$ will be vanished, i.e.
+In accordance with the Kirchhoff hypothesis, the thickness of shell will not change, and the deformation related with direction of $\xi^3$ will vanish, i.e.
 $\epsilon_{3i}=0$.
@@
 \end{equation}
-where $\boldsymbol a^\alpha$'s are the in-plane contravariant base vectors, $\boldsymbol a^\alpha \cdot \boldsymbol a_\beta = \delta^\alpha_\beta$, $\delta$ is the Kronecker delta function.
+where $\boldsymbol a^\alpha$'s is the in-plane contravariant base vector, $\boldsymbol a^\alpha \cdot \boldsymbol a_\beta = \delta^\alpha_\beta$, $\delta$ is the Kronecker delta function.
 Substituting Eq.
@@
 \end{equation}
-in which $\Gamma^\gamma_{\alpha\beta} = \boldsymbol a_{\alpha,\beta} \cdot \boldsymbol a^\gamma$ is namely Christoffel symbol of the second kind.
-And $\boldsymbol v_{,\alpha}\vert$ is the in-plane covariant derivative of $\boldsymbol v_{,\alpha}$, i.e.
+in which $\Gamma^\gamma_{\alpha\beta} = \boldsymbol a_{\alpha,\beta} \cdot \boldsymbol a^\gamma$ is namely the Christoffel symbol of the second kind, and $\boldsymbol v_{,\alpha}\vert\beta$ is the in-plane covariant derivative of $\boldsymbol v_{,\alpha}$, i.e.
 $\boldsymbol v_{,\alpha}\vert_\beta = \Gamma^\gamma_{\alpha\beta}\boldsymbol v_{,\gamma} - \boldsymbol v_{,\alpha\beta}$.
@@
 \subsection{Galerkin weak form for Hu-Washizu principle of complementary energy}
-In this study, the Hu-Washizu variational principle of complementary energy \cite{dah-wei1985} is used herein for development of this method, the corresponding complementary functional, denoted by $\Pi_C$, is listed as follow:
+In this study, the Hu-Washizu variational principle of complementary energy \cite{dah-wei1985} was adopted for the development of the proposed analytical approach, the corresponding complementary functional, denoted by $\Pi_C$, is listed as follows:
 \begin{equation} \label{functionalc}
@@
 \end{equation}
-where $C^{\alpha\beta\gamma\eta}$'s are the components of fourth order elasticity tensor with respect to covariant base and plane stress assumption, and it can be expressed by Young's modulus $E$, Poisson rate $\nu$ and the in-plane contravariant metric coefficients $a^{\alpha\beta}$'s, $a^{\alpha\beta} = \boldsymbol a^\alpha \cdot \boldsymbol a^\beta$, as follow:
+where $C^{\alpha\beta\gamma\eta}$'s represent the components of fourth order elasticity tensor with respect to the covariant base and plane stress assumption, and it can be expressed by Young's modulus $E$, Poisson's ratio $\nu$ and the in-plane contravariant metric coefficients $a^{\alpha\beta}$'s, $a^{\alpha\beta} = \boldsymbol a^\alpha \cdot \boldsymbol a^\beta$, as follows:
 \begin{equation}
@@
 
-Essential boundaries on the edges and corners denoted by $\Gamma_v$, $\Gamma_\theta$ and $C_v$ are naturally existed in complementary energy functional, $\bar{\boldsymbol v}$, $\bar \theta_{\boldsymbol n}$ are the corresponding prescribed displacement and normal rotation.
+Essential boundaries on the edges and corners denoted by $\Gamma_v$, $\Gamma_\theta$ and $C_v$ are naturally existed in complementary energy functional, $\bar{\boldsymbol v}$, $\bar \theta_{\boldsymbol n}$ are the corresponding prescribed displacement and normal rotation,respectively.
 $\boldsymbol T$, $M_{\boldsymbol{nn}}$ and $P$ can be determined by Euler-Lagrange equations of shell problem \cite{benzaken2021} as follows:
@@
 Moreover, the natural boundary conditions should be applied by Lagrangian multiplier method with displacement $\boldsymbol v$ regarded as multiplier.
-Thus then the new complementary energy functional namely $\Pi$ is given by:
+Thus, then the new complementary energy functional namely $\Pi$ is given by:
 \begin{equation} \label{functional}
@@
 \end{equation}
-where $\bar{\boldsymbol T}$, $\bar M_{\boldsymbol nn}$ and $\bar P$ are the corresponding prescribed traction, bending moment and concentrated force on edges $\Gamma_T$, $\Gamma_M$ and corner $C_P$ respectively.
+where $\bar{\boldsymbol T}$, $\bar M_{\boldsymbol nn}$ and $\bar P$ are the prescribed traction, bending moment and concentrated force on edges $\Gamma_T$, $\Gamma_M$ and corner $C_P$ respectively.
 All the boundaries meet the following geometric relationships:
@@
 \end{equation}
-and $\bar{\boldsymbol b}$ stands for the prescribed body force in $\Omega$, $\boldsymbol b$ also can be given based upon Euler-Lagrange equations \cite{benzaken2021} as:
+and $\bar{\boldsymbol b}$ stands for the prescribed body force in $\Omega$, $\boldsymbol b$ also can be written based on Euler-Lagrange equations \cite{benzaken2021} as:
 \begin{equation}

### 2024-03-09 kinematics.tex
20240309

@@
 \end{equation}
-where $\boldsymbol a^\alpha$'s are the in-plane contravariant base vectors, $\boldsymbol a^\alpha \cdot \boldsymbol a_\beta = \delta^\alpha_\beta$, $\delta$ is the Kronecker delta function.
-Substituting Eq.
-(\ref{a3}) into Eq.
-(\ref{kappa1}) leads to:
+where $\boldsymbol a^\alpha$'s is the in-plane contravariant base vector, $\boldsymbol a^\alpha \cdot \boldsymbol a_\beta = \delta^\alpha_\beta$, $\delta$ is the Kronecker delta function.
+The detailed derivation of Eq.
+\ref{a3} can be found in reference \cite{benzaken2021}.
+
+Furthermore, substituting Eq. (\ref{a3}) into Eq. (\ref{kappa1}) leads to:
 \begin{equation}

### 2024-03-10 response.tex
20240310

@@
 \title{Response to Reviewer's Comments}
-\setlength{\parindent}{0em}
+% \setlength{\parindent}{0em}
 \setlength{\parskip}{1em}
@@
 
-\textbf{Reply:}
+\textbf{Reply:} Thanks. The expression of $\boldsymbol \theta$ is derived by:
+\begin{equation}
+    \begin{split}
+        \epsilon_{3i} = 0 \Rightarrow &
+        \left \{
+        \begin{split}
+            \boldsymbol \theta \cdot \boldsymbol a_\alpha &= - \boldsymbol v_{,\alpha} \cdot \boldsymbol a_3 \\
+            \boldsymbol \theta \cdot \boldsymbol a_3 &= 0
+        \end{split}
+        \right . \\ \Rightarrow &
+        \boldsymbol \theta = \underbrace{\boldsymbol \theta \cdot \boldsymbol a_{\alpha}}_{- \boldsymbol v_{,\alpha} \cdot \boldsymbol a_3} \boldsymbol a^\alpha 
+        + \underbrace{\boldsymbol \theta \cdot \boldsymbol a_3}_{0} \boldsymbol a^3 = - \boldsymbol v_{,\alpha} \cdot \boldsymbol a_3 \boldsymbol a^\alpha
+    \end{split}
+\end{equation}
+The above derivation is given by Eq. (9). For a better understanding, the expression of Eq. (9) has been improved on Page 6.
 
@@
 
-\textbf{Reply:} Thanks to reviewer's suggestion. However, the velocity is not involved in this paper, it will not lead any misunstanding as $\boldsymbol v$ is denoted for mid-plane displacement.
+\textbf{Reply:} Thanks to reviewer's suggestion.
+However, the velocity is not involved in this paper, it will not lead any misunstanding as $\boldsymbol v$ is denoted for deflection.
+So the $\boldsymbol v$ is still presented the mid-plane deflection.
 
@@
 \textbf{Reply:} Thanks, the reviewer is right, the rotation $\boldsymbol \theta$ is perpendicular to $\boldsymbol a_3$.
-However, this relationship is also equivalent with $\epsilon_{3i}=0$, which follows the Kirchhofff hypothesis.
+However, this relationship is also equivalent with $\epsilon_{3i}=0$, which follows the Kirchhofff hypothesis and can be easily evidenced by expression of Eq.
+(9).
 
@@
 
-\textbf{Reply:}
+\textbf{Reply:} Following the reviewer's suggestion, the reference value has been updated in Fig. on Page.
 
@@
 
-\textbf{Reply:}
+\textbf{Reply:} Thank your for reviewer's suggestion.
+The pinched cylinder is one of the most famous benchmark example for thin shell formulation, and this example is also based on cylinder coordinate system, which is similar with Scodelis-Lo roof problem.
+So, in this manuscript, the pinched cylinder problem is not considered in this manuscript, and the authors will consider it in further work.
 
@@
 
-\textbf{Reply:} Thanks for this comment, following the suggestion, this sentence have been revised on Page 9 and the authors have also doubly checked the writing of this revised.
+\textbf{Reply:} Thank you for this advised suggestion.
+The proposed method is in the context of RKGSI framework that can be easily extended for the high order basis functions.
+However, for conciseness, only quadratic basis function was considered in this study, and the formulation with high order basis functions will be considered in the further work.
+The related discussion has been added in conclusion on Page 27.
 
@@
 
-\textbf{Reply:} Thanks for this comment, following the suggestion, this sentence have been revised on Page 9 and the authors have also doubly checked the writing of this revised.
+\textbf{Reply:} Thanks for this comment.
+$s_{\alpha I}$ means the support size of the shape function $\Psi_I$.
+Following the suggestion, this related statement has been added on Page 9 and the authors have also doubly checked that all the symbols in manuscript have been properly defined.
 
@@
 
+\textbf{Reply:} Thanks for this comment.
+These two integration scheme contribute different procedures.
+For instance, in the procedures with blue integration points, there exist both domain integration and boundary integration in each integration cells.
+The total number of these blue integration points has been optimized from a global point of view to reduce the computation of meshfree shape functions and their first order derivatives.
+The detailed discussion of these optimized integration scheme can be found in (Wang and Wu, 2019).
+
+On the other hand, the red cross integration points are employed for assembly of stiffness matrix that does not involve any boundary integration, only the integration accuracy is considered for choosing a proper scheme.
+Thus, the traditional 3-point integration scheme is sufficient for this task.
+If this integration scheme uses the identical points with blue ones, the number of integration points for assembly have to be two-fold increased, which will lower the efficiency.
+
+Consequently, so far, the integration schemes are the best choice for the proposed method. The related discussion has been added on Page 16.
+
 \textbf{5.} \textit{On page 13, the authors stated that "Even with p-th order variational consistency, the proposed formulation can not exactly reproduce the solution spanned by basis functions".
@@
 
+\textbf{Reply:} Thanks a lot for this helpful comment.
+
 \textbf{6.} \textit{Numerical results of Nitsche's method and penalty method are also shown in Section 5.1.
@@
 In addition, it is encouraged to provide some observations on numerical results of the RKGSI-penalty in Figure 4 and Tables 1 and 2.}
+
+\textbf{Reply:} Following the reviewer's suggestion, the artificial parameters used in NItsche's method and penalty method have been added on Page 19.
+And the additional demonstrations for RKGSI-penalty also have been added on Pages 19 and 20.
 

### 2024-03-10 conclusion-v0.tex
20240310

\section{Conclusion}\label{conclusion}
In this study, an efficient and quasi-consistent meshfree thin shell formulation was presented to naturally enforce the essential boundary conditions.  Mixed formulation with the Hu-Washizu principle weak form is adopted, where the traditional meshfree shape functions discretized the displacement, and the strains and stresses were expressed by the reproducing kernel smoothed gradients and the covariant smoothed gradients, respectively. The smoothed gradient naturally embedded the first second-order integration constraints and has a quasi variational consistency for the curved models in each integration cell. Owing to the Hu-Washizu variational principle, the essential boundary condition enforcement has a similar form with the conventional Nitsche’s method; both have consistent and stabilized terms. The costly high order derivatives in the Nitsche’s consistent term have been replaced by the smoothed gradients, which improved the computational speed due to the reproducing kernel gradient smoothing framework. Furthermore, the stabilized term naturally existed in the Hu-Washizu weak form, and the artificial parameter needed in Nitsche’s stabilized term has vanished, which can automatically maintain the coercivity for the stiffness matrix. The numerical results demonstrated that the proposed Hu-Washizu quasi-consistent meshfree thin shell formulation showed excellent accuracy, efficiency, and stability.

### 2024-03-10 conclusion.tex
20240310

--- 2024-02-14 conclusion.tex
@@
 \section{Conclusion}\label{conclusion}
-An efficient and quasi-consistent meshfree thin shell formulation was presented to naturally enforce the essential boundary conditions.
-In this approach, the mixed formulation with Hu-Washizu principle weak form is employed, where the displacement is discretized by traditional meshfree shape functions, the strains and stresses can be expressed by reproducing kernel smoothed gradients and covariant smoothed gradients.
-The smoothed gradient naturally embed the first two order integration constraint, and has a quasi variational consistency for curved models in each integration cells.
-Owing to the Hu-Washizu variational principle, the essential boundary condition enforcement has a similar form with conventional Nitsche's method, both have the consistent term and stabilized term.
-Compared with Nitsche's method, the costly high order derivatives in Nitsche's consistent term have been replaced by smoothed gradients, which shows great computational speed due to the reproducing kernel gradient smoothing framework.
-Meanwhile, the stabilized term is naturally existed in Hu-Washizu weak form, and the artificial parameter needed in Nitsche's stabilized term has been vanished, which can automatically maintain the coercivity for stiffness matrix.
-Numerical results demonstrated that the proposed Hu-Washizu quasi-consistent meshfree thin shell formulation show great performance in terms of accuracy, efficiency and stability
+In this study, an efficient and quasi-consistent meshfree thin shell formulation was presented to naturally enforce the essential boundary conditions.
+Mixed formulation with the Hu-Washizu principle weak form is adopted, where the traditional meshfree shape functions discretized the displacement, and the strains and stresses were expressed by the reproducing kernel smoothed gradients and the covariant smoothed gradients, respectively.
+The smoothed gradient naturally embedded the first second-order integration constraints and has a quasi variational consistency for the curved models in each integration cell.
+Owing to the Hu-Washizu variational principle, the essential boundary condition enforcement has a similar form with the conventional Nitsche’s method; both have consistent and stabilized terms.
+The costly high order derivatives in the Nitsche’s consistent term have been replaced by the smoothed gradients, which improved the computational speed due to the reproducing kernel gradient smoothing framework.
+Furthermore, the stabilized term naturally existed in the Hu-Washizu weak form, and the artificial parameter needed in Nitsche’s stabilized term has vanished, which can automatically maintain the coercivity for the stiffness matrix.
+Based on general reproducing kernel gradient smoothing framework, the proposed methodology can be trivially extended to high order basis meshfree formulation.
+The numerical results demonstrated that the proposed Hu-Washizu quasi-consistent meshfree thin shell formulation showed excellent accuracy, efficiency, and stability.

### 2024-03-10 mix-v0.tex
20240310

\section{Mixed meshfree formulation for modified Hellinger-Reissner weak form}\label{mixed}
\subsection{Reproducing kernel approximation for displacement}
This study approximates the displacement by adopting reproducing kernel approximation. As shown in Fig. \ref{fig2}, the mid-surface of the shell $\Omega$ is discretized by a set of meshfree nodes $\{\boldsymbol \xi_I\}_{I=1}^{n_p}$ in parametric configuration, where $n_p$ is the total number of meshfree nodes. The approximated displacement namely $\boldsymbol v^h$ can be expressed as:
\begin{equation}\label{approxv}
\boldsymbol v(\boldsymbol \xi) = \sum_{I=1}^{n_p} \Psi_I(\boldsymbol \xi) \boldsymbol d_I
\end{equation}
in which $\Psi_I$ and $\boldsymbol d_I$ is the shape function and nodal coefficient tensor related by node $\boldsymbol \xi_I$. According to reproducing kernel approximation \cite{liu1995}, the shape function takes the following form:
\begin{equation}
\Psi_I(\boldsymbol \xi) = \boldsymbol p^T(\boldsymbol \xi) \boldsymbol c(\boldsymbol \xi) \phi(\boldsymbol \xi_I - \boldsymbol \xi)
\end{equation}
where $\boldsymbol p$ is the basis function vector represented using the following quadratic function as:
\begin{equation}
        \boldsymbol p = \{1,\;\xi^1,\;\xi^2,\;(\xi^1)^2,\xi^1\xi^2,(\xi^2)^2\}^T
\end{equation}

The kernel function denoted by $\phi$ controls the support and smoothness of meshfree shape functions. The quintic B-spline function with square support is used herein as the kernel function:
\begin{equation}
\phi(\boldsymbol \xi_I - \boldsymbol \xi) = \phi(\hat s_1)\phi(\hat s_2), \quad \hat s_\alpha = \frac{\vert \xi^\alpha_I - \xi^\alpha\vert}{s_{\alpha I}}
\end{equation}
with
\begin{equation}
\phi(\hat s_\alpha) = \frac{1}{5!}\begin{cases}
(3-3\hat s_\alpha)^5 - 6(2-3\hat s_\alpha)^5 + 15(1-3\hat s_\alpha)^5 & \hat s_\alpha \le \frac{1}{3} \\
(3-3\hat s_\alpha)^5 - 6(2-3\hat s_\alpha)^5 & \frac{1}{3}<\hat s_\alpha \le \frac{2}{3} \\
(3-3\hat s_\alpha)^5 & \frac{2}{3}<\hat s_\alpha \le 1 \\
0 & \hat s_\alpha >1
\end{cases}
\end{equation}
and $\hat s_{\alpha I}$ means the characterized size of support for meshfree shape function $\Psi_I$.

The unknown vector $\boldsymbol c$ in shape function are determined by the fulfillment of the so-called consistency condition:
\begin{equation}
\sum_{I=1}^{n_p} \Psi_I(\boldsymbol \xi)\boldsymbol p(\boldsymbol \xi_I) = \boldsymbol p(\boldsymbol \xi)
\end{equation}
or equivalently
\begin{equation}\label{cc}
\sum_{I=1}^{n_p} \Psi_I(\boldsymbol \xi)\boldsymbol p(\boldsymbol \xi_I-\boldsymbol \xi) = \boldsymbol p(\boldsymbol 0)
\end{equation}
Substituting Eq. (\ref{approxv}) into (\ref{cc}), yields:
\begin{equation}\label{A}
\boldsymbol A(\boldsymbol \xi) \boldsymbol c(\boldsymbol \xi) = \boldsymbol p(\boldsymbol 0)\quad \Rightarrow \quad
\boldsymbol c(\boldsymbol \xi) = \boldsymbol A^{-1}(\boldsymbol \xi)\boldsymbol p(\boldsymbol 0)
\end{equation}
where $\boldsymbol A$ is the moment matrix:
\begin{equation}
\boldsymbol A(\boldsymbol \xi) = \sum_{I=1}^{n_p}\phi(\boldsymbol \xi_I - \boldsymbol \xi) \boldsymbol p(\boldsymbol \xi_I-\boldsymbol \xi)\boldsymbol p^T(\boldsymbol \xi_I - \boldsymbol \xi)
\end{equation}
Substituting Eq. (\ref{A}) back into Eq. (\ref{approxv}), the expression of meshfree shape function can be written as:
\begin{equation}
\Psi_I(\boldsymbol \xi) = \boldsymbol p^T(\boldsymbol \xi_I - \boldsymbol \xi)\boldsymbol A^{-1}(\boldsymbol \xi) \boldsymbol p(\boldsymbol 0) \phi(\boldsymbol \xi_I-\boldsymbol \xi)
\end{equation}
\subsection{Reproducing kernel gradient smoothing approximation for effective stress and strain}
In Galerkin meshfree formulation, the mid-plane of thin shell $\Omega$ is split by a set of integration cells $\Omega_C$'s, $\cup_{C=1}^{n_e}\Omega_C\approx \Omega$, as shown in Fig. \ref{fig2}. With the inspiration of reproducing kernel smoothing framework, the Cartesian and covariant derivatives of displacement, $\boldsymbol v_{,\alpha}$ and $-\boldsymbol v_{,\alpha}\vert_\beta$, in strains $\varepsilon_{\alpha\beta}$, $\kappa_{\alpha\beta}$ are approximated by $(p-1)$-th order polynomials in each integration cells. In integration cell $\Omega_C$, the approximated derivatives and strains denoted by $\boldsymbol v^h_{,\alpha}$, $\varepsilon^h_{\alpha\beta}$ and $-\boldsymbol v^h_{,\alpha}\vert_\beta$, $\kappa^h_{\alpha\beta}$ can be expressed by:
\begin{equation}\label{approxsn1}
    \boldsymbol v^h_{,\alpha}(\boldsymbol \xi) = \boldsymbol q^T(\boldsymbol \xi) \boldsymbol d_{\alpha}^\varepsilon, \quad
    \varepsilon^h_{\alpha\beta}(\boldsymbol \xi) = \boldsymbol q^T(\boldsymbol \xi) \frac{1}{2}(\boldsymbol a_\alpha \cdot \boldsymbol d_{\beta}^\varepsilon + \boldsymbol a_\beta \cdot \boldsymbol d_{\alpha}^\varepsilon)
\end{equation}
\begin{equation}\label{approxsn2}
    -\boldsymbol v^h_{,\alpha}\vert_\beta(\boldsymbol \xi) = \boldsymbol q^T(\boldsymbol \xi) \boldsymbol d_{\alpha\beta}^\kappa , \quad
    \kappa^h_{\alpha\beta}(\boldsymbol \xi) = \boldsymbol q^T(\boldsymbol \xi) \boldsymbol a_3 \cdot \boldsymbol d_{\alpha\beta}^\kappa
\end{equation}
where $\boldsymbol q$ is the linear polynomial vector and has the following form:
\begin{equation}
\boldsymbol q = \{ 1,\; \xi^1,\; \xi^2\}^T
\end{equation}
and the $\boldsymbol d^\varepsilon_{\alpha}$, $\boldsymbol d^\kappa_{\alpha\beta}$ are the corresponding coefficient vector tensors. For the conciseness, the mixed usage of tensor and vector is introduced in this study. For instance, the component of coefficient tensor vector $\boldsymbol d^\varepsilon_{\alpha I}$, $\boldsymbol d^\varepsilon_\alpha = \{\boldsymbol d^\varepsilon_{\alpha I}\}$, is a three dimensional tensor, $\dim \boldsymbol d^\varepsilon_{\alpha I} = \dim \boldsymbol v$.

\begin{figure}[!ht]
\centering
\includegraphics[width=\textwidth]{figures/2}
\caption{Integration scheme for Hu-Washizu weak form.}\label{fig2}
\end{figure}

In order to meet the integration constraint of thin shell problem, the approximated stresses $N^{\alpha\beta h}$, $M^{\alpha\beta h}$ are assumed to be a similar form with strains, yields:
\begin{equation}\label{approxse1}
N^{\alpha\beta h}(\boldsymbol \xi) = \boldsymbol q^T(\boldsymbol \xi) \boldsymbol a^\alpha \cdot \boldsymbol d^{\beta}_N,\quad
\boldsymbol a_\alpha N^{\alpha\beta h}(\boldsymbol \xi) = \boldsymbol q^T(\boldsymbol \xi) \boldsymbol d_N^\beta
\end{equation}
\begin{equation}\label{approxse2}
    M^{\alpha\beta h}(\boldsymbol \xi) = \boldsymbol q^T(\boldsymbol \xi) \boldsymbol a_3 \cdot \boldsymbol d^{\alpha\beta}_M,\quad
    \boldsymbol a_3 M^{\alpha\beta h}(\boldsymbol \xi) = \boldsymbol q^T(\boldsymbol \xi) \boldsymbol d^{\alpha\beta}_M
\end{equation}
substituting the approximations of Eqs. (\ref{approxv}), (\ref{approxsn1}), (\ref{approxsn2}), (\ref{approxse1}), (\ref{approxse2}) into Eqs. (\ref{w3}), (\ref{w4}) can express $\boldsymbol d^\varepsilon_\beta$ and $\boldsymbol d^\kappa_{\alpha\beta}$ by $\boldsymbol d$ as:
\begin{equation}\label{depsilon}
\boldsymbol d^\varepsilon_\beta = \boldsymbol G^{-1} \left (\sum_{I=1}^{n_p}(\tilde{\boldsymbol g}_{\beta I} - \bar{\boldsymbol g}_{\beta I}) \boldsymbol d_I + \hat{\boldsymbol g}_\beta \right )
\end{equation}
\begin{equation}\label{dkappa}
\boldsymbol d^\kappa_{\alpha\beta} = \boldsymbol G^{-1} \left (\sum_{I=1}^{n_p}(\tilde{\boldsymbol g}_{\alpha\beta I} - \bar{\boldsymbol g}_{\alpha\beta I})\boldsymbol d_I + \hat{\boldsymbol g}_{\alpha\beta} \right )
\end{equation}
with
\begin{equation}
\boldsymbol G = \int_{\Omega_C} \boldsymbol q^T \boldsymbol q d\Omega
\end{equation}
\begin{subequations}\label{gn}
\begin{align}
\tilde{\boldsymbol g}_{\beta I} &= \int_{\Gamma_C} \Psi_I \boldsymbol q n_\beta d\Gamma
- \int_{\Omega_C} \Psi_I \boldsymbol q_{\vert \beta} d\Omega \\
\bar{\boldsymbol g}_{\beta I} &= \int_{\Gamma_C\cap\Gamma_v} \Psi_I \boldsymbol q n_\beta d\Gamma \\
\hat{\boldsymbol g}_{\beta} &= \int_{\Gamma_C\cap\Gamma_v} \boldsymbol q n_\beta \bar{\boldsymbol v} d\Gamma 
\end{align}
\end{subequations}
\begin{subequations}\label{gm}
\begin{align}
\small
\begin{split}
\tilde{\boldsymbol g}_{\alpha\beta I} &= \int_{\Gamma_C} \Psi_{I,\gamma}n^\gamma \boldsymbol q n_\alpha n_\beta d\Gamma 
- \int_{\Gamma_C} \Psi_I(\boldsymbol q_{\vert \beta} n_\alpha + (\boldsymbol q s_\alpha n_\beta)_{,\gamma}s^\gamma) d\Gamma \\
&+ [[\Psi_I \boldsymbol q s_\alpha n_\beta]]_{\boldsymbol x\in C_C}
- \int_{\Omega_C} \Psi \boldsymbol q_{,\alpha\vert \beta} d\Omega \\
\end{split} \\
\small
\begin{split}
\bar{\boldsymbol g}_{\alpha\beta I} &= \int_{\Gamma_C\cap\Gamma_\theta} \Psi_{I,\gamma}n^\gamma \boldsymbol q n_\alpha n_\beta d\Gamma 
- \int_{\Gamma_C\cap\Gamma_v} \Psi_I(\boldsymbol q_{\vert \beta} n_\alpha + (\boldsymbol q s_\alpha n_\beta)_{,\gamma}s^\gamma) d\Gamma \\
&+ [[\Psi_I \boldsymbol q s_\alpha n_\beta]]_{\boldsymbol x\in C_C\cap C_v}
\end{split} \\
\small
\begin{split}
\hat{\boldsymbol g}_{\alpha\beta} &= \int_{\Gamma_C\cap\Gamma_\theta} \boldsymbol q n_\alpha n_\beta \boldsymbol a_3 \bar{\theta}_{\boldsymbol n} d\Gamma 
- \int_{\Gamma_C\cap\Gamma_v}(\boldsymbol q_{\vert \beta} n_\alpha + (\boldsymbol q s_\alpha n_\beta)_{,\gamma}s^\gamma)\bar{\boldsymbol v} d\Gamma \\
&+ [[\boldsymbol q s_\alpha n_\beta \bar{\boldsymbol v}]]_{\boldsymbol x\in C_C\cap C_v}
\end{split}
\end{align}
\end{subequations}
where evaluations of $\boldsymbol q_{\vert \beta}$, $\boldsymbol q_{,\alpha\vert\beta}$ are detail in \ref{derivative}. Further plugging Eqs. (\ref{depsilon}) and (\ref{dkappa}) back into Eqs. (\ref{approxsn1}) and (\ref{approxsn2}) respectively gives the final expression of $\boldsymbol v^h_{,\alpha}$, $\varepsilon^h_{\alpha\beta}$ and $-\boldsymbol v^h_{,\alpha\beta}$, $\boldsymbol \kappa^h_{\alpha\beta}$ as: \begin{subequations}
\begin{equation}
\boldsymbol v^h_{,\alpha} = \sum_{I=1}^{n_p}(
\tilde \Psi_{I,\alpha} - \bar \Psi_{I,\alpha}) \boldsymbol d_I +
\boldsymbol q^T \boldsymbol G^{-1}\hat{\boldsymbol g}_{\alpha}
\end{equation}
\begin{equation}\label{epsilonh}
\begin{split}
\varepsilon^h_{\alpha\beta} &= 
\sum_{I=1}^{n_p} \frac{1}{2}(\boldsymbol a_\alpha \tilde \Psi_{I,\beta} + \boldsymbol a_\beta \tilde \Psi_{I,\alpha}) \cdot \boldsymbol d_I 
- \sum_{I=1}^{n_p} \frac{1}{2}(\boldsymbol a_\alpha \bar \Psi_{I,\beta} + \boldsymbol a_\beta \bar \Psi_{I,\alpha}) \cdot \boldsymbol d_I \\
&+ \boldsymbol q^T \boldsymbol G^{-1} \frac{1}{2}(\boldsymbol a_\alpha \cdot \hat{\boldsymbol g}_{\beta} + \boldsymbol a_\beta \cdot \hat{\boldsymbol g}_{\alpha}) \\
&= \tilde \varepsilon^h_{\alpha\beta} - \bar \varepsilon^h_{\alpha\beta} + \hat \varepsilon^h_{\alpha\beta}
\end{split}
\end{equation}
\end{subequations}
\begin{subequations}
\begin{equation}
-\boldsymbol v^h_{,\alpha}\vert_\beta = \sum_{I=1}^{n_p} (
\tilde \Psi_{I,\alpha\beta} -
\bar \Psi_{I,\alpha\beta} ) \boldsymbol d_I +
\boldsymbol q^T \boldsymbol G^{-1}\hat{\boldsymbol g}_{\alpha\beta}
\end{equation}
\begin{equation}\label{kappah}
\begin{split}
\kappa^h_{\alpha\beta} &= \sum_{I=1}^{n_p} \tilde \Psi_{I,\alpha\beta} \boldsymbol a_3 \cdot \boldsymbol d_I
- \sum_{I=1}^{n_p} \bar \Psi_{I,\alpha\beta} \boldsymbol a_3 \cdot \boldsymbol d_I +
\boldsymbol q^T \boldsymbol G^{-1}\boldsymbol a_3 \cdot \hat{\boldsymbol g}_{\alpha\beta} \\
&= \tilde \kappa^h_{\alpha\beta} - \bar \kappa^h_{\alpha\beta} + \hat \kappa^h_{\alpha\beta}
\end{split}
\end{equation}
\end{subequations}
with
\begin{equation}\label{epsilon2}
\left \{
\begin{split}
\tilde \varepsilon^h_{\alpha\beta} &= \sum_{I=1}^{n_p} \frac{1}{2}(\boldsymbol a_\alpha \tilde \Psi_{I,\beta} + \boldsymbol a_\beta \tilde \Psi_{I,\alpha}) \cdot \boldsymbol d_I
=\sum_{I=1}^{n_p} \tilde{\boldsymbol \varepsilon}_{\alpha\beta I} \cdot \boldsymbol d_I \\
\bar \varepsilon^h_{\alpha\beta} &= \sum_{I=1}^{n_p} \frac{1}{2}(\boldsymbol a_\alpha \bar \Psi_{I,\beta} + \boldsymbol a_\beta \bar \Psi_{I,\alpha}) \cdot \boldsymbol d_I
=\sum_{I=1}^{n_p} \bar{\boldsymbol \varepsilon}_{\alpha\beta I} \cdot \boldsymbol d_I \\
\hat \varepsilon^h_{\alpha\beta} &= \boldsymbol q^T \boldsymbol G^{-1} \frac{1}{2}(\boldsymbol a_\alpha\cdot\hat{\boldsymbol g}_\beta + \boldsymbol a_\beta \cdot \hat{\boldsymbol g}_\alpha)
\end{split}
\right .
\end{equation}
\begin{equation}
\left \{
\begin{split}
&\tilde{\Psi}_{I,\alpha}(\boldsymbol \xi) = \boldsymbol q^T(\boldsymbol \xi) \boldsymbol G^{-1} \tilde{\boldsymbol g}_{\alpha I} \\
&\bar{\Psi}_{I,\alpha}(\boldsymbol \xi) = \boldsymbol q^T(\boldsymbol \xi) \boldsymbol G^{-1} \bar{\boldsymbol g}_{\alpha I} \\
&\tilde{\boldsymbol \varepsilon}_{\alpha\beta I} = \frac{1}{2}(\boldsymbol a_\alpha \tilde \Psi_{I,\beta} + \boldsymbol a_\beta \tilde \Psi_{I,\alpha}) \\
&\bar{\boldsymbol \varepsilon}_{\alpha\beta I} = \frac{1}{2}(\boldsymbol a_\alpha \bar \Psi_{I,\beta} + \boldsymbol a_\beta \bar \Psi_{I,\alpha})
\end{split}
\right .
\end{equation}
\begin{equation}\label{kappa2}
\left \{
\begin{split}
\tilde \kappa^h_{\alpha\beta} &= \sum_{I=1}^{n_p} \tilde \Psi_{I,\alpha\beta}\boldsymbol a_3 \cdot \boldsymbol d_I 
= \sum_{I = 1}^{n_p} \tilde{\boldsymbol \kappa}_{\alpha\beta I} \cdot \boldsymbol d_I\\
\bar \kappa^h_{\alpha\beta} &= \sum_{I=1}^{n_p} \bar \Psi_{I,\alpha\beta}\boldsymbol a_3 \cdot \boldsymbol d_I
= \sum_{I = 1}^{n_p} \bar{\boldsymbol \kappa}_{\alpha\beta I} \cdot \boldsymbol d_I \\
\hat \kappa^h_{\alpha\beta} &= \boldsymbol q^T \boldsymbol G^{-1} \boldsymbol a_3 \cdot \hat{\boldsymbol g}_{\alpha\beta}
\end{split}
\right .
\end{equation}
\begin{equation}
\left \{
\begin{split}
&\tilde{\Psi}_{I,\alpha\beta}(\boldsymbol \xi) = \boldsymbol q^T(\boldsymbol \xi) \boldsymbol G^{-1} \tilde{\boldsymbol g}_{\alpha\beta I} \\
&\bar{\Psi}_{I,\alpha\beta}(\boldsymbol \xi) = \boldsymbol q^T(\boldsymbol \xi) \boldsymbol G^{-1} \tilde{\boldsymbol g}_{\alpha\beta I} \\
&\tilde{\boldsymbol \kappa}_{\alpha\beta I} = \tilde \Psi_{I,\alpha\beta}\boldsymbol a_3 \\
&\bar {\boldsymbol \kappa}_{\alpha\beta I} = \bar \Psi_{I,\alpha\beta}\boldsymbol a_3 \\
\end{split}
\right .
\end{equation}

% Furthermore, taking Eqs. (\ref{approxsn1}) and (\ref{approxsn2}) into Eqs.(\ref{w1}) and (\ref{w2}) can obtain the approximated effective stresses $N^{\alpha\beta h}$, $M^{\alpha\beta h}$ and their coefficients $\boldsymbol d_N^\beta$, $\boldsymbol d_M^{\alpha\beta}$ as:
% \begin{equation}\label{d_N1}
%  \delta \boldsymbol d^\varepsilon_\alpha \cdot \boldsymbol G^{\alpha\eta}_N \cdot \boldsymbol d^\varepsilon_\eta = \delta \boldsymbol d^\varepsilon_\alpha \cdot \boldsymbol d_N^\alpha \boldsymbol G \quad\Rightarrow \quad & \boldsymbol d_N^\alpha = \boldsymbol G^{-1} \boldsymbol G_N^{\alpha\eta} \cdot \boldsymbol d^\varepsilon_\eta
% \end{equation}
% \begin{equation}\label{d_M1}
%  \delta \boldsymbol d^\kappa_{\alpha\beta} : \boldsymbol G_M^{\alpha\beta\gamma\eta} : \boldsymbol d^\kappa_{\gamma\eta} \boldsymbol G = \delta \boldsymbol d^\kappa_{\alpha\beta} \cdot \boldsymbol d_M^{\alpha\beta} \boldsymbol G \\
% \Rightarrow \; \boldsymbol d_M^{\alpha\beta} = \boldsymbol G^{-1} \boldsymbol G_{\alpha\beta}^M \cdot \boldsymbol d^\kappa_{\gamma\eta}
% \end{equation}
% with
% \begin{equation}
% \boldsymbol G^{\alpha\eta}_N = \int_{\Omega_C} \boldsymbol a_\beta hC^{\alpha\beta\gamma\eta} \boldsymbol a_\gamma \boldsymbol q \boldsymbol q^T d\Omega
% \end{equation}
% \begin{equation}
% \boldsymbol G^{\alpha\beta\gamma\eta}_M = \int_{\Omega_C} \boldsymbol a_3 \frac{h^3}{12}C^{\alpha\beta\gamma\eta}\boldsymbol a_3 \boldsymbol q\boldsymbol q^T d\Omega
% \end{equation}
%  
% Finally, taking Eqs. (\ref{d_N1}) and (\ref{d_M1}) back to Eqs. (\ref{approxse1}), (\ref{approxse2}) can express the components of stresses as follows:
% \begin{equation}\label{Nh}
% N^{\alpha\beta h} = \boldsymbol q^T \boldsymbol G^{-1}\frac{1}{2}(\boldsymbol a^\alpha \cdot \boldsymbol G^{\beta\gamma}_{N} + \boldsymbol a^\beta \cdot \boldsymbol G^{\alpha\gamma}_N) \cdot \boldsymbol d^{\varepsilon}_\gamma
% \end{equation}
% \begin{equation}\label{Mh}
% M^{\alpha\beta h} = \boldsymbol q^T \boldsymbol G^{-1} \boldsymbol a_3 \cdot \boldsymbol G^{\alpha\beta\gamma\eta}_M \cdot \boldsymbol d^\kappa_{\gamma\eta}
% \end{equation}

It has to be noted that, referring to reproducing kernel gradient smoothing framework \cite{wang2019a}, $\tilde \Psi_{I,\alpha}$, $\tilde \Psi_{I,\alpha\beta}$ are actually the first and second order smoothed gradients in curvilinear coordinates. $\tilde{\boldsymbol g}_{\alpha I}$ and $\tilde{\boldsymbol g}_{\alpha \beta I}$ are the right hand side integration constraints for first and second order gradients, then this formulation can meet the variational consistency for the $p$-th order polynomials. It should be known that, in curved model, the variational consistency for non-polynomial functions, like trigonometric functions, should be required for the polynomial solution. Even with $p$-th order variational consistency, the proposed formulation can not exactly reproduce the solution spanned by basis functions. However, the accuracy of reproducing kernel smoothed gradients is still better that traditional meshfree formulation. Numerical examples in the section below will provide better evidence to prove the accuracy of the reproducing kernel smoothed gradients.

### 2024-03-22 response.tex
20240322

@@
 \usepackage{amsmath,amssymb,amsfonts,amsthm,bm}
+\usepackage{enumerate}
 \title{Response to Reviewer's Comments}
+\author{}
+\date{}
 % \setlength{\parindent}{0em}
@@
 For the conciseness, the detailed derivation of Eq.
-(10) is not listed in manuscript, and the related statement has been added on line 150 (Page ).
+(10) is not listed in manuscript, and the related statement has been added on Page 6.
 
@@
 For flat model, the polynomial displacement leads to the polynomial strains and stresses.
-However, for curved model, the only polynomial strains can be got, the stresses turn to be non-polynomial due to the curvilinear coordinates.
+However, for curved model, the only polynomial strains can be got, the stresses turn to be non-polynomial due to the parametrization of curvilinear coordinates.
 As a result, even the integration and parametrization are well posed, the approximated smoothed stresses cannot exactly reproduce this non-polynomial stresses.
@@
 
-\textbf{Reply:}
+\textbf{Reply:} Following the reviewer's suggestion, the artificial parameters using in Figure (7) are scaled by support size of shape function $s$ that can represent the grid size of discrete model $h$.
+In accordance with reference [4], the parameters were set as $\alpha_{v\alpha} = \bar\alpha_v / s$, $\alpha_{v3} = \bar\alpha_v / s^3$ and $\alpha_\theta = \bar \theta / s$, in which $\alpha_{v\alpha}$'s and $\alpha_{v3}$ have been redefined as the parameters referring to in-plane displacements $\boldsymbol v \cdot \boldsymbol a_\alpha$ and deflection $\boldsymbol v \cdot \boldsymbol a_3$ respectively.
+After these parameters scaling by support size, Nitsche's method and penalty method shows less parameter sensitivity, but cannot totally eliminate this.
+The related statements are added on Pages 17, 18 and 21.
 
@@
 
-\textbf{Reply:} Thank you for your suggestion, the reference value has been changed to $-0.3006$. Accordingly, the related statement on Page 21 is modified.
+\textbf{Reply:} Thank you for your suggestion, the reference value has been changed to $-0.3006$. Accordingly, the related statement on Page 21 has been modified.
 
@@
 
-\textbf{Reply:} Following the reviewer's suggestion, the reference value has been updated in Fig. on Page.
+\textbf{Reply:} Following the reviewer's suggestion, the reference value has been updated in Fig.
+10 on Page 26.
+For showing a better convergence performance, the meshfree discretizations were changed to that ranging from $16\times16$ to $40\times40$.
+The relate description also has been revised on Page 21.
 
@@
 The total number of these blue integration points has been optimized from a global point of view to reduce the computation of meshfree shape functions and their first order derivatives.
-The detailed discussion of these optimized integration scheme can be found in (Wang and Wu, 2019).
+The detailed discussion of these optimized integration scheme can be found in [5].
 
@@
 \textbf{Reply:} Thanks a lot for this helpful comment.
+This reproducibility is a requirement for the variational consistency, and it is the necessary to achieve the optimal accuracy for Galerkin formulations.
+The related discussions about the reproducibility and consistency condition have been added on Page 2.
 
@@
 
+\section*{References}
+\begin{enumerate}[{[1]}]
+    \item P. Krysl, J.S. Chen, Benchmarking computational shell models, Archives of Computational Methods in Engineering 30 (2023) 301–315. 
+    \item J. Kiendl, K.U. Bletzinger, J. Linhard, R. Wüchner, Isogeometric shell analysis with Kirchhoff–Love elements, Computer Methods in Applied Mechanics and Engineering 198 (2009) 3902–3914. 
+    \item T. Belytschko, H. Stolarski, W.K. Liu, Stress projection for membrane and shear locking in shell finite elements, Computer Methods in Applied Mechanics and Engineering 51 (1985) 221–258. 
+    \item J.
+Benzaken, J.A.
+Evans, S.F.
+McCormick, R.
+Tamstorf, Nitsche’s method for linear Kirchhoff–Love shells: Formulation, error analysis, and verification, Computer Methods in Applied Mechanics and Engineering 374 (2021) 113544.
+    \item D.
+Wang, J.
+Wu, An inherently consistent reproducing kernel gradient smoothing framework toward efficient Galerkin meshfree formulation with explicit quadrature, Computer Methods in Applied Mechanics and Engineering 349 (2019) 628–672.
+\end{enumerate}
 \end{document}

### 2024-03-22 boundary.tex
20240322

@@
 \subsection{Discrete equilibrium equations}
-With the approximated effective stresses and strains, the last equation of weak form becomes:
+With the approximated effective stresses and strains, the last equation of weak form Eq. (\ref{w5}) becomes:
 \begin{equation}\label{w51}
@@
 \end{equation}
-the left side of Eq. (\ref{w51}) can be simplified by following steps. For clarity, the derivation of first term in Eq. (\ref{w51}) regarding as an example is given by:
+The left side of Eq. (\ref{w51}) can be simplified using the following steps. For clarity, the derivation of first term in Eq. (\ref{w51}) taken as an example is given by:
 \begin{equation}
@@
 \end{equation}
-and further substituting Eqs. (\ref{epsilon2}), (\ref{kappa2}) into above equation gives the final discrete equilibrium equations: 
+on further substituting Eqs. (\ref{epsilon2}) and (\ref{kappa2}) into above equation gives the final discrete equilibrium equations, respectively: 
 \begin{equation}
@@
 
-The detailed derivations of Eqs (\ref{de1})-(\ref{de3}) are listed in the Appendix \ref{derivations}.
-As shown in these equations, the Eq.
+The detailed derivations of Eqs (\ref{de1})-(\ref{de3}) are listed in the \ref{derivations}.
+As shown in these equations, Eq.
 (\ref{de1}) is the conventional stiffness matrix evaluated by smoothed gradients $\tilde \Psi_{I,\alpha}$, $\tilde \Psi_{I,\alpha}\vert_\beta$, and the Eqs.
@@
 (\ref{de1}-\ref{de3}) should be aligned with the those used in the construction of smoothed gradients.
-With a close look with Eqs.
-(\ref{de2}) and (\ref{de3}), the proposed approach for enforcing essential boundary conditions show an identical structure with traditional Nitsche's method, both have the consistent term and stabilized term.
-So the next subsection will review the Nitsche's method and compare it with proposed method.
+The integration scheme used for proposed method is shown in Fig.
+\ref{fig2}, in which the total number of the blue circular integration points has been optimized from a global point of view, aiming to reduce the computation of traditional meshfree shape functions and its first order derivatives.
+In contrast, for assembly stiffness matrix $\boldsymbol K$, the low order Gauss integration rule is suitable to ensure the accuracy due to the inherently variational consistency in smoothed gradients.
+The detailed positions and weight of integration points and the efficiency demonstration of this optimized integration scheme can be found in \cite{wang2019a, du2022}  With a close look at Eqs.
+(\ref{de2}) and (\ref{de3}), the proposed approach for enforcing essential boundary conditions show an identical structure with traditional Nitsche's method, both have the consistent and stabilized terms.
+So, the next subsection will review the Nitsche's method and compare it with the proposed method.
 
 \subsection{Comparison with Nitsche's method}
-The Nitsche's method for enforcing essential boundary can be regarded as a combination of Lagrangian multiplier method and penalty method, in which the Lagrangian multiplier is represented by the approximated displacement.
+The Nitsche's method for enforcing essential boundaries can be regarded as a combination of Lagrangian multiplier method and penalty method, in which the Lagrangian multiplier is represented by the approximated displacement.
 The corresponding total potential energy functional $\Pi_P$ is given by:
@@
                      + (P\boldsymbol a_3 \cdot (\boldsymbol v - \bar{\boldsymbol v}))_{\boldsymbol x \in C_v}}_{\text{consistent term}} \\
-                     &+ \underbrace{\frac{\alpha_v}{2} \int_{\Gamma_v} \boldsymbol v \cdot \boldsymbol v d\Gamma 
+                     &+ \underbrace{\sum_{i=1}^3\frac{\alpha_{vi}}{2} \int_{\Gamma_v} \boldsymbol v \cdot \boldsymbol v d\Gamma 
                      + \frac{\alpha_\theta}{2} \int_{\Gamma_\theta} \theta_{\boldsymbol n}^2 d\Gamma
-             + \frac{\alpha_C}{2}(\boldsymbol v \cdot \boldsymbol v)_{\boldsymbol x\in C_v}}_{\text{stabilized term}}
+             + \frac{\alpha_C}{2}(\boldsymbol v \cdot \boldsymbol a_3)^2_{\boldsymbol x\in C_v}}_{\text{stabilized term}}
 \end{split}
 \end{equation}
-where the consistent term rephrased from Lagrangian multiplier method contributes to enforce the essential boundary and meet the variational consistency condition.
-However the consistent term can not always ensure the coercivity of stiffness, so the penalty method is introduced to be regarded as a stabilized term.
+where the consistent term generated from the Lagrangian multiplier method contributes to enforce the essential boundary, and meet the variational consistency condition.
+However, the consistent term can not always ensure the coercivity of stiffness, so the penalty method is introduced to serve as a stabilized term, in which $\alpha_{vi}$'s, $\alpha_\theta$ and $\alpha_C$ are experimental artificial parameters in penalty method.
 With a standard variational argument, the corresponding weak form can be stated as:
@@
                      + (\delta P\boldsymbol a_3 \cdot (\boldsymbol v - \bar{\boldsymbol v}))_{\boldsymbol x \in C_v} \\
-                     &+ \alpha_v \int_{\Gamma_v} \delta \boldsymbol v \cdot \boldsymbol v d\Gamma 
+                     &+ \sum_{i=1}^{3}\alpha_{vi} \int_{\Gamma_v} (\delta \boldsymbol v \cdot \boldsymbol a_i) (\boldsymbol a_i \cdot \boldsymbol v) d\Gamma 
                      + \alpha_\theta \int_{\Gamma_\theta} \delta \theta_{\boldsymbol n}\theta_{\boldsymbol n} d\Gamma
-                     + \alpha_C(\delta \boldsymbol v \cdot \boldsymbol v)_{\boldsymbol x\in C_v} \\
+                     + \alpha_C(\delta \boldsymbol v \cdot \boldsymbol a_3 \; \boldsymbol a_3 \cdot \boldsymbol v)_{\boldsymbol x\in C_v} \\
                      &= 0
@@
 \end{equation}
-in which $\alpha_v$, $\alpha_\theta$ and $\alpha_C$ are experimental artificial parameters.
-Further invoking the conventional reproducing kernel approximation of Eq.
-(\ref{approxv}) leads to the following discrete equilibrium equations:
+Further invoking the conventional reproducing kernel approximation of Eq. (\ref{approxv}) leads to the following discrete equilibrium equations:
 \begin{equation}
@@
 (\ref{de1}).
-$\boldsymbol K^c_{IJ}$ and $\boldsymbol K^s_{IJ}$ are the stiffness matrix for consistent and stabilized terms respectively, and have the following forms:
+$\boldsymbol K^c_{IJ}$ and $\boldsymbol K^s_{IJ}$ are the stiffness matrices for consistent and stabilized terms, respectively, and have the following form:
 \begin{subequations}\label{nde2}
@@
 \begin{align}
-\boldsymbol K^s_{IJ} &= \alpha_v \int_{\Gamma_v} \Psi_I \Psi_J \boldsymbol 1 d\Gamma 
+\boldsymbol K^s_{IJ} &= \boldsymbol \alpha_v \int_{\Gamma_v} \Psi_I \Psi_J d\Gamma 
 + \alpha_\theta \int_{\Gamma_\theta} \Psi_{I,\eta} n^\eta \boldsymbol a_3 \boldsymbol a_3 n^\gamma\Psi_{J,\gamma} d\Gamma + \alpha_C [[\Psi_I \boldsymbol a_3 \boldsymbol a_3 \Psi_J]]_{\boldsymbol x \in C_v} \\
-\boldsymbol f^s_I &= \alpha_v \int_{\Gamma_v} \Psi_I \bar{\boldsymbol v} d\Gamma + \alpha_\theta \int_{\Gamma_\theta} \Psi_{I,\eta} n^\eta \boldsymbol a_3 \boldsymbol \bar \theta_{\boldsymbol n} d\Gamma + \alpha_C [[\Psi_I \boldsymbol a_3 \boldsymbol a_3 \cdot \bar{\boldsymbol v}]]_{\boldsymbol x \in C_v}
+\boldsymbol f^s_I &= \boldsymbol \alpha_v \int_{\Gamma_v} \Psi_I \bar{\boldsymbol v} d\Gamma + \alpha_\theta \int_{\Gamma_\theta} \Psi_{I,\eta} n^\eta \boldsymbol a_3 \boldsymbol \bar \theta_{\boldsymbol n} d\Gamma + \alpha_C [[\Psi_I \boldsymbol a_3 \boldsymbol a_3 \cdot \bar{\boldsymbol v}]]_{\boldsymbol x \in C_v}
 \end{align}
 \end{subequations}
+with
+\begin{equation}
+\boldsymbol \alpha_v = \begin{bmatrix}
+    \alpha_{v1} & 0 & 0 \\
+    0 & \alpha_{v2} & 0 \\
+    0 & 0 & \alpha_{v3} \\
+\end{bmatrix}
+\end{equation}
 
-Comparing with the consistent terms of Eqs (\ref{de2}) and (\ref{nde2}), their expression is almost identical, the major difference is that the higher order derivatives of shape functions have been replaced by smoothed gradients.
-Owing to the reproducing kernel framework, the construction of smoothed gradients only concerns about the computation of traditional meshfree shape functions and their first order derivatives, which avoids the costly computation of higher order derivatives.
+On comparing with the consistent terms of Eqs.
+(\ref{de2}) and (\ref{nde2}), the expressions were almost identical, the major difference is that the higher order derivatives of shape functions have been replaced by smoothed gradients.
+Owing to the reproducing kernel framework, the construction of smoothed gradients only concerned about the computation of traditional meshfree shape functions and their first order derivatives, which avoid the costly computation of higher order derivatives.
 Moreover, the stabilized terms in Eq.
-(\ref{nd3}) employs the penalty method to ensure the coercivity of stiffness, in contrast, the stabilized term of Eq.
-(\ref{de3}) naturally exist in weak form, and it can stabilize the result without any artificial parameters.
+(\ref{nde3}) employs the penalty method with big enough artificial parameters to ensure the coercivity of stiffness.
+And the optimal values of these artificial parameters are proportional to the grid size of discrete model that can be represented by support size in meshfree approximation, where the $\alpha_{v\alpha} \propto s^{-1}$, $\alpha_{v3} \propto s^{-3}$, $\alpha_\theta \propto s^{-1}$, $\alpha_C \propto s^{-2}$\cite{benzaken2021}, and $s = \min\{s_{\alpha I}\}$.
+In contrast, the stabilized term of Eq.
+(\ref{de3}) naturally exists in its weak form, and can stabilize the result without considering any artificial parameters.

### 2024-03-22 boundary_v0.tex
20240322

--- 2024-03-22 boundary.tex
@@
 The integration scheme used for proposed method is shown in Fig.
-\ref{fig2}, in which the total number of the blue circular integration points has been optimized from a global point of view, aiming to reduce the computation of traditional meshfree shape functions and its first order derivatives.
-In contrast, for assembly stiffness matrix $\boldsymbol K$, the low order Gauss integration rule is suitable to ensure the accuracy due to the inherently variational consistency in smoothed gradients.
-The detailed positions and weight of integration points and the efficiency demonstration of this optimized integration scheme can be found in \cite{wang2019a, du2022}  With a close look at Eqs.
+\ref{fig2}, the detailed positions and weight of integration points can be found in \cite{du2022}  With a close look at Eqs.
 (\ref{de2}) and (\ref{de3}), the proposed approach for enforcing essential boundary conditions show an identical structure with traditional Nitsche's method, both have the consistent and stabilized terms.
@@
                      + (P\boldsymbol a_3 \cdot (\boldsymbol v - \bar{\boldsymbol v}))_{\boldsymbol x \in C_v}}_{\text{consistent term}} \\
-                     &+ \underbrace{\sum_{i=1}^3\frac{\alpha_{vi}}{2} \int_{\Gamma_v} \boldsymbol v \cdot \boldsymbol v d\Gamma 
+                     &+ \underbrace{\frac{\alpha_v}{2} \int_{\Gamma_v} \boldsymbol v \cdot \boldsymbol v d\Gamma 
                      + \frac{\alpha_\theta}{2} \int_{\Gamma_\theta} \theta_{\boldsymbol n}^2 d\Gamma
-             + \frac{\alpha_C}{2}(\boldsymbol v \cdot \boldsymbol a_3)^2_{\boldsymbol x\in C_v}}_{\text{stabilized term}}
+             + \frac{\alpha_C}{2}(\boldsymbol v \cdot \boldsymbol v)_{\boldsymbol x\in C_v}}_{\text{stabilized term}}
 \end{split}
@@
 where the consistent term generated from the Lagrangian multiplier method contributes to enforce the essential boundary, and meet the variational consistency condition.
-However, the consistent term can not always ensure the coercivity of stiffness, so the penalty method is introduced to serve as a stabilized term, in which $\alpha_{vi}$'s, $\alpha_\theta$ and $\alpha_C$ are experimental artificial parameters in penalty method.
+However, the consistent term can not always ensure the coercivity of stiffness, so the penalty method is introduced to serve as a stabilized term.
 With a standard variational argument, the corresponding weak form can be stated as:
@@
                      + (\delta P\boldsymbol a_3 \cdot (\boldsymbol v - \bar{\boldsymbol v}))_{\boldsymbol x \in C_v} \\
-                     &+ \sum_{i=1}^{3}\alpha_{vi} \int_{\Gamma_v} (\delta \boldsymbol v \cdot \boldsymbol a_i) (\boldsymbol a_i \cdot \boldsymbol v) d\Gamma 
+                     &+ \alpha_v \int_{\Gamma_v} \delta \boldsymbol v \cdot \boldsymbol v d\Gamma 
                      + \alpha_\theta \int_{\Gamma_\theta} \delta \theta_{\boldsymbol n}\theta_{\boldsymbol n} d\Gamma
-                     + \alpha_C(\delta \boldsymbol v \cdot \boldsymbol a_3 \; \boldsymbol a_3 \cdot \boldsymbol v)_{\boldsymbol x\in C_v} \\
+                     + \alpha_C(\delta \boldsymbol v \cdot \boldsymbol v)_{\boldsymbol x\in C_v} \\
                      &= 0
@@
 \end{equation}
-Further invoking the conventional reproducing kernel approximation of Eq. (\ref{approxv}) leads to the following discrete equilibrium equations:
+in which $\alpha_v$, $\alpha_\theta$ and $\alpha_C$ represent experimental artificial parameters.
+Further invoking the conventional reproducing kernel approximation of Eq.
+(\ref{approxv}) leads to the following discrete equilibrium equations:
 \begin{equation}
@@
 \begin{align}
-\boldsymbol K^s_{IJ} &= \boldsymbol \alpha_v \int_{\Gamma_v} \Psi_I \Psi_J d\Gamma 
+\boldsymbol K^s_{IJ} &= \alpha_v \int_{\Gamma_v} \Psi_I \Psi_J \boldsymbol 1 d\Gamma 
 + \alpha_\theta \int_{\Gamma_\theta} \Psi_{I,\eta} n^\eta \boldsymbol a_3 \boldsymbol a_3 n^\gamma\Psi_{J,\gamma} d\Gamma + \alpha_C [[\Psi_I \boldsymbol a_3 \boldsymbol a_3 \Psi_J]]_{\boldsymbol x \in C_v} \\
-\boldsymbol f^s_I &= \boldsymbol \alpha_v \int_{\Gamma_v} \Psi_I \bar{\boldsymbol v} d\Gamma + \alpha_\theta \int_{\Gamma_\theta} \Psi_{I,\eta} n^\eta \boldsymbol a_3 \boldsymbol \bar \theta_{\boldsymbol n} d\Gamma + \alpha_C [[\Psi_I \boldsymbol a_3 \boldsymbol a_3 \cdot \bar{\boldsymbol v}]]_{\boldsymbol x \in C_v}
+\boldsymbol f^s_I &= \alpha_v \int_{\Gamma_v} \Psi_I \bar{\boldsymbol v} d\Gamma + \alpha_\theta \int_{\Gamma_\theta} \Psi_{I,\eta} n^\eta \boldsymbol a_3 \boldsymbol \bar \theta_{\boldsymbol n} d\Gamma + \alpha_C [[\Psi_I \boldsymbol a_3 \boldsymbol a_3 \cdot \bar{\boldsymbol v}]]_{\boldsymbol x \in C_v}
 \end{align}
 \end{subequations}
-with
-\begin{equation}
-\boldsymbol \alpha_v = \begin{bmatrix}
-    \alpha_{v1} & 0 & 0 \\
-    0 & \alpha_{v2} & 0 \\
-    0 & 0 & \alpha_{v3} \\
-\end{bmatrix}
-\end{equation}
 
@@
 Moreover, the stabilized terms in Eq.
-(\ref{nde3}) employs the penalty method with big enough artificial parameters to ensure the coercivity of stiffness.
-And the optimal values of these artificial parameters are proportional to the grid size of discrete model that can be represented by support size in meshfree approximation, where the $\alpha_{v\alpha} \propto s^{-1}$, $\alpha_{v3} \propto s^{-3}$, $\alpha_\theta \propto s^{-1}$, $\alpha_C \propto s^{-2}$\cite{benzaken2021}, and $s = \min\{s_{\alpha I}\}$.
+(\ref{nde3}) employs the penalty method to ensure the coercivity of stiffness.
 In contrast, the stabilized term of Eq.

### 2024-03-22 examples.tex
20240322

@@
 \ref{ptf1}, the flat and curved models are depicted by an identical parametric domain $\Omega = (0,1)\otimes(0,1)$, where the cylindrical coordinate system with radius $R=1$ is employed to describe the curved model, and the whole domain $\Omega$ is discretized by the $165$ meshfree nodes.
+The artificial parameters of $\alpha_v=10^5, \alpha_\theta=10^3, \alpha_C=10^5$ and $\alpha_v=10^9, \alpha_\theta=10^9, \alpha_C=10^9$ are used for Nitsche's method and penalty method respectively.
 All the boundaries are enforced as essential boundary conditions with the following manufactured exact solution:
@@
 RKGSI-Nitsche and RKGSI-HW, can pass the linear and quadratic patch test.
+In contrast, the RKGSI-Penalty cannot pass the patch test since the Penalty method is unable to ensure the variational consistency.
 Due to the loss of variational consistency condition, even with Nitsche's method, Gauss meshfree formulations show noticeable errors.
@@
 However, the RKGSI-HW and RKGSI-Nitsche methods also provide better accuracy compared to others due to the fulfillment of first second-order variational consistency.
+And, even only with local variational consistency, the RKGSI-Penalty obtained a better result than traditional Gauss scheme.
 Meanwhile, the bending moment contours of $M^{12}$ are listed in Fig.
 \ref{ptf2}, which further verify that the proposed method provided a satisfactory result compared to exact solution.
-On the other hand, the conventional Gauss meshree formulations showed errors.
+On the other hand, the RKGSI-Penalty and the conventional Gauss meshree formulations showed errors.
 
@@
 \ref{slf2}.
-The comparison of the displacement in $z-$direction at node $A$, $v_{A3}$, is used as the investigated quantity, with the reference value 0.3024 given by \cite{macneal1985}.
+The comparison of the displacement in $z-$direction at node $A$, $v_{A3}$, is used as the investigated quantity, with the reference value 0.3006 given by \cite{kiendl2009}.
 Firstly, Fig.
-\ref{slf3} presents a sensitivity study for the artificial parameters of $\alpha_v$'s, $\alpha_\theta$'s in the RKGSI meshfree formulations with Nitsche's method and penalty method.
+\ref{slf3} presents a sensitivity study for the artificial parameters of $\alpha_{vi}$'s and $\alpha_\theta$'s in the RKGSI meshfree formulations with Nitsche's method and penalty method, where all of the parameters are scaled by the support size as, $\alpha_{v\alpha} = s^{-1}\bar \alpha_v$, $\alpha_{v3} = s^{-3} \bar \alpha_v$ and $\alpha_\theta = s^{-1}\bar \alpha_\theta$.
+For a better comparison, the result of proposed RKGSI-HW is also listed in this figure.
 The results of Fig.
@@
 \centering
-\includegraphics[width=\textwidth]{figures/sla}
+\includegraphics[width=\textwidth]{figures/sla_r1}
 \caption{Sensitivity comparison of $\alpha_v$ and $\alpha_\theta$ for Scordelis-Lo problem.}\label{slf3}
@@
 \centering
-\includegraphics[width=\textwidth]{figures/sld}
+\includegraphics[width=\textwidth]{figures/sld_r1}
 \caption{Displacement convergence for Scordelis-Lo roof problem.}\label{slf4}
@@
 
-Due to symmetry, only quadrant model, where the $8\times8$, $16\times16$, $24\times24$ and $32\times32$ meshfree nodes have been discretized, was considered.
+Due to symmetry, only quadrant model, where the $16\times16$, $24\times24$, $32\times32$ and $40\times40$ meshfree nodes have been discretized as shown in Fig.
+(\ref{phfm}), was considered.
 The quantity under investigation for convergence is the displacement at $x-$direction on point $A$, $v_{A1}$.
@@
 \centering
-\includegraphics[width=\textwidth]{figures/pfd}
+\includegraphics[width=\textwidth]{figures/pfmsh_r1}
+\caption{Meshfree discretizations for pinched hemispherical shell problem.}\label{phfm}
+\end{figure}
+\begin{figure}[!ht]
+\centering
+\includegraphics[width=\textwidth]{figures/pfd_r1}
 \caption{Displacement convergence for pinched hemispherical shell problem.}\label{phf2}

### 2024-03-22 frontmatter.tex
20240309
20240322

@@
     % \title{A Hu-Washizu variational consistent meshfree thin shell formulation naturally accommodating essential boundary conditions}
-    \title{An quasi-consistent efficient meshfree thin shell formulation naturally accommodating essential boundary conditions}
+    % \title{Quasi-consistent efficient meshfree thin shell formulation to naturally accommodate essential boundary conditions}
+    \title{Quasi-consistent efficient meshfree thin shell formulation with penalty-free essential boundary condition enforcement}
     \author[1]{Junchao Wu\corref{cor1}}
     \ead{jcwu@hqu.edu.cn}
-    \author[2]{Yangtao Xu}
+    \author[1]{Yangtao Xu}
     \author[1]{Bin Xu}
-    \author[3]{Syed Humayun Basha}
+    \author[1]{Syed Humayun Basha}
 
     \affiliation[1]{organization={Key Laboratory for Intelligent Infrastructure and Monitoring of Fujian Province,
-                                  College of Civil Engineering,
-                                  Huaqiao University},
-                    city={Xiamen},
-                    state={Fujian},
-                    postcode={361021},
-                    country={China}}
-
-    \affiliation[2]{organization={College of Civil Engineering,
-                                  Huaqiao University},
-                    city={Xiamen},
-                    state={Fujian},
-                    postcode={361021},
-                    country={China}}
-
-    \affiliation[3]{organization={Key Laboratory for Structural Engineering and Disaster Prevention of Fujian Province,
+                                  Key Laboratory for Structural Engineering and Disaster Prevention of Fujian Province,
                                   College of Civil Engineering,
@@
 \begin{abstract}
-This research proposed an eficient and quasi-consistent meshfree thin shell formulation with natural enforcement of essential boundary conditions.
+This research proposed an eficient and quasi-consistent meshfree thin shell formulation with penalty-free enforcement of essential boundary conditions.
 Within the framework of the Hu-Washizu variational principle, a mixed formulation of displacements, strains and stresses is employed in this approach, where the displacements are discretized using meshfree shape functions, and the strains and stresses are expressed using smoothed gradients, covariant smoothed gradients and covariant bases.
-The smoothed gradients satisfy the first and second order integration constraint and have quasi-consistent consistency.
+The smoothed gradients satisfy the first second-order integration constraint and have variational consistency for polynomial strains and stresses.
 Owing to Hu-Washizu variational principle, the essential boundary conditions automatically arise in its weak form.
@@
 Contrary to Nitsche's method, the costly higher order derivatives of conventional meshfree shape functions were replaced by the smoothed gradients with fast computation, which improve the efficiency.
-Meanwhile, the proposed formulation features a naturally stabilized term without adding any artificial stabilization factors, which eliminates the stabilization parameter-dependent issue in the Nitsche's method.
+Meanwhile, the proposed formulation features a naturally stabilized term without adding any artificial stabilization factors, which eliminates the employment of penalty method as a stabilization.
 The efficacy of the proposed Hu-Washizu meshfree thin shell formulation is illustrated by a set of classical standard thin shell problems.

### 2024-03-22 introduction.tex
20240322

@@
 Furthermore, nodal-based meshfree approximations generally offer the flexibility of local refinement and can relieve the burden of mesh distortion.
-Owing to these benefits, numerous meshfree techniques have been developed and implemented in many scientific and engineering fields \cite{liu2009,zhang2000meshless,millan2011,wang2023b,suchde2023,deng2023b}.
+Owing to these benefits, numerous meshfree techniques have been developed and implemented in many scientific and engineering fields \cite{liu2009,zhang2000,millan2011,wang2023b,suchde2022,deng2023a,wang2024}.
 However, the high order smoothed meshfree shape functions accompany the enlarged and overlapping supports, which may potentially cause many problems for shape functions.
 One of the issues is the loss of the Kronecker delta property, which means that, unlike the finite element methods, the necessary boundary conditions cannot be directly enforced  \cite{fernandez-mendez2004}.
-Another issue is that the variational consistency or said integration constraint cannot be satisfied due to the misalignment between the numerical integration domains and supports of shape functions.
-Besides, the shape functions exhibit a piecewise rational nature in each integration domain.
-Therefore, variational consistency is vital to the solution accuracy in Galerkin formulations \cite{li2016, wu2021}.
+Another issue is that the variational consistency or said integration constraint, which is a condition requires the formulation to exactly reproduce the solution spanned by basis functions, cannot be satisfied.
+This issue is caused by the misalignment between the numerical integration domains and supports of shape functions, and thus, the shape functions exhibit to a piecewise nature in each integration domain.
+It turns to that the traditional integration rules like Gauss scheme cannot ensure the integration accuracy in Galerkin weak form \cite{li2016, wu2021}.
+Therefore, variational consistency is vital to the solution accuracy in Galerkin formulations.
 
@@
 In order to address the issue of numerical integration, a series of consistent integration schemes have been developed for Galerkin meshfree methods.
-Among these include stabilized conforming nodal integration \cite{chen2001} , variational consistent integration \cite{chen2013}, quadratic consistent integration \cite{duan2012a}, reproducing kernel gradient smoothing integration \cite{wang2019a}, and consistent projection integration  \cite{wang2023}.
+Among these include stabilized conforming nodal integration \cite{chen2001} , variational consistent integration \cite{chen2013a}, quadratic consistent integration \cite{duan2012a}, reproducing kernel gradient smoothing integration \cite{wang2019a}, and consistent projection integration  \cite{wang2023}.
 The assumed strain approach establishes the most consistent integration scheme, while the smoothed gradient replaces the costly higher order derivatives of traditional meshfree shape functions and shows a high efficiency.

### 2024-03-22 generatediff.sh

@@ -1,0 +1,8 @@
+for filename in $(ls .)
+    if test -z $(string match -r '\S+[^diff,^v0,^backup,^response][.]tex' $filename)
+    else
+        echo $filename
+        set name $(string split . $filename)[1]
+        latexdiff --math-markup=1 $PWD/$(string join '' $name "_v0.tex") $PWD/$filename > $PWD/$(string join '' $name "_diff.tex")
+    end
+end

### 2024-03-23 response.tex
check the responses

--- 2024-03-09 response.tex
@@
 \usepackage{amsmath,amssymb,amsfonts,amsthm,bm}
+\usepackage{enumerate}
 \title{Response to Reviewer's Comments}
-\setlength{\parindent}{0em}
+\author{}
+\date{}
+% \setlength{\parindent}{0em}
 \setlength{\parskip}{1em}
@@
 
-The authors sincerely thank the reviewers for their further comments. Accordingly, the authors have meticulously revised the manuscript and the details are given as follows.
+Authors appreciate careful reading of the manuscript by the reviewers, and are thankful for helpful suggestions for its improvement.
+Authors have modified the manuscript substantially in light of the reviewer's comments.
+All the modifications and changes made are highlighted in the Marked Revised Manuscript.
+Issues and concerns raised by the reviewers are discussed as follows:
 
@@
 
-\textbf{1.} \textit{After Eq. 5, the formulation of theta needs to be provided.}
+\textbf{Comment 1.} \textit{After Eq. 5, the formulation of theta needs to be provided.}
 
-\textbf{Reply:}
+\textbf{Response:} Authors thank the reviewer for the suggestion. The expression to calcualte rotation ($\boldsymbol \theta$) is derived as follows:
+\begin{equation}
+    \begin{split}
+        \epsilon_{3i} = 0 \Rightarrow &
+        \left \{
+        \begin{split}
+            \boldsymbol \theta \cdot \boldsymbol a_\alpha &= - \boldsymbol v_{,\alpha} \cdot \boldsymbol a_3 \\
+            \boldsymbol \theta \cdot \boldsymbol a_3 &= 0
+        \end{split}
+        \right . \\ \Rightarrow &
+        \boldsymbol \theta = \underbrace{\boldsymbol \theta \cdot \boldsymbol a_{\alpha}}_{- \boldsymbol v_{,\alpha} \cdot \boldsymbol a_3} \boldsymbol a^\alpha 
+        + \underbrace{\boldsymbol \theta \cdot \boldsymbol a_3}_{0} \boldsymbol a^3 = - \boldsymbol v_{,\alpha} \cdot \boldsymbol a_3 \boldsymbol a^\alpha
+    \end{split}
+\end{equation}
+Based on reveiwers suggestion Eq. (9) on Page 6 (lines ??) has been modified to provide more clarity regarding the calculation of rotation ($\boldsymbol \theta$).
 
-\textbf{2.} \textit{Consider using different symbols for the mid-surface displacement, v is always referring to velocity.}
+\textbf{Comment 2.} \textit{Consider using different symbols for the mid-surface displacement, v is always referring to velocity.}
 
-\textbf{Reply:} Thanks to reviewer's suggestion. However, the velocity is not involved in this paper, it will not lead any misunstanding as $\boldsymbol v$ is denoted for mid-plane displacement.
+\textbf{Response:} Authors appreciate reviewer's suggestion regarding the representation of mid-surface displacement.
+However, it has to be noted that present research article doesnot deal with the calculation of velocity.
+Therefore, the authors believe that the use of notation $\boldsymbol v$ to represent mid-surface displacement will not create confusion.
 
-\textbf{3.} $\boldsymbol \theta$ \textit{is the variation of $\boldsymbol a_3$, so $\boldsymbol \theta \cdot \boldsymbol a_3=0$.
+\textbf{Comment 3.} $\boldsymbol \theta$ \textit{is the variation of $\boldsymbol a_3$, so $\boldsymbol \theta \cdot \boldsymbol a_3=0$.
 This relationship does not come from $\epsilon_{3i} = 0$, which was in Eq.
 (9).}
+% TODO: check the technical part of shear deformation to define Kirchoff hypothesis
+\textbf{Response:} Thanks, the reviewer is right, the rotation $\boldsymbol \theta$ is perpendicular to $\boldsymbol a_3$.
+However, this relationship is also equivalent with $\epsilon_{3i}=0$, which follows the Kirchhofff hypothesis [].
+and can be easily evidenced by expression of Eq.
+(9).
 
-\textbf{Reply:} Thanks, the reviewer is right, the rotation $\boldsymbol \theta$ is perpendicular to $\boldsymbol a_3$.
-However, this relationship is also equivalent with $\epsilon_{3i}=0$, which follows the Kirchhofff hypothesis.
+\textbf{Comment 4.} \textit{Eq. (10) seems to be wrong. Where is $\boldsymbol a_{3,\alpha}$ and where is the most complicated term $\boldsymbol \theta_{,\alpha}$?}
 
-\textbf{4.} \textit{Eq. (10) seems to be wrong. Where is $\boldsymbol a_{3,\alpha}$ and where is the most complicated term $\boldsymbol \theta_{,\alpha}$?}
-
-\textbf{Reply:} Thank you for this comment. The detailed dervation of Eq. (10) is given by the following steps:
+\textbf{Reply:} Authors are thankful to the reviewer for the careful observation. The detailed dervation of curvature given in Eq. (10) is appended below:
 \begin{equation}
@@
 \end{equation}
-The detailed derivation can be found in reference (Benzaken et al.
-2021).
-For the conciseness, the detailed derivation of Eq.
-(10) is not listed in manuscript, and the related statement has been added on line 150 (Page ).
+It has to bring to the notice of the reviewer that the detailed derivation of curvature can be found in previous studies by Benzaken et al.
+[4].
+For the conciseness, a statement related to the derivation of curvature has been added on revised manuscript at page 6 (line???).
 
-\textbf{5.} \textit{Patchtest: table 2 is interesting.
+\textbf{Comment 5.} \textit{Patchtest: table 2 is interesting.
 Eq.
@@
 In general, the solution should be able to reproduce the parametric polynomials if the integration and parametrization are both good.}
-
-\textbf{Reply:} Thank you for your comment.
-As we can find in Eqs.
-(32), (33), (35), (36),  the proposed approach was designated for polynomial strains and stresses.
-For flat model, the polynomial displacement leads to the polynomial strains and stresses.
-However, for curved model, the only polynomial strains can be got, the stresses turn to be non-polynomial due to the curvilinear coordinates.
+% TODO: please check the technicality related to the polynomial and error
+\textbf{Response:} Authors are thankful to the reviewer for the careful insight.
+In the present study, the proposed approach as given in Eqs.
+(32, 33, 35, 36) was used to designate polynomial strains and stresses.
+In the case of flat model, the polynomial mid-surface displacement leads to the polynomial strains and stresses.
+However, for curved model, the only polynomial strains can be got, the stresses turn to be non-polynomial due to the parametrization of curvilinear coordinates.
 As a result, even the integration and parametrization are well posed, the approximated smoothed stresses cannot exactly reproduce this non-polynomial stresses.
@@
 
-\textbf{6.} \textit{Example 5.2, figure (7) is distracting.
+\textbf{Comment 6.} \textit{Example 5.2, figure (7) is distracting.
 The purpose of the newly designed method is to get rid of the penalty parameters.
@@
 
-\textbf{Reply:}
+\textbf{Response:} Based on the reviewer's suggestion, the artificial parameters shown in Figure (7) were scaled by shape function support size ($s$) which can measure the grid size of discrete model ($h$) .
+In accordance with reference Benzaken et al.
+[4], the modified parameters were set as $\alpha_{v\alpha} = \bar\alpha_v / s$, $\alpha_{v3} = \bar\alpha_v / s^3$ and $\alpha_\theta = \bar \theta / s$.
+The parameters $\alpha_{v\alpha}$'s and $\alpha_{v3}$ were redefined to represent in-plane displacements $\boldsymbol v \cdot \boldsymbol a_\alpha$ and deflection $\boldsymbol v \cdot \boldsymbol a_3$ respectively.
+After the parameters were scaled by support size ($s$), both the Nitsche's method and penalty method observed less parameter sensitivity.
+However, the scaled up paramters cannot completely eliminate the \textbf{sensivity issue}.
+Tp provide further clarity, the related statements are added in revised mansucript on Pages 17, 18 and 21.
 
-\textbf{7.} \textit{In Example 5.2, the authors provided the wrong reference value.
+\textbf{Comment 7.} \textit{In Example 5.2, the authors provided the wrong reference value.
 $-0.3024$ is the one under RM shell theory.
@@
 
-\textbf{Reply:} Thank you for your suggestion, the reference value has been changed to $-0.3006$. Accordingly, the related statement on Page 21 is modified.
+\textbf{Response:} Authors are thankful to the reviewer for pointing out the wrong reference value.
+The reference value has been changed to $-0.3006$.
+Accordingly, the related statement on Page 21 has been modified in the revised mansucript.
 
-\textbf{8.} \textit{In Example 6.2, also check if the reference value provided in this study is for RM shells [2].}
+\textbf{Comment 8.} \textit{In Example 6.2, also check if the reference value provided in this study is for RM shells [2].}
 
-\textbf{Reply:}
+\textbf{Response:} Following the reviewer's suggestion, the reference values (???) has been updated in Fig.
+10 on Page 26.
+In order to show a better convergence performance, the meshfree discretizations were modified ranging from $16\times16$ to $40\times40$.
+The related discussions were updated in the revised manuscript on Page 21.
 
-\textbf{9.} \textit{Scodelis-Lo roof, pinched hemisphere, and pinched cylinder are the most famous shell benchmark problems.
+\textbf{Comment 9.} \textit{Scodelis-Lo roof, pinched hemisphere, and pinched cylinder are the most famous shell benchmark problems.
 In [3], the authors named them ”shell obstacle course”.
@@
 
-\textbf{Reply:}
+\textbf{Response:} Authors appreciate reviewer's suggestion.
+Authors also believe the pinched cylinder is one of the most common benchmark example for thin shell formulation.
+Besides, this example was also based on cylinder coordinate system, which is similar to that of Scodelis-Lo roof problem.
+Therefore, taking into account the limitations of the current manuscript content, the pinched cylinder problem was not considered.
+It will be considered as a  further prospective.
 
@@
 
-\textbf{1.} \textit{Please check the gramma of the sentence below Eq. (22).}
+\textbf{Comment 1.} \textit{Please check the grammar of the sentence below Eq. (22).}
 
-\textbf{Reply:} Thanks, following the suggestion, this sentence have been revised on Page 9 and the authors have also doubly checked the writing of this revised.
+\textbf{Response:} Authors are thankful to the reviewer for identifying the grammatical error.
+The sentence below Eq.
+(22)  has beeen modified in the revised mansucript on Page 9 as "?????".
+Besides, the manuscript was double checked to address other grammatical and typo issues.
 
-\textbf{2.} \textit{Why is only the quadratic function used for the basis function vector p in Eq. (23)?}
+\textbf{Comment 2.} \textit{Why is only the quadratic function used for the basis function vector p in Eq. (23)?}
 
-\textbf{Reply:} Thanks for this comment, following the suggestion, this sentence have been revised on Page 9 and the authors have also doubly checked the writing of this revised.
+\textbf{Response:} In the present study, the proposed method is in the context of RKGSI framework that can be easily extended for the high order basis functions.
+However, for conciseness, only quadratic basis function was considered in this study which can be considered as a limitation.
+The formulation with high order basis functions will be considered in the further work and the related statements has been added  in the conclusion of the revised manuscript on Page 27.
 
-\textbf{3.} \textit{Please provide the meaning of the symbol $s_{\alpha I}$ in Eq. (25). What is the parameter value used in this paper?}
+\textbf{Comment 3.} \textit{Please provide the meaning of the symbol $s_{\alpha I}$ in Eq. (25). What is the parameter value used in this paper?}
+% TODO: please check the parameter assignment
+\textbf{Response:} The parameter $s_{\alpha I}$ represents the support size of the shape function $\Psi_I$.
+Following the suggestion, this related statement has been added on Page 9 and the authors have also doubly checked that all the symbols in manuscript have been properly defined.
 
-\textbf{Reply:} Thanks for this comment, following the suggestion, this sentence have been revised on Page 9 and the authors have also doubly checked the writing of this revised.
-
-\textbf{4.} \textit{Fig.
+\textbf{Comment 4.} \textit{Fig.
 2 contains two sets of integration points.
@@
 
-\textbf{5.} \textit{On page 13, the authors stated that "Even with p-th order variational consistency, the proposed formulation can not exactly reproduce the solution spanned by basis functions".
+\textbf{Response:} In the present study, two integration schemes (blue circular integration points and red cross integration points) were considered depending on their contribution.
+For instance, in the case of blue circular integration scheme both domain integration and boundary integration were exist in each integration cell.
+Further, the total number of these blue integration points has been optimized from a global point of view to reduce the computation of meshfree shape functions and their first order derivatives [5].
+On the other hand, the red cross integration scheme was employed for the assembly of stiffness matrix which involve only the integration accuracy and does not consider any boundary integration.
+Thus, the traditional 3-point integration scheme is sufficient to carry out this task.
+Therefore, if the Galerkin formulation adopts the identical points with the blue circular integration scheme, the number of integration points for assembly were increased by two-fold.
+This will reduce the efficiency of the Galerkin meshfree method.
+Taking into account the computational burden, the two different integration schemes adopted in the present study were found to be the ideal choice for the proposed method.
+To provide more clarity, the related discussion has been added in the revised mansucript on Page 16 (lines???).
+
+\textbf{Comment 5.} \textit{On page 13, the authors stated that "Even with p-th order variational consistency, the proposed formulation can not exactly reproduce the solution spanned by basis functions".
 The reproducibility is important for Galerkin meshfree methods.
 So, just suggestion, is it possible to give some more explicit explanations.}
+
+\textbf{Response:} Thanks a lot for this helpful comment.
+This reproducibility is a requirement for the variational consistency, and it is the necessary to achieve the optimal accuracy for Galerkin formulations.
+The related discussions about the reproducibility and consistency condition have been added on Page 2.
 
@@
 
+\textbf{Reply:} Following the reviewer's suggestion, the artificial parameters used in NItsche's method and penalty method have been added on Page 19.
+And the additional demonstrations for RKGSI-penalty also have been added on Pages 19 and 20.
+
 \textbf{7.} \textit{On pages 32-34, some reference information such as journal title and year of publication is missed.}

### 2024-03-23 response.tex
reposne
Check and reply

@@
 
-\textbf{Response:} Thanks a lot for this helpful comment.
-This reproducibility is a requirement for the variational consistency, and it is the necessary to achieve the optimal accuracy for Galerkin formulations.
-The related discussions about the reproducibility and consistency condition have been added on Page 2.
+\textbf{Response:} The reproducibility is one of the essential requirement for the Galerkin formulation variational consistency to achieve an optimal accuracy.
+Based on reviewer's suggestion, the discussion related to the reproducibility and consistency conditions were added on Page 2 of the revised manuscript.
 
@@
 
-\textbf{Reply:} Following the reviewer's suggestion, the artificial parameters used in NItsche's method and penalty method have been added on Page 19.
-And the additional demonstrations for RKGSI-penalty also have been added on Pages 19 and 20.
+\textbf{Reply:} Based on reviewer's suggestion, to provide further clarity the artificial parameters used in Nitsche's method and penalty method were updated on Page 19.
+Additional discussions for RKGSI-penalty were also added on Pages 19 and 20 of the revised manuscript.
+%did you modify the figures.. if so please mention that figures were also modified in the revised manuscript.
 
@@
 
-\textbf{Reply:} Thanks a lot, following the reviewer's suggestion, these reference's information have been revised, the authors also have doubly checked all the information and formats of references.
+\textbf{Reply:} Authors thank the reviewer for the careful observation. The reference information "??? write the details of the reference" has been modified in the revised manuscript.
 

### 2024-03-23 response.tex
fix the todo list, and add the line number

@@
 \end{equation}
-Based on reveiwers suggestion Eq. (9) on Page 6 (lines ??) has been modified to provide more clarity regarding the calculation of rotation ($\boldsymbol \theta$).
+Based on reveiwers suggestion Eq. (9) on Page 6 (lines 150) has been modified to provide more clarity regarding the calculation of rotation ($\boldsymbol \theta$).
 
@@
 % TODO: check the technical part of shear deformation to define Kirchoff hypothesis
-\textbf{Response:} Thanks, the reviewer is right, the rotation $\boldsymbol \theta$ is perpendicular to $\boldsymbol a_3$.
-However, this relationship is also equivalent with $\epsilon_{3i}=0$, which follows the Kirchhofff hypothesis [].
-and can be easily evidenced by expression of Eq.
-(9).
+% NOTE: revised
+
+\textbf{Response:} Thanks for this comment.
+In the authors' opinion, the equation $\epsilon_{3i}=0$ is equivalent with $\boldsymbol \theta \cdot \boldsymbol a_3$, which follows the Kirchhoff hypothesis.
+And the identical statements can be found in previous work by Benzaken et al.
+[4].
 
@@
 [4].
-For the conciseness, a statement related to the derivation of curvature has been added on revised manuscript at page 6 (line???).
+For the conciseness, a statement related to the derivation of curvature has been added on revised manuscript at page 6 (line150).
 
@@
 % TODO: please check the technicality related to the polynomial and error
+% NOTE: revised
+
 \textbf{Response:} Authors are thankful to the reviewer for the careful insight.
@@
 (32, 33, 35, 36) was used to designate polynomial strains and stresses.
-In the case of flat model, the polynomial mid-surface displacement leads to the polynomial strains and stresses.
-However, for curved model, the only polynomial strains can be got, the stresses turn to be non-polynomial due to the parametrization of curvilinear coordinates.
+It can be found from Eqs. (7) and (8), the strains were expressed by the in-plane covariant base ($\boldsymbol a_i$) and the derivatives of displacement ($\boldsymbol v_{,i}$).
+For the flat model, both of $\boldsymbol a_i$ and $\boldsymbol v_{,i}$ are polynomials, so the formulation can easily pass the patch test. 
+However, for the curved model, the $\boldsymbol a_i$ turns to be non-polynomial due the parametrization of curvilinear coordinate system.
 As a result, even the integration and parametrization are well posed, the approximated smoothed stresses cannot exactly reproduce this non-polynomial stresses. 
@@
 After the parameters were scaled by support size ($s$), both the Nitsche's method and penalty method observed less parameter sensitivity.
-However, the scaled up paramters cannot completely eliminate the \textbf{sensivity issue}.
+However, the scaled up paramters cannot completely eliminate the parameter sensitivity problem.
 Tp provide further clarity, the related statements are added in revised mansucript on Pages 17, 18 and 21.
@@
 
-\textbf{Response:} Following the reviewer's suggestion, the reference values (???) has been updated in Fig.
+\textbf{Response:} Following the reviewer's suggestion, the reference values (0.094) has been updated in Fig.
 10 on Page 26.
@@
 The sentence below Eq.
-(22)  has beeen modified in the revised mansucript on Page 9 as "?????".
+(22)  has beeen modified in the revised mansucript on Page 9 as "208".
 Besides, the manuscript was double checked to address other grammatical and typo issues.
@@
 % TODO: please check the parameter assignment
+% NOTE: add some statements.
+
 \textbf{Response:} The parameter $s_{\alpha I}$ represents the support size of the shape function $\Psi_I$.
 Following the suggestion, this related statement has been added on Page 9 and the authors have also doubly checked that all the symbols in manuscript have been properly defined.
+The value of charactorized support size is 2.5 for all examples, which is presented on Page 20 (line 342).
 
@@
 \textbf{Response:} In the present study, two integration schemes (blue circular integration points and red cross integration points) were considered depending on their contribution.
-For instance, in the case of blue circular integration scheme both domain integration and boundary integration were exist in each integration cell.
+For instance, in the case of blue circular integration scheme both domain integration and boundary integration were existed in each integration cell.
 Further, the total number of these blue integration points has been optimized from a global point of view to reduce the computation of meshfree shape functions and their first order derivatives [5].
@@
 Taking into account the computational burden, the two different integration schemes adopted in the present study were found to be the ideal choice for the proposed method.
-To provide more clarity, the related discussion has been added in the revised mansucript on Page 16 (lines???).
+To provide more clarity, the related discussion has been added in the revised mansucript on Page 16 (lines287).
 
@@
 Additional discussions for RKGSI-penalty were also added on Pages 19 and 20 of the revised manuscript.
-%did you modify the figures.. if so please mention that figures were also modified in the revised manuscript.
+% WARN:did you modify the figures.. if so please mention that figures were also modified in the revised manuscript. 
+% NOTE: I modify the figures, however it is not for the comment, it's for the reviewer 1 's Comment 6
 
@@
 
+% NOTE: too many references has been modified, do we list all?
 \textbf{Reply:} Authors thank the reviewer for the careful observation. The reference information "??? write the details of the reference" has been modified in the revised manuscript.

### 2024-03-25 response.tex
Please check and update me if any corrections are needed

@@
 (9).}
-% TODO: check the technical part of shear deformation to define Kirchoff hypothesis
-% NOTE: revised
+% TODO: please check it i have modified it
 
-\textbf{Response:} Thanks for this comment.
-In the authors' opinion, the equation $\epsilon_{3i}=0$ is equivalent with $\boldsymbol \theta \cdot \boldsymbol a_3$, which follows the Kirchhoff hypothesis.
-And the identical statements can be found in previous work by Benzaken et al.
-[4].
+\textbf{Response:} Authors appreciate the reviewers insight regarding the calculation of ???
+(is it strain or what please add the technical term here).
+In the authors' opinion, the equation $\epsilon_{3i}=0$ is equivalent with $\boldsymbol \theta \cdot \boldsymbol a_3$, which follows the Kirchhoff hypothesis of shear deformation.
+Previoulsy, Benzaken et al.
+[4] also adopted similar approach to calculate the rotation.
 
@@
 % NOTE: revised
-
+% NOTE: checked and modified
 \textbf{Response:} Authors are thankful to the reviewer for the careful insight.
@@
 (32, 33, 35, 36) was used to designate polynomial strains and stresses.
-It can be found from Eqs. (7) and (8), the strains were expressed by the in-plane covariant base ($\boldsymbol a_i$) and the derivatives of displacement ($\boldsymbol v_{,i}$).
-For the flat model, both of $\boldsymbol a_i$ and $\boldsymbol v_{,i}$ are polynomials, so the formulation can easily pass the patch test. 
-However, for the curved model, the $\boldsymbol a_i$ turns to be non-polynomial due the parametrization of curvilinear coordinate system.
-As a result, even the integration and parametrization are well posed, the approximated smoothed stresses cannot exactly reproduce this non-polynomial stresses. 
-That is why the approach was named with "quasi-consistent".
+It can be found from Eqs.
+(7) and (8), of the revised manuscript the strains were expressed by the in-plane covariant base ($\boldsymbol a_i$) and the derivatives of displacement ($\boldsymbol v_{,i}$).
+For the flat surface model, both of $\boldsymbol a_i$ and $\boldsymbol v_{,i}$ are polynomials, so the mesh free formulation can easily pass the patch test.
+However, in the case of the curved surface model, the $\boldsymbol a_i$ turns to be non-polynomial due the parametrization of curvilinear coordinate system.
+As a result, even though the integration and parametrization are well poised, the approximated smoothed stresses cannot exactly reproduce the non-polynomial stresses.
+For this reason, the adopted approach in the present study was termed as "quasi-consistent".
 
@@
 % NOTE: add some statements.
-
+% NOTE: modified accordingly.. please check
 \textbf{Response:} The parameter $s_{\alpha I}$ represents the support size of the shape function $\Psi_I$.
-Following the suggestion, this related statement has been added on Page 9 and the authors have also doubly checked that all the symbols in manuscript have been properly defined.
-The value of charactorized support size is 2.5 for all examples, which is presented on Page 20 (line 342).
+Accordingly, the statements related  to support size has been added on Page 9 (line??).
+Besides, the authors have also checked the definitions of all the symbols in the revised manuscript.
+The value of characterized support size of shape function is taken ad 2.5 for all the considered examples, which is reported on Page 20 (line 342).
 
@@
 % NOTE: I modify the figures, however it is not for the comment, it's for the reviewer 1 's Comment 6 
+% NOTE: you can add the modifications here also.. no problem
 
@@
 % NOTE: too many references has been modified, do we list all?
+% TODO: Its just numbers we can add them here also
 \textbf{Reply:} Authors thank the reviewer for the careful observation. The reference information "??? write the details of the reference" has been modified in the revised manuscript.

### 2024-03-26 response.tex
20240326

@@
 (9).}
-% TODO: please check it i have modified it
 
-\textbf{Response:} Authors appreciate the reviewers insight regarding the calculation of ???
-(is it strain or what please add the technical term here).
+\textbf{Response:} Authors appreciate the reviewers insight regarding the calculation of rotation ($\boldsymbol \theta$).
 In the authors' opinion, the equation $\epsilon_{3i}=0$ is equivalent with $\boldsymbol \theta \cdot \boldsymbol a_3$, which follows the Kirchhoff hypothesis of shear deformation.
@@
 In general, the solution should be able to reproduce the parametric polynomials if the integration and parametrization are both good.}
-% TODO: please check the technicality related to the polynomial and error
-% NOTE: revised
-% NOTE: checked and modified
+
 \textbf{Response:} Authors are thankful to the reviewer for the careful insight.
@@
 (7) and (8), of the revised manuscript the strains were expressed by the in-plane covariant base ($\boldsymbol a_i$) and the derivatives of displacement ($\boldsymbol v_{,i}$).
-For the flat surface model, both of $\boldsymbol a_i$ and $\boldsymbol v_{,i}$ are polynomials, so the mesh free formulation can easily pass the patch test.
+For the flat surface model, both of $\boldsymbol a_i$ and $\boldsymbol v_{,i}$ are polynomials, so the meshfree formulation can easily pass the patch test.
 However, in the case of the curved surface model, the $\boldsymbol a_i$ turns to be non-polynomial due the parametrization of curvilinear coordinate system.
-As a result, even though the integration and parametrization are well poised, the approximated smoothed stresses cannot exactly reproduce the non-polynomial stresses.
+As a result, even though the integration and parametrization are well posed, the approximated smoothed stresses cannot exactly reproduce the non-polynomial stresses.
 For this reason, the adopted approach in the present study was termed as "quasi-consistent".
@@
 \textbf{Comment 3.} \textit{Please provide the meaning of the symbol $s_{\alpha I}$ in Eq. (25). What is the parameter value used in this paper?}
-% TODO: please check the parameter assignment
-% NOTE: add some statements.
-% NOTE: modified accordingly.. please check
+
 \textbf{Response:} The parameter $s_{\alpha I}$ represents the support size of the shape function $\Psi_I$.
-Accordingly, the statements related  to support size has been added on Page 9 (line??).
+Accordingly, the statements related  to support size has been added on Page 9 (line 210).
 Besides, the authors have also checked the definitions of all the symbols in the revised manuscript.
@@
 Additional discussions for RKGSI-penalty were also added on Pages 19 and 20 of the revised manuscript.
-% WARN:did you modify the figures.. if so please mention that figures were also modified in the revised manuscript. 
-% NOTE: I modify the figures, however it is not for the comment, it's for the reviewer 1 's Comment 6 
-% NOTE: you can add the modifications here also.. no problem
 

### 2024-03-26 introduction_v0.tex
20240326

--- 2024-03-09 introduction.tex
@@
 Furthermore, nodal-based meshfree approximations generally offer the flexibility of local refinement and can relieve the burden of mesh distortion.
-Owing to these benefits, numerous meshfree techniques have been developed and implemented in many scientific and engineering fields \cite{liu2009,zhang2000meshless,millan2011,wang2023b,suchde2023,deng2023b}.
+Owing to these benefits, numerous meshfree techniques have been developed and implemented in many scientific and engineering fields \cite{liu2009,zhang2000,millan2011,wang2023b,suchde2022,deng2023a}.
 However, the high order smoothed meshfree shape functions accompany the enlarged and overlapping supports, which may potentially cause many problems for shape functions.

### 2024-03-26 introduction.tex
asas

@@
 Thin shell structures generally adhere to the Kirchhoff hypothesis \cite{donnell1976}, that neglects the shear deformation can be described using Galerkin formulation which requires to have at least $C^1$ continuity.
-The traditional finite element methods usually only have $C^0$ continuous shape functions, and it prefers Mindlin thick shear theory, hybrid and mixed models in simulation of shell structure  \cite{hughes2000}.
+The traditional finite element methods usually have $C^0$ continuous shape functions, and it prefers Mindlin thick shear theory, hybrid and mixed models in simulation of shell structure  \cite{hughes2000}.
 Meshfree methods \cite{belytschko1994,liu1995,chen2017} with high order smoothed shape functions have garnered much research attention over the past thirty years.
-These techniques established the shape functions based on a collection of dispersed nodes, and the high order continuity of shape functions can be easily achieved even with low-order basis functions.
-For thin shell analysis, this high order meshfree approximation can also alleviate the membrane locking caused by the mismatched approximation order of membrane strain and bending strain \cite{krysl1996}.
-Furthermore, nodal-based meshfree approximations generally offer the flexibility of local refinement and can relieve the burden of mesh distortion.
+These techniques established the shape functions based on a collection of dispersed nodes, and high order continuity of shape functions can be easily achieved even with low-order basis functions.
+For thin shell analysis, high order meshfree approximation can also furhter alleviate the membrane locking caused by the mismatched approximation order of membrane strain and bending strain \cite{krysl1996}.
+Moreover, nodal-based meshfree approximations generally offer the flexibility of local refinement and can relieve the burden of mesh distortion.
 Owing to these benefits, numerous meshfree techniques have been developed and implemented in many scientific and engineering fields \cite{liu2009,zhang2000,millan2011,wang2023b,suchde2022,deng2023a,wang2024}.
@@
 One of the issues is the loss of the Kronecker delta property, which means that, unlike the finite element methods, the necessary boundary conditions cannot be directly enforced  \cite{fernandez-mendez2004}.
-Another issue is that the variational consistency or said integration constraint, which is a condition requires the formulation to exactly reproduce the solution spanned by basis functions, cannot be satisfied.
-This issue is caused by the misalignment between the numerical integration domains and supports of shape functions, and thus, the shape functions exhibit to a piecewise nature in each integration domain.
-It turns to that the traditional integration rules like Gauss scheme cannot ensure the integration accuracy in Galerkin weak form \cite{li2016, wu2021}.
-Therefore, variational consistency is vital to the solution accuracy in Galerkin formulations.
+Another issue is that the variational consistency or said integration constraint, which is a condition that requires the formulation to exactly reproduce the solution spanned by the basis functions, cannot be satisfied.
+This issue is mainly caused by the misalignment between the numerical integration domains and supports of shape functions.
+Thus, the shape functions exhibit a piecewise nature in each integration domain.
+Besides, it has to be noted that the traditional integration rules like Gauss scheme cannot ensure the integration accuracy in Galerkin weak form \cite{li2016, wu2021}.
+Therefore, variational consistency is vital to the solution accuracy in the Galerkin meshfree formulations.
 
@@
 However, these methods are not based on a variational setting and cannot guarantee variational consistency.
-In the absence of a meshfree node, accuracy enforcement might be poorer.
+In the absence of a meshfree node, accuracy enforcement might be poor.
 In contrast, enforcing the essential boundary conditions using a variational approach is preferred for Galerkin meshfree methods.

### 2024-03-27 introduction.tex
asa

@@
 Various ways have been presented to enforce the necessary boundary for Galerkin meshfree methods directly, including the boundary singular kernel method \cite{chen2000a}, mixed transformation method  \cite{chen2000a}, and interpolation element-free method \cite{liu2019a} for recovering shape functions’ Kronecker property.
-However, these methods are not based on a variational setting and cannot guarantee variational consistency.
+However, these methods were not based on variational setting and cannot guarantee variational consistency.
 In the absence of a meshfree node, accuracy enforcement might be poor.
@@
 In this method, the extra degrees of freedom are used to determine the discretion of Lagrange multiplier.
-Furthermore, Ivannikov et al.
-\cite{ivannikov2014a} have extended this approach to geometrically nonlinear thin shells.
+Ivannikov et al.
+\cite{ivannikov2014a} extended this approach to geometrically nonlinear thin shells.
 Lu et al.
@@
 The assumed strain approach establishes the most consistent integration scheme, while the smoothed gradient replaces the costly higher order derivatives of traditional meshfree shape functions and shows a high efficiency.
-Moreover, to achieve global variational consistency, a consistent essential boundary condition enforcement should cooperate with the consistent integration scheme.
-The consistent integration scheme and Nitsche’s method for treating essential boundary conditions show a good performance since they can satisfy the coercivity without requiring additional degrees of freedom.
-Nevertheless, Nitsche's approach still retains the artificial parameters in stabilized terms, and it is essential to remain conscious of the costly higher order derivatives, particularly for thin plate and thin shell problems.
+Moreover, to achieve global variational consistency, a consistent essential boundary condition enforcement must be combined with the consistent integration scheme.
+The combination of consistent integration scheme and Nitsche’s method for treating essential boundary conditions may demonstrate better performance since both the methods can satisfy the coercivity without requiring additional degrees of freedom.
+Nevertheless, Nitsche's approach still retains the artificial parameters in the stabilized terms, and it is essential to remain cautious of the costly higher order derivatives, particularly for thin plate and thin shell problems.
 Recently, Wu et al.
 \cite{wu2022a,wu2023}  proposed an efficient and stabilized essential boundary condition enforcement method based upon the Hellinger-Reissner variational principle, where a mixed formulation in Hellinger-Reissner weak form recasts the reproducing kernel gradient smoothing integration.
-The terms for enforcing essential boundary conditions are identical to the Nitsche’s method, and both have consistent and stabilized terms.
-Nevertheless, the stabilized term of this method naturally exists in the Hellinger-Reissner weak form and no longer needs the artificial parameters, even for essential boundary enforcement; instead all of the higher order derivatives are represented by smoothed gradients and their derivatives.
+The terms required for enforcing essential boundary conditions are identical to the Nitsche’s method, and both have consistent and stabilized terms.
+However, the stabilized term of this method naturally exists in the Hellinger-Reissner weak form and no longer needs the artificial parameters, even for essential boundary enforcement.
+Instead all of the higher order derivatives are represented by the smoothed gradients and their derivatives.
 
-In this study, an efficient and stabilized variational consistent meshfree method that naturally enforces the essential boundary conditions is developed for thin shell structure.
-Following the concept of the Hellinger-Reissner principle base consistent meshfree method, the Hu-Washizu variational principle of complementary energy with variables of displacement, strains, and stresses is employed.
-The displacement is approximated by conventional meshfree shape functions, and the strains and stresses are expressed by smoothed gradients with covariant bases.
-It is important to note that although the first second-order integration requirements are naturally embedded in the smoothed gradients, their fulfillment can only result in a quasi-satisfaction of variational consistency because of the non-polynomial nature of the stresses.
-Hu-Washizu's weak form is used to evaluate all the essential boundary conditions regarding displacements and rotations.
+In this study, an efficient and stabilized variational consistent meshfree method that naturally enforces the essential boundary conditions is developed for thin shell structures.
+Following the concept of the Hellinger-Reissner principle base consistent meshfree method, the Hu-Washizu variational principle of complementary energy with variables of displacement, strains, and stresses were employed.
+The displacement is approximated by conventional meshfree shape functions, and the strains and stresses were expressed by smoothed gradients with covariant bases.
+It is important to note that although the first second-order integration requirements were naturally embedded in the smoothed gradients, their fulfillment resulted in a quasi-satisfaction of variational consistency.
+This is mainly because of the non-polynomial nature of the stresses.
+Hu-Washizu's weak form was used to evaluate all the essential boundary conditions regarding displacements and rotations.
 This type of formulation is similar to the Nitsche's method but does not require any artificial parameters.

### 2024-03-27 boundary.tex
modfied manuscript

@@
 \end{equation}
-where $\boldsymbol f_I$'s are the components of the traditional force vector:
+where $\boldsymbol f_I$'s denote the components of the traditional force vector:
 \begin{equation}
@@
 \end{equation}
-on further substituting Eqs. (\ref{epsilon2}) and (\ref{kappa2}) into above equation gives the final discrete equilibrium equations, respectively: 
+The complete discrete equilibrium equations can be obtained by further substituting Eqs. (\ref{epsilon2}) and (\ref{kappa2}) into above equation, respectively: 
 \begin{equation}
@@
 (\ref{de2}) and (\ref{de3}) contribute for the enforcement of essential boundary.
-It should be mentioned that, in accordance with reproducing kernel smoothed gradient framework, the integration scheme of Eqs.
-(\ref{de1}-\ref{de3}) should be aligned with the those used in the construction of smoothed gradients.
-The integration scheme used for proposed method is shown in Fig.
+It should be noticed that, in accordance with reproducing kernel smoothed gradient framework, the integration scheme of Eqs.
+(\ref{de1}-\ref{de3}) should be aligned with those used in the construction of smoothed gradients.
+The integration scheme used for the proposed method is shown in Fig.
 \ref{fig2}, in which the total number of the blue circular integration points has been optimized from a global point of view, aiming to reduce the computation of traditional meshfree shape functions and its first order derivatives.
-In contrast, for assembly stiffness matrix $\boldsymbol K$, the low order Gauss integration rule is suitable to ensure the accuracy due to the inherently variational consistency in smoothed gradients.
-The detailed positions and weight of integration points and the efficiency demonstration of this optimized integration scheme can be found in \cite{wang2019a, du2022}  With a close look at Eqs.
-(\ref{de2}) and (\ref{de3}), the proposed approach for enforcing essential boundary conditions show an identical structure with traditional Nitsche's method, both have the consistent and stabilized terms.
-So, the next subsection will review the Nitsche's method and compare it with the proposed method.
-
+In contrast, for assembly stiffness matrix $\boldsymbol K$, the low order Gauss integration rule is suitable to ensure the accuracy due to the inherently variational consistency in the smoothed gradients.
+The detailed positions and weight of the integration points and the efficiency demonstration of this optimized integration scheme can be found in \cite{wang2019a, du2022}.
+Examining Eqs.
+(\ref{de2}) and (\ref{de3}), closely reveal that the structure of the suggested approach to enforce essential boundary conditions is identical to that of the conventional Nitsche's method, with both having the consistent and stabilized terms.
+Thus, a review of Nitsche's method and a comparison with the proposed approach will be provided in the next subsection.
 \subsection{Comparison with Nitsche's method}
@@
 where the consistent term generated from the Lagrangian multiplier method contributes to enforce the essential boundary, and meet the variational consistency condition.
-However, the consistent term can not always ensure the coercivity of stiffness, so the penalty method is introduced to serve as a stabilized term, in which $\alpha_{vi}$'s, $\alpha_\theta$ and $\alpha_C$ are experimental artificial parameters in penalty method.
+However, the consistent term cannot always ensure the coercivity of stiffness, so the penalty method is introduced to serve as a stabilized term, in which $\alpha_{vi}$'s, $\alpha_\theta$ and $\alpha_C$ are experimental artificial parameters in the penalty method.
 With a standard variational argument, the corresponding weak form can be stated as:
@@
 \end{equation}
-Further invoking the conventional reproducing kernel approximation of Eq. (\ref{approxv}) leads to the following discrete equilibrium equations:
+Upon further invoking the conventional reproducing kernel approximation of Eq. (\ref{approxv}), the subsequent discrete equilibrium equations can be obtained:
 \begin{equation}
@@
 On comparing with the consistent terms of Eqs.
-(\ref{de2}) and (\ref{nde2}), the expressions were almost identical, the major difference is that the higher order derivatives of shape functions have been replaced by smoothed gradients.
-Owing to the reproducing kernel framework, the construction of smoothed gradients only concerned about the computation of traditional meshfree shape functions and their first order derivatives, which avoid the costly computation of higher order derivatives.
+(\ref{de2}) and (\ref{nde2}), the expressions were almost identical, the major difference is that the higher order derivatives of shape functions have been replaced by the smoothed gradients.
+Owing to the reproducing kernel framework, the construction of the smoothed gradients only concerned about the computation of traditional meshfree shape functions and their first order derivatives, which avoid the costly computation of higher order derivatives.
 Moreover, the stabilized terms in Eq.
 (\ref{nde3}) employs the penalty method with big enough artificial parameters to ensure the coercivity of stiffness.
-And the optimal values of these artificial parameters are proportional to the grid size of discrete model that can be represented by support size in meshfree approximation, where the $\alpha_{v\alpha} \propto s^{-1}$, $\alpha_{v3} \propto s^{-3}$, $\alpha_\theta \propto s^{-1}$, $\alpha_C \propto s^{-2}$\cite{benzaken2021}, and $s = \min\{s_{\alpha I}\}$.
+Besides, the optimal values of these artificial parameters are proportional to the grid size of discrete model that can be represented by the support size in meshfree approximation, where $\alpha_{v\alpha} \propto s^{-1}$, $\alpha_{v3} \propto s^{-3}$, $\alpha_\theta \propto s^{-1}$, $\alpha_C \propto s^{-2}$\cite{benzaken2021}, and $s = \min\{s_{\alpha I}\}$.
 In contrast, the stabilized term of Eq.

### 2024-03-27 examples.tex
modfied manuscript

@@
 \section{Numerical examples}\label{examples}
-The suggested method, which uses Nitsche's method, the consistent reproducing kernel gradient smoothing integration scheme (RKGSI), and the non-consistent Gauss integration scheme (GI) with penalty method, as well as the proposed Hu-Washizu formulation (HW) to enforce the necessary boundary conditions, is validated in this section through several examples.
-A normalized support size of 2.5 is used for all the methods to ensure the requirement of quadratic base meshfree approximation.
-To eliminate the influence of integration, the Gauss integration scheme uses 6 Gauss points for domain integration and 3 points for boundary integration, so as to maintain the same integration accuracy between domain and boundaries.
+In this section, the suggested method is validated through several examples using the Nitsche's method, the consistent reproducing kernel gradient smoothing integration scheme (RKGSI), and the non-consistent Gauss integration scheme (GI) with penalty method, as well as the proposed Hu-Washizu formulation (HW) to enforce the necessary boundary conditions.
+A normalized support size of 2.5 is used for all the considered methods to ensure the requirement of quadratic base meshfree approximation.
+To eliminate the influence of integration error, the Gauss integration scheme uses 6 Gauss points for domain integration and 3 points for boundary integration, so as to maintain the same integration accuracy between domain and boundaries.
 Moreover, the number of integration points are identical between the Gauss and RKGSI schemes.
@@
 \ref{ptf1}, the flat and curved models are depicted by an identical parametric domain $\Omega = (0,1)\otimes(0,1)$, where the cylindrical coordinate system with radius $R=1$ is employed to describe the curved model, and the whole domain $\Omega$ is discretized by the $165$ meshfree nodes.
-The artificial parameters of $\alpha_v=10^5, \alpha_\theta=10^3, \alpha_C=10^5$ and $\alpha_v=10^9, \alpha_\theta=10^9, \alpha_C=10^9$ are used for Nitsche's method and penalty method respectively.
+The artificial parameters of $\alpha_v=10^5, \alpha_\theta=10^3, \alpha_C=10^5$ and $\alpha_v=10^9, \alpha_\theta=10^9, \alpha_C=10^9$ were adopted in Nitsche's- and penalty- method, respectively.
 All the boundaries are enforced as essential boundary conditions with the following manufactured exact solution:
@@
 In contrast, the RKGSI-Penalty cannot pass the patch test since the Penalty method is unable to ensure the variational consistency.
-Due to the loss of variational consistency condition, even with Nitsche's method, Gauss meshfree formulations show noticeable errors.
+Due to the loss of variational consistency condition, even with the Nitsche's method, Gauss meshfree formulations show noticeable errors.
 Table \ref{ptt2} shows the results for curved model, which indicated that all the considered methods cannot pass the patch test.
 This is mainly because the proposed smoothed gradient of Eqs.
-(\ref{approxse1}) and (\ref{approxse2}) could not exactly reproduce the non-polynomial membrane and bending stress.
-However, the RKGSI-HW and RKGSI-Nitsche methods also provide better accuracy compared to others due to the fulfillment of first second-order variational consistency.
-And, even only with local variational consistency, the RKGSI-Penalty obtained a better result than traditional Gauss scheme.
+(\ref{approxse1}) and (\ref{approxse2}) could not exactly reproduce the non-polynomial membrane and bending stresses.
+On the other hand, the RKGSI-HW and RKGSI-Nitsche methods provide better accuracy compared to the other approaches due to the fulfillment of first second-order variational consistency.
+Even only with local variational consistency, the RKGSI-Penalty obtained a better result than the traditional Gauss scheme.
 Meanwhile, the bending moment contours of $M^{12}$ are listed in Fig.
-\ref{ptf2}, which further verify that the proposed method provided a satisfactory result compared to exact solution.
-On the other hand, the RKGSI-Penalty and the conventional Gauss meshree formulations showed errors.
+\ref{ptf2}, which further verify that the proposed method provided a satisfactory result compared to the exact solution.
+Contrarily, both the RKGSI-Penalty and the conventional Gauss meshree formulations observed errors.
 
@@
 Firstly, Fig.
-\ref{slf3} presents a sensitivity study for the artificial parameters of $\alpha_{vi}$'s and $\alpha_\theta$'s in the RKGSI meshfree formulations with Nitsche's method and penalty method, where all of the parameters are scaled by the support size as, $\alpha_{v\alpha} = s^{-1}\bar \alpha_v$, $\alpha_{v3} = s^{-3} \bar \alpha_v$ and $\alpha_\theta = s^{-1}\bar \alpha_\theta$.
-For a better comparison, the result of proposed RKGSI-HW is also listed in this figure.
+\ref{slf3} presents a sensitivity study for the artificial parameters of $\alpha_{vi}$'s and $\alpha_\theta$'s in the RKGSI meshfree formulations with the Nitsche's- and penalty- method, where all of the parameters are scaled by the support size as, $\alpha_{v\alpha} = s^{-1}\bar \alpha_v$, $\alpha_{v3} = s^{-3} \bar \alpha_v$ and $\alpha_\theta = s^{-1}\bar \alpha_\theta$.
+For a better comparison, the result of the proposed RKGSI-HW is also listed in this figure.
 The results of Fig.
-\ref{slf3} revealed, Nitsche's method observed less artificial sensitivity.
+\ref{slf3} revealed, that Nitsche's method observed less artificial sensitivity.
 However, both the methods cannot trivially determine the optimal values of the artificial parameters.
@@
 \ref{slf4}.
-The convergence result showed that the RKGSI get satisfactory results while the traditional Gauss methods demonstrated noticeable errors.
+The convergence result showed that the RKGSI method get satisfactory results while the traditional Gauss methods demonstrated noticeable errors.
 
@@
 Due to symmetry, only quadrant model, where the $16\times16$, $24\times24$, $32\times32$ and $40\times40$ meshfree nodes have been discretized as shown in Fig.
-(\ref{phfm}), was considered.
+(\ref{phfm}), were considered.
 The quantity under investigation for convergence is the displacement at $x-$direction on point $A$, $v_{A1}$.
@@
 Meanwhile, the efficiency comparison for this problem is also shown in Fig.
-\ref{phf3}, in which the CPU time for assembly and calculation of shape functions are considered.
+\ref{phf3}, in which the CPU time for the assembly and calculation of shape functions are considered.
 Fig.
 \ref{phf3}(a) indicates that the RKGSI scheme observed high efficiency in assembly.
-This is due to the variational inconsistent Gauss meshfree formulation which require more Gaussian points to get satisfactory results.
+This is due to the variational inconsistent Gauss meshfree formulation which require more Gaussian points to achieve satisfactory results.
 Fig.
-\ref{phf3}(b) lists the CPU time spent on enforcing essential boundary conditions for the penalty method, Nitsche's method and proposed HW method.
-The results highlighted that the proposed HW method consumed comparable CPU time in assembly compared to Nitsche's method.
+\ref{phf3}(b) lists the CPU time spent on enforcing essential boundary conditions for the penalty-, Nitsche's- and proposed HW- methods.
+The results highlighted that the proposed HW method consumed comparable CPU time in the assembly compared to Nitsche's method.
 However, less time was spent to calculate the shape functions.
-Since both the HW method and penalty method were developed considering the shape functions first order derivatives.
+Since both the HW- and penalty- method were developed considering the shape functions first order derivatives.
 For this reason, both the methods shared an almost identical time in computing the shape functions.

### 2024-03-27 introduction.tex
modfied manuscript

@@
 
-The remainder of this research paper is structured as follows: The kinematics of the thin shell structure and the weak form of the associated Hu-Washizu principle are briefly described in Section 2.
+The remainder of this research article is structured as follows: The kinematics of the thin shell structure and the weak form of the associated Hu-Washizu principle are briefly described in Section 2.
 Subsequently, the mixed formulation regarding the displacements, strains and stresses in accordance with Hu-Washizu weak form are presented in Section 3.
-The discrete equilibrium equations are derived in Section 4 using the naturally occurring accommodation of essential, and they are compared to the equations obtained using Nitsche's method.
+The discrete equilibrium equations are derived in Section 4 using the naturally occurring accommodation of essential.
+Subsequently, they are compared to the equations obtained using Nitsche's method.
 The numerical results in Section 5 validate the efficacy of the proposed Hu-Washizu meshfree thin shell formulation.

### 2024-03-27 kinematics.tex
20240322
modfied manuscript

@@
 \begin{split}
-&\boldsymbol \theta \cdot \boldsymbol a_\alpha + \boldsymbol v_{,\alpha} \cdot \boldsymbol a_3 = 0 \\
+&\boldsymbol \theta \cdot \boldsymbol a_\alpha =- \boldsymbol v_{,\alpha} \cdot \boldsymbol a_3 \\
 &\boldsymbol \theta \cdot \boldsymbol a_3 = 0
@@
 \end{equation}
-and $N^{\alpha\beta}$, $M^{\alpha\beta}$ are the components of membrane and bending stresses given by:
+and $N^{\alpha\beta}$, $M^{\alpha\beta}$ represent the components of membrane- and bending- stresses which are given by:
 \begin{equation}
@@
 
-Essential boundaries on the edges and corners denoted by $\Gamma_v$, $\Gamma_\theta$ and $C_v$ are naturally existed in complementary energy functional, $\bar{\boldsymbol v}$, $\bar \theta_{\boldsymbol n}$ are the corresponding prescribed displacement and normal rotation,respectively.
+Essential boundaries on the edges and corners denoted by $\Gamma_v$, $\Gamma_\theta$ and $C_v$ are naturally existed in complementary energy functional, and $\bar{\boldsymbol v}$, $\bar \theta_{\boldsymbol n}$ are the corresponding prescribed displacement and normal rotation, respectively.
 $\boldsymbol T$, $M_{\boldsymbol{nn}}$ and $P$ can be determined by Euler-Lagrange equations of shell problem \cite{benzaken2021} as follows:
@@
 \end{equation}
-where $\bar{\boldsymbol T}$, $\bar M_{\boldsymbol nn}$ and $\bar P$ are the prescribed traction, bending moment and concentrated force on edges $\Gamma_T$, $\Gamma_M$ and corner $C_P$ respectively.
-All the boundaries meet the following geometric relationships:
+where $\bar{\boldsymbol T}$, $\bar M_{\boldsymbol nn}$ and $\bar P$ are the prescribed traction, bending moment and concentrated force on the edges $\Gamma_T$, $\Gamma_M$ and corner $C_P$, respectively.
+All the specified boundaries meet the following geometric relationships:
 \begin{equation}\label{geo}
@@
 \end{equation}
-and $\bar{\boldsymbol b}$ stands for the prescribed body force in $\Omega$, $\boldsymbol b$ also can be written based on Euler-Lagrange equations \cite{benzaken2021} as:
+and $\bar{\boldsymbol b}$ stands for the prescribed body force in $\Omega$, $\boldsymbol b$ can be written based on Euler-Lagrange equations \cite{benzaken2021} as:
 \begin{equation}

### 2024-04-06 boundary.tex
revised 1

@@
 - \sum_{C=1}^{n_e}\sum_{I=1}^{n_p} \delta \boldsymbol d_I \cdot \left ( (\tilde{\boldsymbol g}^T_{\alpha I} - \bar{\boldsymbol g}^T_{\alpha I}) \boldsymbol d_N^{\alpha}
-+ (\tilde{\boldsymbol g}^T_{\alpha\beta I} - \bar{\boldsymbol g}^T_{\alpha\beta I}) \boldsymbol d_M^{\alpha\beta} \right ) = - \sum_{I=1}^{n_p}\delta d_I \cdot \boldsymbol f_I
++ (\tilde{\boldsymbol g}^T_{\alpha\beta I} - \bar{\boldsymbol g}^T_{\alpha\beta I}) \boldsymbol d_M^{\alpha\beta} \right ) = - \sum_{I=1}^{n_p}\delta \boldsymbol d_I \cdot \boldsymbol f_I
 \end{equation}
@@
 &= \sum_{I=1}^{n_p} \delta \boldsymbol d_I \cdot (\boldsymbol G^{-1} \tilde{\boldsymbol g}_{\alpha I})^T  \boldsymbol G \boldsymbol d^\alpha_N \\
-&= \int_{\Omega_C} \sum_{I=1}^{n_p} \delta \boldsymbol d_I \cdot (\boldsymbol q^T\boldsymbol G^{-1} \tilde{\boldsymbol g}_{\alpha I})^T  \boldsymbol q^T \boldsymbol d^\alpha_N d\Omega \\
-&= \int_{\Omega_C} \sum_{I=1}^{n_p} \delta \boldsymbol d_I \cdot \boldsymbol a_\beta(\boldsymbol q^T\boldsymbol G^{-1} \tilde{\boldsymbol g}_{\alpha I})^T  N^{\alpha\beta h} d\Omega \\
+&= \int_{\Omega_C} \sum_{I=1}^{n_p} \delta \boldsymbol d_I \cdot (\boldsymbol q^T\boldsymbol G^{-1} \tilde{\boldsymbol g}_{\alpha I})  \boldsymbol q^T \boldsymbol d^\alpha_N d\Omega \\
+&= \int_{\Omega_C} \sum_{I=1}^{n_p} \delta \boldsymbol d_I \cdot \boldsymbol a_\beta(\boldsymbol q^T\boldsymbol G^{-1} \tilde{\boldsymbol g}_{\alpha I})  N^{\alpha\beta h} d\Omega \\
 & = \int_{\Omega_C} \delta \tilde \varepsilon_{\alpha\beta}^h N^{\alpha\beta h} d\Omega 
@@
 \end{equation}
-where
+where the components of stiffness matrices and force vectors in discrete equilibrium equations can be evaluated as follows:
 \begin{equation}\label{de1}
-        \boldsymbol K_{IJ} = \int_\Omega \tilde{\boldsymbol \varepsilon}_{\alpha\beta I} hC^{\alpha\beta\gamma\eta}\tilde{\boldsymbol \varepsilon}_{\gamma\eta J} d\Omega + \int_\Omega \tilde{\boldsymbol \kappa}_{\alpha\beta I} \frac{h^3}{12}C^{\alpha\beta\gamma\eta} \tilde{\boldsymbol \kappa}_{\alpha\beta J} d\Omega
+        \boldsymbol K_{IJ} = \int_\Omega \tilde{\boldsymbol \varepsilon}_{\alpha\beta I} hC^{\alpha\beta\gamma\eta}\tilde{\boldsymbol \varepsilon}_{\gamma\eta J} d\Omega + \int_\Omega \tilde{\boldsymbol \kappa}_{\alpha\beta I} \frac{h^3}{12}C^{\alpha\beta\gamma\eta} \tilde{\boldsymbol \kappa}_{\gamma\eta J} d\Omega
 \end{equation}
@@
 \begin{split}
-        \tilde{\boldsymbol K}_{IJ} = &- \int_{\Gamma_v} (\Psi_I \tilde{\boldsymbol T}_{NJ} + \tilde{\boldsymbol T}_{NJ} \Psi_J) d\Gamma \\
-                                     &+ \int_{\Gamma_\theta} (\Psi_{I,\gamma} n^\gamma \boldsymbol a_3 \tilde{\boldsymbol M}_{\boldsymbol{nn}J} + \boldsymbol a_3 \tilde{\boldsymbol M}_{\boldsymbol{nn}I} \Psi_{I,\gamma}n^\gamma)d\Gamma \\
+        \tilde{\boldsymbol K}_{IJ} = &- \int_{\Gamma_v} (\Psi_I \tilde{\boldsymbol T}_{NJ} + \tilde{\boldsymbol T}_{NI} \Psi_J) d\Gamma \\
+                                     &+ \int_{\Gamma_\theta} (\Psi_{I,\gamma} n^\gamma \boldsymbol a_3 \tilde{\boldsymbol M}_{\boldsymbol{nn}J} + \boldsymbol a_3 \tilde{\boldsymbol M}_{\boldsymbol{nn}I} \Psi_{J,\gamma}n^\gamma)d\Gamma \\
                                      & + ([[\Psi_I \boldsymbol a_3 \tilde{\boldsymbol P}_J]] + [[\tilde{\boldsymbol P}_I \boldsymbol a_3 \Psi_J]])_{\boldsymbol x \in C_v}
@@
                      + (P\boldsymbol a_3 \cdot (\boldsymbol v - \bar{\boldsymbol v}))_{\boldsymbol x \in C_v}}_{\text{consistent term}} \\
-                     &+ \underbrace{\sum_{i=1}^3\frac{\alpha_{vi}}{2} \int_{\Gamma_v} \boldsymbol v \cdot \boldsymbol v d\Gamma 
+                     &+ \underbrace{\sum_{i=1}^3\frac{\alpha_{vi}}{2} \int_{\Gamma_v} (\boldsymbol v \cdot \boldsymbol a_i)^2 d\Gamma 
                      + \frac{\alpha_\theta}{2} \int_{\Gamma_\theta} \theta_{\boldsymbol n}^2 d\Gamma
@@
 where the consistent term generated from the Lagrangian multiplier method contributes to enforce the essential boundary, and meet the variational consistency condition.
-However, the consistent term cannot always ensure the coercivity of stiffness, so the penalty method is introduced to serve as a stabilized term, in which $\alpha_{vi}$'s, $\alpha_\theta$ and $\alpha_C$ are experimental artificial parameters in the penalty method.
+However, the consistent term can not always ensure the coercivity of stiffness, so the penalty method is introduced to serve as a stabilized term, in which $\alpha_{vi}$ is the experimental artificial parameter to enforce the displacement towards the $\boldsymbol a_i$ direction, $\alpha_\theta$ and $\alpha_C$ are parameters to enforce rotation and corner deflection, respectively.
 With a standard variational argument, the corresponding weak form can be stated as:
@@
 \begin{equation}
-\sum_{J=1}^{n_p}(\boldsymbol K_{IJ} + \boldsymbol K^c_{IJ} + \boldsymbol K^s_{IJ}) \boldsymbol d_J = \boldsymbol f_I + \boldsymbol f^c + \boldsymbol f^s
+(\boldsymbol K + \boldsymbol K^c + \boldsymbol K^s) \boldsymbol d = \boldsymbol f + \boldsymbol f^c + \boldsymbol f^s
 \end{equation}
-where the stiffness $\boldsymbol K_{IJ}$ is identical with Eq.
+where the stiffness $\boldsymbol K$ is identical with Eq.
 (\ref{de1}).
-$\boldsymbol K^c_{IJ}$ and $\boldsymbol K^s_{IJ}$ are the stiffness matrices for consistent and stabilized terms, respectively, and have the following form:
+$\boldsymbol K^c$ and $\boldsymbol K^s$ are the stiffness matrices for consistent and stabilized terms, respectively, and their components have the following form:
 \begin{subequations}\label{nde2}
@@
 \begin{split}
-\boldsymbol K^c_{IJ} = &- \int_{\Gamma_v} (\Psi_I \boldsymbol T_{NJ} + \boldsymbol T_{NJ} \Psi_J) d\Gamma \\
-                                     &+ \int_{\Gamma_\theta} (\Psi_{I,\gamma} n^\gamma \boldsymbol a_3 \boldsymbol M_{\boldsymbol{nn}J} + \boldsymbol a_3 \boldsymbol M_{\boldsymbol{nn}I} \Psi_{I,\gamma}n^\gamma)d\Gamma \\
+\boldsymbol K^c_{IJ} = &- \int_{\Gamma_v} (\Psi_I \boldsymbol T_{NJ} + \boldsymbol T_{NI} \Psi_J) d\Gamma \\
+                                     &+ \int_{\Gamma_\theta} (\Psi_{I,\gamma} n^\gamma \boldsymbol a_3 \boldsymbol M_{\boldsymbol{nn}J} + \boldsymbol a_3 \boldsymbol M_{\boldsymbol{nn}I} \Psi_{J,\gamma}n^\gamma)d\Gamma \\
                                      & + ([[\Psi_I \boldsymbol a_3 \boldsymbol P_J]] + [[\boldsymbol P_I \boldsymbol a_3 \Psi_J]])_{\boldsymbol x \in C_v}

### 2024-04-06 conclusion.tex
revised 1

@@
 In this study, an efficient and quasi-consistent meshfree thin shell formulation was presented to naturally enforce the essential boundary conditions.
-Mixed formulation with the Hu-Washizu principle weak form is adopted, where the traditional meshfree shape functions discretized the displacement, and the strains and stresses were expressed by the reproducing kernel smoothed gradients and the covariant smoothed gradients, respectively.
+Mixed formulation with the Hu-Washizu principle weak form is adopted, where the traditional meshfree shape functions discretized the displacement, and the strains and stresses were expressed by the reproducing kernel smoothed gradients and the covariant bases, respectively.
 The smoothed gradient naturally embedded the first second-order integration constraints and has a quasi variational consistency for the curved models in each integration cell.

### 2024-04-06 frontmatter.tex
revised 1

@@
     % \title{Quasi-consistent efficient meshfree thin shell formulation to naturally accommodate essential boundary conditions}
-    \title{Quasi-consistent efficient meshfree thin shell formulation with penalty-free essential boundary condition enforcement}
+    % \title{Quasi-consistent efficient meshfree thin shell formulation with penalty-free essential boundary condition enforcement}
+    \title{Quasi-consistent efficient meshfree thin shell formulation with naturally stabilized enforced essential boundary conditions}
     \author[1]{Junchao Wu\corref{cor1}}
@@
 \begin{abstract}
-This research proposed an eficient and quasi-consistent meshfree thin shell formulation with penalty-free enforcement of essential boundary conditions.
-Within the framework of the Hu-Washizu variational principle, a mixed formulation of displacements, strains and stresses is employed in this approach, where the displacements are discretized using meshfree shape functions, and the strains and stresses are expressed using smoothed gradients, covariant smoothed gradients and covariant bases.
-The smoothed gradients satisfy the first second-order integration constraint and have variational consistency for polynomial strains and stresses.
+This research proposed an efficient and quasi-consistent meshfree thin shell formulation with naturally stabilized enforcement of essential boundary conditions.
+Within the framework of the Hu-Washizu variational principle, a mixed formulation of displacements, strains and stresses is employed in this approach, where the displacements are discretized using meshfree shape functions, and the strains and stresses are expressed using smoothed gradients and covariant bases.
+The smoothed gradients satisfy the first second-order integration constraint and observed variational consistency for polynomial strains and stresses.
 Owing to Hu-Washizu variational principle, the essential boundary conditions automatically arise in its weak form.
 As a result, the suggested technique's enforcement of essential boundary conditions resembles that of the traditional Nitsche's method.
-Contrary to Nitsche's method, the costly higher order derivatives of conventional meshfree shape functions were replaced by the smoothed gradients with fast computation, which improve the efficiency.
-Meanwhile, the proposed formulation features a naturally stabilized term without adding any artificial stabilization factors, which eliminates the employment of penalty method as a stabilization.
-The efficacy of the proposed Hu-Washizu meshfree thin shell formulation is illustrated by a set of classical standard thin shell problems.
+Contrary to Nitsche's method, the costly higher order derivatives of conventional meshfree shape functions are replaced by the smoothed gradients with fast computation, which improve the efficiency.
+Meanwhile, the proposed formulation features a naturally stabilized term without adding any artificial stabilization factors, which eliminates the application of penalty method as a stabilization.
+Further, the efficacy of the proposed Hu-Washizu meshfree thin shell formulation is illustrated by a set of classical standard thin shell problems.
 \end{abstract}

### 2024-04-06 kinematics.tex
revised 1

@@
 The detailed derivation of Eq.
-\ref{a3} can be found in reference \cite{benzaken2021}.
+\ref{a3} can be found in \cite{benzaken2021}.
 
-Furthermore, substituting Eq. (\ref{a3}) into Eq. (\ref{kappa1}) leads to:
+Furthermore, on substituting Eq. (\ref{a3}) into Eq. (\ref{kappa1}) leads to:
 \begin{equation}
@@
 \end{equation}
-in which $\Gamma^\gamma_{\alpha\beta} = \boldsymbol a_{\alpha,\beta} \cdot \boldsymbol a^\gamma$ is namely the Christoffel symbol of the second kind, and $\boldsymbol v_{,\alpha}\vert\beta$ is the in-plane covariant derivative of $\boldsymbol v_{,\alpha}$, i.e.
+in which $\Gamma^\gamma_{\alpha\beta} = \boldsymbol a_{\alpha,\beta} \cdot \boldsymbol a^\gamma$ is namely the Christoffel symbol of the second kind, and $\boldsymbol v_{,\alpha}\vert_\beta$ is the in-plane covariant derivative of $\boldsymbol v_{,\alpha}$, i.e.
 $\boldsymbol v_{,\alpha}\vert_\beta = \Gamma^\gamma_{\alpha\beta}\boldsymbol v_{,\gamma} - \boldsymbol v_{,\alpha\beta}$.
@@
 \end{equation}
-where $\bar{\boldsymbol T}$, $\bar M_{\boldsymbol nn}$ and $\bar P$ are the prescribed traction, bending moment and concentrated force on the edges $\Gamma_T$, $\Gamma_M$ and corner $C_P$, respectively.
+where $\bar{\boldsymbol T}$, $\bar M_{\boldsymbol{nn}}$ and $\bar P$ are the prescribed traction, bending moment and concentrated force on edges $\Gamma_T$, $\Gamma_M$ and corner $C_P$ respectively.
 All the specified boundaries meet the following geometric relationships:

### 2024-04-06 generatediff.sh

@@ -1,8 +1,0 @@
-for filename in $(ls .)
-    if test -z $(string match -r '\S+[^diff,^v0,^backup,^response][.]tex' $filename)
-    else
-        echo $filename
-        set name $(string split . $filename)[1]
-        latexdiff --math-markup=1 $PWD/$(string join '' $name "_v0.tex") $PWD/$filename > $PWD/$(string join '' $name "_diff.tex")
-    end
-end

### 2024-04-11 examples_v1.tex
pulish 1

--- 2024-03-27 examples.tex
@@
 As shown in Fig.
-\ref{ptf1}, the flat and curved models are depicted by an identical parametric domain $\Omega = (0,1)\otimes(0,1)$, where the cylindrical coordinate system with radius $R=1$ is employed to describe the curved model, and the whole domain $\Omega$ is discretized by the $165$ meshfree nodes.
-The artificial parameters of $\alpha_v=10^5, \alpha_\theta=10^3, \alpha_C=10^5$ and $\alpha_v=10^9, \alpha_\theta=10^9, \alpha_C=10^9$ were adopted in Nitsche's- and penalty- method, respectively.
+\ref{ptf1}, the flat and curved models are depicted by an identical parametric domain $\Omega = (0,1)\otimes(0,1)$, where the cylindrical coordinate system with radius $R=1$, thickness $h=0.1$ is employed to describe the curved model, and the whole domain $\Omega$ is discretized by the $165$ meshfree nodes.
+The Young's modulus and Poisson's ratio of thin shell are set to $E=1$, $\nu=0$.
+The artificial parameters of $\alpha_v=10^5\times E$, $\alpha_\theta=10^3\times E$, $\alpha_C=10^5\times E$ and $\alpha_v=10^9\times E, \alpha_\theta=10^9\times E, \alpha_C=10^9\times E$ were adopted in Nitsche's- and penalty- method, respectively.
 All the boundaries are enforced as essential boundary conditions with the following manufactured exact solution:
@@
     \midrule
-    GI-Penalty & $4.45E-4$ & $1.35E-2$ & $2.01E-3$ & $1.63E-2$ \\
-    GI-Nitsche & $4.51E-4$ & $1.42E-2$ & $1.22E-3$ & $1.68E-2$ \\
-    RKGSI-Penalty & $3.64E-9$ & $6.77E-8$ & $4.54E-9$ & $6.57E-8$ \\
-    RKGSI-Nitsche & $3.31E-12$ & $1.34E-11$ & $5.98E-12$ & $1.21E-11$ \\
-    RKGSI-HR & $6.67E-13$ & $1.50E-11$ & $1.07E-12$ & $1.26E-11$ \\
+    GI-Penalty & 4.45E-04 & 1.35E-02 & 2.01E-03 & 1.63E-02 \\
+    GI-Nitsche & 4.51E-04 & 1.42E-02 & 1.22E-03 & 1.68E-02 \\
+    RKGSI-Penalty & 3.64E-09 & 6.77E-08 & 4.54E-09 & 6.57E-08 \\
+    RKGSI-Nitsche & 3.31E-12 & 1.34E-11 & 5.98E-12 & 1.21E-11 \\
+    RKGSI-HR & 6.67E-13 & 1.50E-11 & 1.07E-12 & 1.26E-11 \\
     \bottomrule
@@
     \midrule
-    GI-Penalty & $3.79E-4$ & $1.30E-2$ & $1.74E-3$ & $1.37E-2$ \\
-    GI-Nitsche & $4.04E-4$ & $1.42E-2$ & $1.15E-3$ & $1.49E-2$ \\
-    RKGSI-Penalty & $1.47E-4$ & $5.39E-3$ & $2.26E-4$ & $2.09E-3$ \\
-    RKGSI-Nitsche & $2.41E-6$ & $7.37E-5$ & $2.47E-6$ & $2.89E-5$ \\
-    RKGSI-HR & $4.28E-6$ & $1.30E-4$ & $9.69E-6$ & $2.41E-4$ \\
+    GI-Penalty & 3.79E-04 & 1.30E-02 & 1.74E-03 & 1.37E-02 \\
+    GI-Nitsche & 4.04E-04 & 1.42E-02 & 1.15E-03 & 1.49E-02 \\
+    RKGSI-Penalty & 1.47E-04 & 5.39E-03 & 2.26E-04 & 2.09E-03 \\
+    RKGSI-Nitsche & 2.41E-06 & 7.37E-05 & 2.47E-06 & 2.89E-05 \\
+    RKGSI-HR & 4.28E-06 & 1.30E-04 & 9.69E-06 & 2.41E-04 \\
     \bottomrule
@@
 (\ref{phfm}), were considered.
-The quantity under investigation for convergence is the displacement at $x-$direction on point $A$, $v_{A1}$.
+The quantity under investigation for convergence is the displacement at $x$-direction on point $A$, $v_{A1}$ = 0.094 \cite{macneal1985}.
 Fig.
@@
 Meanwhile, the efficiency comparison for this problem is also shown in Fig.
-\ref{phf3}, in which the CPU time for the assembly and calculation of shape functions are considered.
+\ref{phf3}, in which the CPU time for assembly and calculation of shape functions are considered.
 Fig.
 \ref{phf3}(a) indicates that the RKGSI scheme observed high efficiency in assembly.
-This is due to the variational inconsistent Gauss meshfree formulation which require more Gaussian points to achieve satisfactory results.
+This is due to the variational inconsistent Gauss meshfree formulation which require more Gaussian points to get satisfactory results.
 Fig.
-\ref{phf3}(b) lists the CPU time spent on enforcing essential boundary conditions for the penalty-, Nitsche's- and proposed HW- methods.
-The results highlighted that the proposed HW method consumed comparable CPU time in the assembly compared to Nitsche's method.
+\ref{phf3}(b) lists the CPU time spent on enforcing essential boundary conditions for the penalty method, Nitsche's method and proposed HW method.
+The results highlighted that the proposed HW method consumed comparable CPU time in assembly compared to Nitsche's method.
 However, less time was spent to calculate the shape functions.
-Since both the HW- and penalty- method were developed considering the shape functions first order derivatives.
+Since both the HW method and penalty method were developed considering the shape functions first order derivatives.
 For this reason, both the methods shared an almost identical time in computing the shape functions.
@@
 \includegraphics[width=\textwidth]{figures/efficient}
-\caption{efficiency comparison for pinched hemispherical shell problem: (a) Whole domain; (b) Essential boundaries}\label{phf3}
+\caption{Efficiency comparison for pinched hemispherical shell problem: (a) Whole domain; (b) Essential boundaries}\label{phf3}
 \end{figure}

### 2024-04-11 introduction.tex
pulish 1

@@
 Thin shell structures generally adhere to the Kirchhoff hypothesis \cite{donnell1976}, that neglects the shear deformation can be described using Galerkin formulation which requires to have at least $C^1$ continuity.
-The traditional finite element methods usually have $C^0$ continuous shape functions, and it prefers Mindlin thick shear theory, hybrid and mixed models in simulation of shell structure  \cite{hughes2000}.
-Meshfree methods \cite{belytschko1994,liu1995,chen2017} with high order smoothed shape functions have garnered much research attention over the past thirty years.
-These techniques established the shape functions based on a collection of dispersed nodes, and high order continuity of shape functions can be easily achieved even with low-order basis functions.
-For thin shell analysis, high order meshfree approximation can also furhter alleviate the membrane locking caused by the mismatched approximation order of membrane strain and bending strain \cite{krysl1996}.
-Moreover, nodal-based meshfree approximations generally offer the flexibility of local refinement and can relieve the burden of mesh distortion.
-Owing to these benefits, numerous meshfree techniques have been developed and implemented in many scientific and engineering fields \cite{liu2009,zhang2000,millan2011,wang2023b,suchde2022,deng2023a,wang2024}.
+Traditional finite element method typically employs $C^0$ continuous shape functions, and it prefers hybrid and mixed shell models, like linear and nonlinear Mindlin models \cite{ahmad1970, hughes2000} and the one inextensible director model \cite{simo1989b}.
+Over the past thirty years, various novel formulations with high order smoothed shape functions have been applied to thin shell formulations.
+These include element-free Galerkin method \cite{krysl1996}, maximum-entropy meshfree method \cite{millan2011}, Hermite reproducing kernel particle method \cite{wang2015a}, peridynamics \cite{behzadinasab2022}, isogeometric analysis \cite{kiendl2009}, and others.
+For a more comprehensive review of advances and applications of high order formulations in various scientific and engineering fields, refer to \cite{liu2009,chen2017,zhang2017a,suchde2022,wang2023b,deng2023a,wang2024,wang2024a}.
+Among these approaches, Galerkin meshfree methods with moving least square approximation (MLS) \cite{belytschko1994} or reproducing kernel approximation (RK) \cite{liu1995} established the shape functions based on a collection of dispersed nodes, and high order continuity of shape functions can be easily achieved even with low-order basis functions.
+For thin shell analysis, high order meshfree approximation can also further alleviate the membrane locking caused by the mismatched approximation order of membrane strain and bending strain \cite{krysl1996}.
+Moreover, node-based MLS/RK approximations generally offer the flexibility of local refinement and can relieve the burden of mesh distortion. 
 However, the high order smoothed meshfree shape functions accompany the enlarged and overlapping supports, which may potentially cause many problems for shape functions.
@@
 However, these methods were not based on variational setting and cannot guarantee variational consistency.
-In the absence of a meshfree node, accuracy enforcement might be poor.
+The accuracy maybe poor at locations away from the sample points.
 In contrast, enforcing the essential boundary conditions using a variational approach is preferred for Galerkin meshfree methods.
@@
 Lu et al.
-\cite{lu1994} suggested the modified variational essential boundary enforcement approach and expressed the Lagrange multiplier by equivalent tractions to eliminate the excess degrees of freedom.
+\cite{lu1994} suggested the modified variational essential boundary enforcement approach and expressed the Lagrange multiplier by equivalent traction to eliminate the excess degrees of freedom.
 However, the coercivity of this approach is not always ensured and potentially reduces the accuracy.
@@
 Skatulla and Sansour \cite{skatulla2008} extended Nitsche’s thin shell analysis method and proposed an iteration algorithm to determine artificial parameters at each integration point.
+Additionally, the Nitsche's method has been successfully applied to maintain the variational consistency between different geometrical or material domains in problems with multiple patches \cite{guo2021} and composite materials \cite{wang2021b}.
 
 In order to address the issue of numerical integration, a series of consistent integration schemes have been developed for Galerkin meshfree methods.
-Among these include stabilized conforming nodal integration \cite{chen2001} , variational consistent integration \cite{chen2013a}, quadratic consistent integration \cite{duan2012a}, reproducing kernel gradient smoothing integration \cite{wang2019a}, and consistent projection integration  \cite{wang2023}.
+Among these include stabilized conforming nodal integration \cite{chen2001}, variational consistent integration \cite{chen2013a}, quadratic consistent integration \cite{duan2012a}, reproducing kernel gradient smoothing integration \cite{wang2019a}, and consistent projection integration \cite{wang2023}.
 The assumed strain approach establishes the most consistent integration scheme, while the smoothed gradient replaces the costly higher order derivatives of traditional meshfree shape functions and shows a high efficiency.
@@
 The remainder of this research article is structured as follows: The kinematics of the thin shell structure and the weak form of the associated Hu-Washizu principle are briefly described in Section 2.
-Subsequently, the mixed formulation regarding the displacements, strains and stresses in accordance with Hu-Washizu weak form are presented in Section 3.
+The mixed formulation regarding the displacements, strains and stresses in accordance with Hu-Washizu weak form are presented in Section 3.
 The discrete equilibrium equations are derived in Section 4 using the naturally occurring accommodation of essential.

### 2025-04-09 examples.tex
release 1.0

@@
 As shown in Fig.
-\ref{ptf1}, the flat and curved models are depicted by an identical parametric domain $\Omega = (0,1)\otimes(0,1)$, where the cylindrical coordinate system with radius $R=1$ is employed to describe the curved model, and the whole domain $\Omega$ is discretized by the $165$ meshfree nodes.
-The artificial parameters of $\alpha_v=10^5, \alpha_\theta=10^3, \alpha_C=10^5$ and $\alpha_v=10^9, \alpha_\theta=10^9, \alpha_C=10^9$ were adopted in Nitsche's- and penalty- method, respectively.
+\ref{ptf1}, the flat and curved models are depicted by an identical parametric domain $\Omega = (0,1)\otimes(0,1)$, where the cylindrical coordinate system with radius $R=1$, thickness $h=0.05$ is employed to describe the curved model, and the whole domain $\Omega$ is discretized by the $165$ meshfree nodes.
+The Young's modulus and Poisson's ratio of thin shell are set to $E=1$, $\nu=0$.
+The artificial parameters of $\alpha_v=10^5$, $\alpha_\theta=10^3$, $\alpha_C=10^5$ and $\alpha_v=10^9, \alpha_\theta=10^9, \alpha_C=10^9$ were adopted in Nitsche's- and penalty- method, respectively.
 All the boundaries are enforced as essential boundary conditions with the following manufactured exact solution:
@@
     \midrule
-    GI-Penalty & $4.45E-4$ & $1.35E-2$ & $2.01E-3$ & $1.63E-2$ \\
-    GI-Nitsche & $4.51E-4$ & $1.42E-2$ & $1.22E-3$ & $1.68E-2$ \\
-    RKGSI-Penalty & $3.64E-9$ & $6.77E-8$ & $4.54E-9$ & $6.57E-8$ \\
-    RKGSI-Nitsche & $3.31E-12$ & $1.34E-11$ & $5.98E-12$ & $1.21E-11$ \\
-    RKGSI-HR & $6.67E-13$ & $1.50E-11$ & $1.07E-12$ & $1.26E-11$ \\
+    GI-Penalty & 1.41E-04 & 4.62E-03 & 1.97E-03 & 7.17E-03 \\
+    GI-Nitsche & 1.73E-04 & 5.61E-03 & 1.85E-03 & 7.76E-03 \\
+    RKGSI-Penalty & 5.04E-09 & 1.02E-07 & 3.01E-09 & 3.41E-08 \\
+    RKGSI-Nitsche & 9.75E-12 & 8.98E-11 & 1.29E-12 & 1.06E-12 \\
+    RKGSI-HR & 6.15E-13 & 6.91E-12 & 7.51E-13 & 8.36E-12 \\
     \bottomrule
@@
 \centering
-\caption{Results of patch test for cylindrical model.}\label{ptt2}
+\caption{Results of patch test for curved model.}\label{ptt2}
 \begin{tabular}{lcccc}
@@
     \midrule
-    GI-Penalty & $3.79E-4$ & $1.30E-2$ & $1.74E-3$ & $1.37E-2$ \\
-    GI-Nitsche & $4.04E-4$ & $1.42E-2$ & $1.15E-3$ & $1.49E-2$ \\
-    RKGSI-Penalty & $1.47E-4$ & $5.39E-3$ & $2.26E-4$ & $2.09E-3$ \\
-    RKGSI-Nitsche & $2.41E-6$ & $7.37E-5$ & $2.47E-6$ & $2.89E-5$ \\
-    RKGSI-HR & $4.28E-6$ & $1.30E-4$ & $9.69E-6$ & $2.41E-4$ \\
+    GI-Penalty & 1.75E-04 & 4.50E-03 & 1.08E-03 & 5.83E-03 \\
+    GI-Nitsche & 1.77E-04 & 5.36E-03 & 1.07E-03 & 6.33E-03 \\
+    RKGSI-Penalty & 8.59E-05 & 9.11E-04 & 4.28E-04 & 2.08E-03 \\
+    RKGSI-Nitsche & 1.27E-05 & 5.32E-05 & 1.88E-05 & 5.6E-04 \\
+    RKGSI-HR & 1.43E-05 & 1.60E-04 & 2.93E-05 & 2.85E-04 \\
     \bottomrule
@@
 \centering
-\includegraphics[width=\textwidth]{figures/ptc}
+\includegraphics[width=\textwidth]{figures/ptc_r2}
 \caption{Contour plots of $M^{12}$ for curved shell patch test.}\label{ptf2}
@@
 
-\subsection{Scordelis-Lo roof}
+\subsection{Scordelis--Lo roof}
 This example considers the classical Scordelis-Lo roof problem, as depicted in Fig.
@@
 The cylindrical roof has dimensions $R=25$, $L=50$, $h=0.25$, Young's modulus $E=4.32\times 10^8$ and Poisson's ratio $\nu=0.0$.
-The entire roof is subjected to an uniform body force of $b_z = -90$, with the straight edges remainning free and the the curved edges are enforced by $v_x=v_z=0$.
+The entire roof is subjected to a uniform body force of $b_z = -90$, with the straight edges remaining free and the curved edges are enforced by $v_x=v_z=0$.
 
@@
 \ref{slf2}.
-The comparison of the displacement in $z-$direction at node $A$, $v_{A3}$, is used as the investigated quantity, with the reference value 0.3006 given by \cite{kiendl2009}.
+The comparison of the displacement in $z-$direction at node $A$, $v_{A3}$, is used as the investigated quantity, with the reference value -0.3006 given by \cite{kiendl2009}.
 Firstly, Fig.
-\ref{slf3} presents a sensitivity study for the artificial parameters of $\alpha_{vi}$'s and $\alpha_\theta$'s in the RKGSI meshfree formulations with the Nitsche's- and penalty- method, where all of the parameters are scaled by the support size as, $\alpha_{v\alpha} = s^{-1}\bar \alpha_v$, $\alpha_{v3} = s^{-3} \bar \alpha_v$ and $\alpha_\theta = s^{-1}\bar \alpha_\theta$.
+\ref{slf3} presents a sensitivity study for the artificial parameters of $\alpha_{vi}$'s and $\alpha_\theta$'s in the RKGSI meshfree formulations with the Nitsche's- and penalty- method, where all the parameters are scaled by the support size as, $\alpha_{v\alpha} = s^{-1}\bar \alpha_v$, $\alpha_{v3} = s^{-3} \bar \alpha_v$ and $\alpha_\theta = s^{-1}\bar \alpha_\theta$.
 For a better comparison, the result of the proposed RKGSI-HW is also listed in this figure.
@@
 \centering
-\includegraphics[width=\textwidth]{figures/sld_r1}
+\includegraphics[width=\textwidth]{figures/sld_r2}
 \caption{Displacement convergence for Scordelis-Lo roof problem.}\label{slf4}
@@
 \ref{phf1}, which is loaded at four points $P=\pm 2$ at $90^\circ$ interval at its bottom.
-The hemispherical shell has an radius $R=10$, thickness $h=0.04$, Young's modulus $E=6.825\times10^7$ and Poisson's ratio $\nu = 0.3$.
+The hemispherical shell has a radius $R=10$, thickness $h=0.04$, Young's modulus $E=6.825\times10^7$ and Poisson's ratio $\nu = 0.3$.
 

### 2025-04-09 kinematics.tex
release 1.0

@@
 \end{equation}
-where $\boldsymbol a^\alpha$'s is the in-plane contravariant base vector, $\boldsymbol a^\alpha \cdot \boldsymbol a_\beta = \delta^\alpha_\beta$, $\delta$ is the Kronecker delta function.
+where $\boldsymbol a^\alpha$'s are the in-plane contravariant base vectors, $\boldsymbol a^\alpha \cdot \boldsymbol a_\beta = \delta^\alpha_\beta$, $\delta$ is the Kronecker delta function.
 The detailed derivation of Eq.
@@
 in which $\Gamma^\gamma_{\alpha\beta} = \boldsymbol a_{\alpha,\beta} \cdot \boldsymbol a^\gamma$ is namely the Christoffel symbol of the second kind, and $\boldsymbol v_{,\alpha}\vert_\beta$ is the in-plane covariant derivative of $\boldsymbol v_{,\alpha}$, i.e.
-$\boldsymbol v_{,\alpha}\vert_\beta = \Gamma^\gamma_{\alpha\beta}\boldsymbol v_{,\gamma} - \boldsymbol v_{,\alpha\beta}$.
+$\boldsymbol v_{,\alpha}\vert_\beta = \boldsymbol v_{,\alpha\beta} - \Gamma^\gamma_{\alpha\beta}\boldsymbol v_{,\gamma}$.
 
@@
 where $\boldsymbol n = n^\alpha \boldsymbol a_\alpha = n_\alpha \boldsymbol a^\alpha$ and $\boldsymbol s = s^\alpha \boldsymbol a_\alpha = s_\alpha \boldsymbol a^\alpha$ are the outward normal and tangent directions on boundaries.
-$[[f]]$ is the jump operator defined by:
+$[[\bullet]]$ is the jump operator defined by:
 \begin{equation}
-[[f]]_{\boldsymbol x = \boldsymbol x_c} = \lim_{\boldsymbol \epsilon\rightarrow \boldsymbol 0+}(f(\boldsymbol x_c + \boldsymbol \epsilon) - f(\boldsymbol x_c - \boldsymbol \epsilon)), \boldsymbol x_c \in \Gamma
+[[f]]_{\boldsymbol x = \boldsymbol x_c} = \lim_{\boldsymbol \epsilon\rightarrow \boldsymbol 0+}(f(\boldsymbol x_c + \boldsymbol \epsilon) - f(\boldsymbol x_c - \boldsymbol \epsilon)),\quad \boldsymbol x_c \in \Gamma
 \end{equation}
